---
title: "Outcome_analysis"
author: "Khadija Ismail"
date: "`r Sys.Date()`"
format:
  pdf:
    documentclass: article
    geometry: margin=1in
    code-overflow: wrap
    latex-engine: xelatex  # allows better font and color handling
    highlight-style: kate    # built-in code coloring
header-includes:
  - \usepackage{tcolorbox}
  - |
    \tcbset{
      colback=blue!10,
      colframe=blue!50,
      boxrule=0.5pt,
      arc=2mm,
      left=2mm,
      right=2mm,
      top=1mm,
      bottom=1mm
    }  
---

## Create the folders

```{r create folders, eval=FALSE}

dir.create("output")
dir.create("figures")
dir.create("reports")

```

## Load necessary libraries

```{r libraries, include = FALSE, warning=FALSE}

library(here)            # To manage project file paths reproducibly
library(dplyr)           # For data manipulation and wrangling
library(VIM)             # For KNN imputation and visualization of missing data
library(gtsummary)       # To create publication-ready summary and regression tables
library(flextable)       # To export  gtsummary tables in a Word Doc, ideal for gtsummary
library(ggplot2)         # For data visualization and plotting
library(survival)        # For survival analysis (Kaplan–Meier and Cox proportional hazards models)
library(survminer)       # For enhanced visualization of survival curves and reporting of log-rank tests
library(patchwork)       # To save Kaplan–Meier plots with risk tables, and eliminates alignment drift
library(MatchIt)         # For propensity score matching
library(readr)           # To read and write rectangular data files (e.g., CSV)
library(cobalt)          # To assess covariate balance and create Love plots
library(sensitivitymv)   # For Rosenbaum sensitivity analysis in matched studies with 1:k matching
library(purrr)           # To apply functions repeatedly over vectors, lists, or data frames without writing explicit loops.

library(sensitivitymult) # For Rosenbaum sensitivity analysis with Multiple  Outcomes
library(rbounds)     # For Rosenbaum sensitivity analysis in matched studies with 1:1 matching
library(EValue)      # For E-value sensitivity analysis: impact of unmeasured confounders on the observed treatment-outcome relationship.
library(geepack)     # For generalized estimating equations (GEE) models
library(pROC)        # For ROC curve analysis and AUC calculation
library(tidyr)       # For reshaping and tidying data
library(labelled)    # To manage variable labels and metadata


# library(tableone)    # To create descriptive “Table 1” baseline tables
# library(knitr)       # To create formatted tables in R Markdown/Quarto reports
# options(timeout = 600)
# set.seed(123) # Fixes the sequence of "random" operations = the same individuals are matched every time
# library(gridExtra)   # To save Kaplan–Meier plots with risk tables when `arrange_ggsurvplots()` fails, showed alignement issue between plot and risk table

```

## 1 Import data and define variables

```{r import, include = TRUE}

Outcome <- read.csv(
  here("data", "Outcome_data.csv"),
  header = TRUE,
  check.names = FALSE
)

Outcome <- Outcome %>%
  mutate(
    across(c(PID, QCODE), as.character),
    
    across(c(AGS, YEARS,BLDLOSS, BMI, CATHPERIOD, FUPM, HOSPTIME,OPRTIME,
             POSTUTIFUP, POSTUTI_T), as.numeric),
    
    across(c(REC011, ANASTOMO,BLDCOMPLEAK,BLDCOMPRETN,BLDCOMPVOID,BLDSPASM,CATH,CENTER,
             CLAVIENCLASS,EPIDURAL,GENDER, GU30, GU90N, GUER30, GUER90, HEMAT, 
             HISTOINJ,ILEUS, INCCOMPBLEED, INCCOMPINF, INCCOMPSCAR, NARC, 
             NONARC, PAIN, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR, PREOPTYPEU1,
             PREOPVURGRADE, PROC365, STENT, SURGIND, SURGTECH2, TRT2, UDR7M,
             URCOMPCVUR, URCOMPINJ, URCOMPOBST, URCOMPSTEN, POSTUTI, VURPHASE,
             VURSIDE, RECGRADE_MAX), as.factor)
  )

str(Outcome) # 412 obs. of 55 variables

```

## 2 Data Imputation using KNN (k-nearest neighbors)

```{r imputation, include = TRUE}

# Missingness in the dataset
m_outcome <- colSums(is.na(Outcome)) / nrow(Outcome) * 100
print(m_outcome)


# KNN imputation
Outcome_knn <- Outcome # create a temporary dataset copy for KNN using scaled variables

# Convert categorical variables
cat_vars <- c(
  "GENDER","PREOPVURGRADE", "VURPHASE","VURSIDE",
  "UDR7M","PREOPRNSCR","HISTOINJ","SURGIND",
  "CENTER","TRT2", "SURGTECH2",
  "PREOPEPISODE1", "PREOPRNPLN","PREOPTYPEU1"
)
Outcome_knn[cat_vars] <- lapply(Outcome_knn[cat_vars], as.factor)

# Scale continuous variables
continuous_vars <- c("AGS", "BMI", "YEARS")
Outcome_knn[continuous_vars] <- scale(Outcome_knn[continuous_vars])


# KNN imputation without subsetting the dataset
Outcome_knn <- kNN(
  Outcome_knn,
  variable = c("PREOPEPISODE1", "PREOPRNPLN", "PREOPTYPEU1"),  # Variables to impute
  dist_var = c("AGS","GENDER","BMI", # Variables used to compute patient similarity
    "PREOPVURGRADE","VURPHASE","VURSIDE","UDR7M",
    "PREOPRNSCR","HISTOINJ","SURGIND","YEARS",
    "TRT2"
  ),
  k = 5,
  imp_var = FALSE
)


# CENTER + TRT2 + SURGTECH2 together may overweight institutional structure, which means clustering patients by institution rather than biology → keep only one of them, I will keep "TRT2".

Out <- Outcome   # New dataset for analysis including imputed variables 

Out$PREOPEPISODE1 <- Outcome_knn$PREOPEPISODE1
Out$PREOPRNPLN   <- Outcome_knn$PREOPRNPLN
Out$PREOPTYPEU1  <- Outcome_knn$PREOPTYPEU1
```

## 3 Recode and create (composite) variables

```{r recode}

# Recode SURGIND into SURGIND2

Out <- Out %>%
  mutate(
    SURGIND2 = case_when(
      SURGIND == 4 ~ 1,
      SURGIND == 3 ~ 2,
      SURGIND == 1 ~ 3,
      SURGIND == 2 ~ 4,
      SURGIND %in% c(5, 6, 7, 8, 9, 10, 11) ~ 5,
      TRUE ~ NA_real_
    ),
    SURGIND2 = factor(SURGIND2)
  )


# Create a new variable LUTD by combining BLDCOMPRETN, BLDCOMPVOID, BLDCOMPLEAK
Out <- Out %>%
  mutate(
    LUTD = case_when(
      BLDCOMPRETN == 1 |
      BLDCOMPVOID == 1 |
      BLDCOMPLEAK == 1 ~ 1,

      BLDCOMPRETN == 0 &
      BLDCOMPVOID == 0 &
      BLDCOMPLEAK == 0 ~ 0,

      TRUE ~ NA_real_
    ),
    LUTD = factor(LUTD)
  )


# Create a new variable OBST by combining URCOMPOBST, URCOMPSTEN, ANASTOMO
Out <- Out %>%
  mutate(
    OBST = case_when(
      URCOMPOBST == 1 |
      URCOMPSTEN == 1 |
      ANASTOMO == 1 ~ 1,

      URCOMPOBST == 0 &
      URCOMPSTEN == 0 &
      ANASTOMO == 0 ~ 0,

      TRUE ~ NA_real_
    ),
    OBST = factor(OBST)
  )


# Create a new variable SURG by combining INCCOMPBLEED, INCCOMPINF, INCCOMPSCAR
Out <- Out %>%
  mutate(
    SURG = case_when(
      INCCOMPBLEED == 1 |
      INCCOMPINF == 1 |
      INCCOMPSCAR == 1 ~ 1,

      INCCOMPBLEED == 0 &
      INCCOMPINF == 0 &
      INCCOMPSCAR == 0 ~ 0,

      TRUE ~ NA_real_
    ),
    SURG = factor(SURG)
  )

# Create a new variable GU90 by combining no readmission (0) and unplanned readmission (2)
Out <- Out %>%
  mutate(
    GU90 = recode(as.character(GU90N),
                  "0" = "0",
                  "1" = "1",
                  "2" = "0"),
    GU90 = factor(GU90)
  )

# Convert variables to appropriate data types for analysis
Out <- Out %>%
  mutate(
    across(c(PID, QCODE), as.character),
    
    across(c(AGS, YEARS,BLDLOSS, BMI, CATHPERIOD, FUPM, HOSPTIME,OPRTIME,
             POSTUTIFUP, POSTUTI_T), as.numeric),
    
    across(c(REC011, ANASTOMO,BLDCOMPLEAK,BLDCOMPRETN,BLDCOMPVOID,BLDSPASM,CATH,CENTER,
             CLAVIENCLASS,EPIDURAL,GENDER, GU30, GU90N, GUER30, GUER90, HEMAT, 
             HISTOINJ,ILEUS, INCCOMPBLEED, INCCOMPINF, INCCOMPSCAR, NARC, 
             NONARC, PAIN, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR, PREOPTYPEU1,
             PREOPVURGRADE, PROC365, STENT, SURGIND, SURGTECH2, TRT2, UDR7M,
             URCOMPCVUR, URCOMPINJ, URCOMPOBST, URCOMPSTEN, POSTUTI, VURPHASE,
             VURSIDE, RECGRADE_MAX, SURGIND2, LUTD, OBST, SURG, GU90), as.factor)
  )

str(Out) # 412 obs. of 60 variables

```


## 4 Descriptive analysis: BEFORE matching

```{r descriptive, warning=FALSE}

# Baseline characteristics
table1<- Out %>%
  select(AGS, GENDER, BMI, HISTOINJ, SURGIND2, PREOPVURGRADE, VURSIDE, UDR7M, 
         VURPHASE, PREOPTYPEU1, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR,
         SURGTECH2, CENTER, TRT2
  ) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",  # shows missing only when present
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table1

table1 %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/baseline_before_matching.docx")



# Procedural factors
table2<- Out %>%
  select(TRT2, OPRTIME, STENT, CATH, CATHPERIOD, HOSPTIME) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})", # or ~ "{mean} ± {sd}",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table2

table2 %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/procedural_factors_before_matching.docx")


# Plot catheterization distribution
p <- ggplot(
  Out,
  aes(
    x = factor(
      TRT2,
      levels = c(0, 1),
      labels = c("Cohen Group", "Lich-Gregoir Group")
    ),
    y = CATHPERIOD
  )
) +
  geom_boxplot() +
  labs(
    x = "Treatment Group",
    y = "Catheterization Duration (days) Before Matching"
  ) +
  theme_bw()   #optional

ggsave(filename = "figures/catheterization_duration_before_matching.png", 
       plot = p, 
       width = 8,   # width in inches
       height = 6,  # height in inches
       dpi = 300)   # resolution



# Outcomes
table3<- Out %>%
  select(TRT2, FUPM, LUTD, OBST, URCOMPINJ, SURG, ILEUS, CLAVIENCLASS, URCOMPCVUR,
         GU30, GU90, GU90N, GUER30, GUER90, PROC365, 
         REC011, RECGRADE_MAX, 
         BLDLOSS, BLDSPASM, HEMAT, 
         POSTUTI) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})", # or ~ "{mean} ± {sd}",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table3

table3 %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/outcomes_before_matching.docx")


# Proportion plot for treatment across years (temporal changes in practice)
p_y <- ggplot(
  Out,
  aes(
    x = factor(YEARS),
    fill = factor(TRT2,
                  levels = c(0,1),
                  labels = c("Cohen Group", "Lich-Gregoir Group"))
  )
) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c(
    "Cohen Group" = "#ADD8E6",
    "Lich-Gregoir Group" = "#00008B"
  )) +
  labs(x = "Year of Surgery", y = "Proportion", fill = "Group") +
  theme_bw()

p_y

ggsave(filename = "figures/treatment_across_years_before_matching.png", 
       plot = p_y, 
       width = 8,   # width in inches
       height = 6,  # height in inches
       dpi = 300)   # resolution


######## Postoperative UTI outcome as time-to-event outcome

# Create labeled TRT2 variable only for survival analysis
Out$Treatment <- factor(
  Out$TRT2,
  levels = c(0,1),
  labels = c("Cohen", "Lich–Gregoir")
)

surv_object <- Surv(time = Out$POSTUTIFUP, event = Out$POSTUTI== 1)
fit <- survfit(surv_object ~ Treatment , data = Out)

p_u <- ggsurvplot(
  fit,
  data = Out,
  fun="event",  # Show cumulative incidence (1 - survival)
  pval = TRUE,
  pval.size = 4,
  conf.int = TRUE,
  risk.table = TRUE,

  xlim = c(0, 135),
  break.time.by = 12,

  xlab = "Follow-up time",
  ylab = "Cumulative incidence of 
      postopetative symptomatic UTI before matching",

  risk.table.y.text = FALSE,   # to remove text from y-axis in the risk table
  # risk.table.title = "At risk",
  risk.table.fontsize = 4,   # ontrols numbers in table

  palette = c("#ADD8E6", "#00008B"),
  ylim = c(0, 1),  # Force y-axis from 0 to 1

  pval.coord = c(0, 0.9)  #  c(x,y) according to my x and y scale

)

# To modify the plot
p_u$plot <- p_u$plot + scale_x_continuous(limits = c(0, 135), breaks = seq(0, 135, 12))
p_u$plot <- p_u$plot +
  scale_y_continuous(
    labels = function(x) paste0(round(x * 100, 1), "%"),
    limits = c(0, 1)
  )
p_u$plot <- p_u$plot +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10)
  )

# To modify the risk table
p_u$table <- p_u$table + scale_x_continuous(limits = c(0, 135), breaks = seq(0, 135, 12))
p_u$table <- p_u$table +                 
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.line.x = element_blank(),
    axis.line.y = element_blank()
  )
p_u$table <- p_u$table +
  theme(
    plot.title = element_text(size = 12),
    text = element_text(size = 10),
    axis.title.y = element_text(size = 12),
  )
# To save plot and risk table using patchwork
# ggsave() only works with a single ggplot object.
final_plot <- p_u$plot / p_u$table + plot_layout(heights = c(4, 1))
ggsave(filename = "figures/UTI_outcome_before_matching.png", final_plot, width = 8, height = 6, dpi = 300)

```


## 5 Pain descriptive analysis: BEFORE matching

```{r pain}

# Filter dataset to only those who did not receive EPIDURAL
Outp <- Out %>%
  filter(EPIDURAL == "0") %>%
  mutate(
    PAIN = factor(
      PAIN,
      levels = c("0", "1", "2", "3"),
      labels = c(
        "No pain",
        "Mild pain (score 1-3)",
        "Moderate pain (score 4-6)",
        "Severe pain (score 7-10)"
      )
    )
  )

table4 <- Outp %>%
  select(PAIN, NARC, NONARC, Treatment) %>%
  tbl_summary(
    by = Treatment,
    statistic = list(
      all_categorical() ~ "{n} ({p}%)"
    ),
    label = list(
      PAIN ~ "Pain score",
      NARC ~ "Narcotic use",
      NONARC ~ "Non-narcotic use"
    ),
    digits = all_categorical() ~ c(0, 1),
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%
  bold_labels()

table4

table4 %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/pain_before_matching.docx")
```

## 6 Do matching

```{r matching, warning=FALSE}

# Fit matching model using propensity score (calculated inside MatchIt)

set.seed(123) # Fixes the sequence of "random" operations = the same individuals are matched every time
 
m.out <- matchit(
  TRT2 ~ AGS + YEARS + GENDER + BMI + PREOPRNPLN + HISTOINJ +
    SURGIND2 + PREOPVURGRADE + VURSIDE + UDR7M + VURPHASE +
    PREOPEPISODE1 + PREOPTYPEU1 + PREOPRNSCR + SURGTECH2,
  data = Out,
  method = "nearest",
  ratio = 3,  # 1:3 matching (1 treated : 3 control), it is up to 3 controls, not necessarily 3 controls for each treated
  distance = "logit",
# caliper should be a numeric value in MatchIt
# This means: 0.2 SD of the logit of PS (MatchIt interprets correctly)
   caliper = 0.2   # A caliper = maximum allowed distance between treated and control, Caliper = 0.2 SD of the logit of the propensity score (Austin, 2011 recommendation)
)


# When the variance of the linear propensity score in the treatment group is twice as large as that in the control group, a caliper of 0.2 standard deviations removes 98% of the bias in a normally distributed covariate. If the variance in the treatment group is much larger than that in the control group, smaller calipers are necessary.

mdata <- match.data(m.out)    # Extract the matched dataset with columns: distance(PS), weights, subclass
# weights = how much each matched subject contributes in analysis
# In 1:1 matching, weights usually = 1
# you can ignore weights in further analysis, but using them is safer and more standard
# glm(outcome ~ TRT2, data = mdata, weights = weights) (standard) or glm(outcome ~ TRT2, data = mdata)

readr::write_csv(mdata, "data/matched_data.csv")  
# write.csv() = base R, simple, works everywhere: write.csv(mdata, file = "data/matched_data.csv", row.names = FALSE)
# write_csv() = modern, faster, cleaner, recommended for research workflows 


# Table for balance
# This gives: SMD before and after matching, and flagged imbalance (>0.1)
bal <- cobalt::bal.tab(m.out, un = TRUE, m.threshold = 0.1)  
# un=TRUE shows imbalance before AND after matching, un=FALSE shows only after matching
bal 

bal_df <- as.data.frame(bal$Balance)
smd_table <- bal_df %>%
  mutate(
    Variable = rownames(bal_df),
    SMD_Before = round(abs(Diff.Un), 3),
    SMD_After  = round(abs(Diff.Adj), 3)
  ) %>%
  select(Variable, SMD_Before, SMD_After) # SMDs for each covariate individually, before and after matching

smd_table %>%
  flextable() %>%
  save_as_docx(path = "output/SMD_table.docx")


# Figure for balance - Love plot
# Review guidelines to decide on plotting Standardized or Absolute Mean Differences
pl <- love.plot(
  m.out,
  threshold = 0.1,
  abs = FALSE, # As SMD sign is meaningless for balance, show only absolute SMDs using abs = TRUE (the correct interpretation of SMD): Because SMD direction (+/-) is meaningless, only magnitude matters
  stats = "mean.diffs",       # forces SMD instead of raw differences
  var.order = "unadjusted",   # Orders variables based on imbalance before matching
  drop.distance = TRUE,      # To exclude the distance from the plot
  sample.names = c("Before Matching", "After Matching"),
    var.names = c(
    AGS = "Age at surgery",
    YEARS = "Year of surgery",
    BMI = "Body mass index",
    GENDER = "Female gender",
    PREOPRNPLN = "Preop pyelonephritis",
    HISTOINJ = "History of injection",
    VURSIDE = "Right-sided VUR",
    UDR7M = "Ureteral dilation ≥ 7mm",
    PREOPTYPEU1 = "Preop febrile UTIs",
    PREOPRNSCR = "Preop renal scarring",
    VURPHASE_1 = "Reflux: voiding phase",
    VURPHASE_2 = "Reflux: filling phase",
    VURPHASE_3 = "Reflux: filling + voiding",
    SURGTECH2_1 = "Surgeon experience ≥100 operations",
    SURGTECH2_2 = "Surgeon experience 50-100 operations",
    SURGTECH2_3 = "Surgeon experience <50 operations",
    PREOPEPISODE1_1 = "Preop UTI episodes: 1",
    PREOPEPISODE1_2 = "Preop UTI episodes: 2",
    PREOPEPISODE1_3 = "Preop UTI episodes: ≥3",
    SURGIND2_1 = "Indication: breakthrough UTI",
    SURGIND2_2 = "Indication: high-grade reflux (III-V)",
    SURGIND2_3 = "Indication: poor compliance to medical treatment",
    SURGIND2_4 = "Indication: ineffective/poorly tolerated CAP",
    SURGIND2_5 = "Indication: other",
    PREOPVURGRADE_3 = "Preop VUR grade: III",
    PREOPVURGRADE_4 = "Preop VUR grade: IV",
    PREOPVURGRADE_5 = "Preop VUR grade: V"
  )
  )

pl <- pl +
    labs(x = "Standardized Mean Differences") +
    theme(
      plot.margin = margin(10, 10, 10, 10),
      axis.text = element_text(size = 16),
      axis.title = element_text(size = 16),
      plot.title = element_text(size = 16),
      legend.text = element_text(size = 16),
      legend.title = element_text(size = 16),
      axis.ticks = element_line(size = 0.5, color = "black"),
      axis.line = element_line(size = 0.5, color = "black"),
      panel.background = element_blank(), 
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      axis.ticks.length = unit(0.3, "cm"),
      panel.spacing = unit(2, "lines")
   )

ggsave ("figures/love_plot.png", plot = pl, width = 12, height = 10, dpi = 300)


# To save the plot with white background, if requested for publication
# ggsave(
#   "figures/love_plot.png",
#   plot = pl,
#   width = 12,
#   height = 10,
#   dpi = 300,
#   bg = "white"
# )


# Note: A propensity score should include: only baseline variables measured before treatment assignment

# “Distance” in the Love plot is the propensity score itself, included to show how well matching balanced the overall treatment assignment mechanism.
# Reviewers mainly check:
## All covariates < 0.1 after matching
## Distance reduced substantially
## Visual improvement in Love plot
# many papers exclude distance because: It is not a confounder, it is a derived variable, it often has very large pre-match imbalance (can visually dominate plot), it adds little clinical interpretation


# Compute mean SMD
smd_df <- bal$Balance
mean_smd_before <- mean(abs(smd_df$Diff.Un), na.rm = TRUE) # calculate mean SMD before matching
mean_smd_after <- mean(abs(smd_df$Diff.Adj), na.rm = TRUE) # calculate mean SMD before matching
mean_smd <- data.frame(
  Mean_SMD_Before = mean_smd_before,
  Mean_SMD_After = mean_smd_after
)

mean_smd

# Best reporting practices
# “All covariates had SMD < 0.1 (threshold) after matching": Covariate balance was assessed using standardized mean differences (SMD), with values < 0.1 indicating adequate balance.
# (optionally) “Mean absolute SMD decreased from X to Y”: It is acceptable as a summary metric but not a replacement for individual SMDs

```


## 7 Descriptive analysis: AFTER matching

```{r descriptive, warning=FALSE}

# The following descriptive tables are correct for matching without replacement.
# For matching with replacment, some papers report the characteristics of the unique matched individuals (unweighted matched subjects). This answers: "Who was retained after matching?" It is acceptable, especially if the authors explicitly state that matching was performed with replacement. However, it does not represent the analytical contribution of each subject.
# For matching with replacment, weighted descriptive statistics summarize the matched pseudo-population. This reflects the actual population analyzed.


# Baseline characteristics
table1m<- mdata %>%
  select(AGS, GENDER, BMI, HISTOINJ, SURGIND2, PREOPVURGRADE, VURSIDE, UDR7M, 
         VURPHASE, PREOPTYPEU1, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR,
         SURGTECH2, CENTER, TRT2
  ) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",  # shows missing only when present
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table1m

table1m %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/baseline_after_matching.docx")



# Procedural factors
table2m<- mdata %>%
  select(TRT2, OPRTIME, STENT, CATH, CATHPERIOD, HOSPTIME) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})", # or ~ "{mean} ± {sd}",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table2m

table2m %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/procedural_factors_after_matching.docx")


# Plot catheterization distribution
p_m <- ggplot(
  mdata,
  aes(
    x = factor(
      TRT2,
      levels = c(0, 1),
      labels = c("Cohen Group", "Lich-Gregoir Group")
    ),
    y = CATHPERIOD
  )
) +
  geom_boxplot() +
  labs(
    x = "Treatment Group",
    y = "Catheterization Duration (days) After Matching"
  ) +
  theme_bw()   #optional

ggsave(filename = "figures/catheterization_duration_after_matching.png", 
       plot = p_m, 
       width = 8,   # width in inches
       height = 6,  # height in inches
       dpi = 300)   # resolution



# Outcomes
table3m<- mdata %>%
  select(TRT2, FUPM, LUTD, OBST, URCOMPINJ, SURG, ILEUS, CLAVIENCLASS, URCOMPCVUR,
         GU30, GU90, GU90N, GUER30, GUER90, PROC365, 
         REC011, RECGRADE_MAX, 
         BLDLOSS, BLDSPASM, HEMAT, 
         POSTUTI) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})", # or ~ "{mean} ± {sd}",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table3m

table3m %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/outcomes_after_matching.docx")


# Proportion plot for treatment across years (temporal changes in practice)
p_y_m <- ggplot(
  mdata,
  aes(
    x = factor(YEARS),
    fill = factor(TRT2,
                  levels = c(0,1),
                  labels = c("Cohen Group", "Lich-Gregoir Group"))
  )
) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c(
    "Cohen Group" = "#ADD8E6",
    "Lich-Gregoir Group" = "#00008B"
  )) +
  labs(x = "Year of Surgery", y = "Proportion", fill = "Group") +
  theme_bw()

p_y_m

ggsave(filename = "figures/treatment_across_years_after_matching.png", 
       plot = p_y_m, 
       width = 8,   # width in inches
       height = 6,  # height in inches
       dpi = 300)   # resolution


######## Postoperative UTI outcome as time-to-event outcome

# Create labeled TRT2 variable only for survival analysis
mdata$Treatment <- factor(
  mdata$TRT2,
  levels = c(0,1),
  labels = c("Cohen", "Lich–Gregoir")
)

surv_object <- Surv(time = mdata$POSTUTIFUP, event = mdata$POSTUTI== 1)
fit <- survfit(surv_object ~ Treatment , data = mdata)

p_u_m <- ggsurvplot(
  fit,
  data = mdata,
  fun="event",  # Show cumulative incidence (1 - survival)
  pval = TRUE,
  pval.size = 4,
  conf.int = TRUE,
  risk.table = TRUE,

  xlim = c(0, 135),
  break.time.by = 12,

  xlab = "Follow-up time",
  ylab = "Cumulative incidence of 
      postopetative symptomatic UTI after matching",

  risk.table.y.text = FALSE,   # to remove text from y-axis in the risk table
  # risk.table.title = "At risk",
  risk.table.fontsize = 4,   # ontrols numbers in table

  palette = c("#ADD8E6", "#00008B"),
  ylim = c(0, 1),  # Force y-axis from 0 to 1

  pval.coord = c(0, 0.9)  #  c(x,y) according to my x and y scale

)

# To modify the plot
p_u_m$plot <- p_u_m$plot + scale_x_continuous(limits = c(0, 135), breaks = seq(0, 135, 12))
p_u_m$plot <- p_u_m$plot +
  scale_y_continuous(
    labels = function(x) paste0(round(x * 100, 1), "%"),
    limits = c(0, 1)
  )
p_u_m$plot <- p_u_m$plot +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10)
  )

# To modify the risk table
p_u_m$table <- p_u_m$table + scale_x_continuous(limits = c(0, 135), breaks = seq(0, 135, 12))
p_u_m$table <- p_u_m$table +                 
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.line.x = element_blank(),
    axis.line.y = element_blank()
  )
p_u_m$table <- p_u_m$table +
  theme(
    plot.title = element_text(size = 12),
    text = element_text(size = 10),
    axis.title.y = element_text(size = 12),
  )
# To save plot and risk table using patchwork
# ggsave() only works with a single ggplot object.
final_plot_m <- p_u_m$plot / p_u_m$table + plot_layout(heights = c(4, 1))
ggsave(filename = "figures/UTI_outcome_after_matching.png", final_plot_m, width = 8, height = 6, dpi = 300)

```


## 8 Pain descriptive analysis: AFTER matching

```{r pain}

# Filter dataset to only those who did not receive EPIDURAL
mdatap <- mdata %>%
  filter(EPIDURAL == "0") %>%
  mutate(
    PAIN = factor(
      PAIN,
      levels = c("0", "1", "2", "3"),
      labels = c(
        "No pain",
        "Mild pain (score 1-3)",
        "Moderate pain (score 4-6)",
        "Severe pain (score 7-10)"
      )
    )
  )

table4m <- mdatap %>%
  select(PAIN, NARC, NONARC, Treatment) %>%
  tbl_summary(
    by = Treatment,
    statistic = list(
      all_categorical() ~ "{n} ({p}%)"
    ),
    label = list(
      PAIN ~ "Pain score",
      NARC ~ "Narcotic use",
      NONARC ~ "Non-narcotic use"
    ),
    digits = all_categorical() ~ c(0, 1),
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%
  bold_labels()

table4m



table4m %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/pain_after_matching.docx")


# MERGE TABLES
table_combined <- tbl_merge(
  tbls = list(table4, table4m),
  tab_spanner = c("**Before Matching**", "**After Matching**")
) %>%
  modify_caption(
    "Table 4. Comparison of pain intensity and analgesic use between treatment groups before and after propensity score matching."
) %>%
  modify_source_note(
    "Analysis restricted to patients not receiving epidural analgesia."
  )

table_combined

table_combined %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/pain_before_after.docx")

```

## 9 Pain distribution: BEFORE-AFTER matching - Non-epidural Cohort

```{r painplot}

# label datasets
before <- Outp %>%
  mutate(MatchingStatus = "Before matching (N=383), p<0.001")

after <- mdatap %>%
  mutate(MatchingStatus = "After matching (N=219), p<0.001")

# Combine
plot_data <- bind_rows(before, after)


# pain labels
plot_data <- plot_data %>%
  mutate(
    PAIN_plot = factor(
      PAIN,
      levels = levels(PAIN),
      labels = c("No pain", "Mild pain", "Moderate pain", "Severe pain")
    )
  )

# To define order of data
plot_data <- plot_data %>%
  mutate(
    MatchingStatus = factor(
      MatchingStatus,
      levels = c(
        "Before matching (N=383), p<0.001",
        "After matching (N=219), p<0.001"
      )
    )
  )

# `MatchingStatus` is a character, so ggplot orders it alphabetically:
# "After matching..." → comes first (A)
# "Before matching..." → comes second (B)
# That’s why "After matching" appears on the left → we need to order factor levels to see "After" on the rigt

# Pain distribution stacked by Treatment (within facet)

# summary
plot_summary <- plot_data %>%
  group_by(MatchingStatus, Treatment, PAIN_plot) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(MatchingStatus, Treatment) %>%
  mutate(Percent = 100 * n / sum(n))


s0 <- ggplot(plot_summary, 
             aes(x = PAIN_plot, y = Percent, fill = Treatment)) +
  geom_bar(stat = "identity", position = "stack") + 
  facet_wrap(~MatchingStatus) +
  labs(x = "
       1-Day Postoperative Pain Score", 
       y = "Percentage of Patients not receiving epidural analgesia (%)") +
  scale_fill_manual(values = c(
    "Cohen" = "#ADD8E6", 
    "Lich–Gregoir" = "#00008B"), 
    name = NULL) +
  scale_y_continuous(limits = c(0, 100)) +  
  theme_minimal() +
  theme(
    panel.grid = element_blank(),  # Remove gridlines
    axis.title = element_text(size = 14),  # Set axis labels size
    axis.text = element_text(size = 8),  # Set axis text size
    panel.border = element_rect(color = "black", fill = NA),  # Add frame to the plot
    plot.title = element_text(hjust = 0.5, size = 16),  # Center the title
    axis.ticks = element_line(size = 0.5, color = "black"),  # Set tick line properties
    axis.ticks.length = unit(-0.2, "cm"),  # Move ticks inside the plot
    axis.text.y = element_text(size = 12),  # Adjust the y-axis text size
    panel.spacing = unit(0, "lines")  # Reduce space between panels
  )

ggsave(filename = "figures/pain_before_after_matching.png", 
       plot = s0, 
       width = 8,   # width in inches
       height = 6,  # height in inches
       dpi = 300)   # resolution


# 100% stacked grouped bar plot

# summary
plot_summary1 <- plot_data %>%
  group_by(MatchingStatus, Treatment, PAIN) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(MatchingStatus, Treatment) %>%
  mutate(Percent = 100 * n / sum(n))

s1 <- ggplot(plot_summary1,
            aes(x = Treatment, y = Percent, fill = PAIN)) +
  geom_bar(stat = "identity", position = "fill", width = 0.7) +
  facet_wrap(~MatchingStatus) +
  labs(
    x = "
    Treatment groups",
    y = "Percentage of patients not receiving epidural analgesia (%)",
    fill = "1-Day postoperative pain score"
  ) +
  scale_fill_manual(values = c(
  "No pain" = "#f5f5f5",  # Intead of pure white "#ffffff"
  "Mild pain (score 1-3)" = "#fee8c8",
  "Moderate pain (score 4-6)" = "#fdbb84",
  "Severe pain (score 7-10)" = "#e34a33"
  )) +
  scale_y_continuous(labels = scales::percent_format(scale = 100)) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 11),
    panel.border = element_rect(color = "black", fill = NA),
    strip.text = element_text(face = "bold"),
    panel.spacing = unit(0, "lines")
  )

ggsave(
  filename = "figures/pain_grouped_stacked.png",
  plot = s1,
  width = 8,
  height = 6,
  dpi = 300
)


# Title: Distribution of pain intensity (score) in treatment groups
```


## 10 Rosenbaum's sensitivity analyses 

```{r sensitivitymv}

mdata <- match.data(m.out)  


## One unified sensitivity-analysis framework applied separately but consistently across multiple outcomes.
  

# Define outcomes
outcomes <- c("LUTD", "OBST", "URCOMPINJ", "SURG", "ILEUS", "GU30", "GU90", "PROC365")

# Prepare matched sets (1:k)
mdata <- match.data(m.out)
mdata$TRT2 <- as.numeric(mdata$TRT2)
sets <- split(mdata, mdata$subclass)

# Create a reusable function
run_sensitivity_one_outcome <- function(outcome_var, Gamma_seq) {
  
  results <- data.frame()
  
  # build Y/Z for sensitivitymv
  Y <- list()
  Z <- list()
  
  for (i in seq_along(sets)) {
    
    df <- sets[[i]]
    
    if(length(unique(df$TRT2)) < 2) next
    
    Y[[i]] <- df[[outcome_var]]
    Z[[i]] <- df$TRT2
  }
  
  # loop over Gamma
  for (g in Gamma_seq) {
    
    res <- senmv(
      ylist = Y,
      zlist = Z,
      gamma = g,
      alternative = "greater"
    )
    
    results <- rbind(results,
                     data.frame(
                       outcome = outcome_var,
                       Gamma = g,
                       p_value = res$pval
                     ))
  }
  
  return(results)
}

# Run all outcomes under SAME Γ grid
Gamma_seq <- seq(1, 3, by = 0.2)

all_results <- bind_rows(
  lapply(outcomes, run_sensitivity_one_outcome, Gamma_seq = Gamma_seq)
)

# Summarize robustness per outcome
summary_table <- all_results %>%
  group_by(outcome) %>%
  summarise(
    max_gamma_significant = max(Gamma[p_value < 0.05], na.rm = TRUE)
  )

summary_table


# Apply Bonferroni adjustment
  
all_results
# columns: outcome, Gamma, p_value

# Define number of outcomes
K <- length(unique(all_results$outcome))

# Apply Bonferroni per Gamma level
all_results_bonf <- all_results %>%
  mutate(p_bonf = pmin(p_value * K, 1))

# Interpret robustness under Γ
robustness <- all_results_bonf %>%
  group_by(outcome) %>%
  summarise(
    max_gamma_bonf = max(Gamma[p_bonf < 0.05], na.rm = TRUE)
  )

robustness

# Global Bonferroni decision
global_results <- all_results_bonf %>%
  group_by(Gamma) %>%
  summarise(min_p = min(p_bonf)) %>%
  mutate(global_significant = min_p < 0.05)

max_gamma_global <- max(global_results$Gamma[global_results$global_significant])
max_gamma_global

```


## 11 E-value

```{r evalue}

# E-value explains away a specific treatment–outcome association.
# Code to compute E-value and its confidence interval
# “Default E-value (vs null)” is simply the standard output when true = 1 (implicitly)
# For "Non-null E-value (shifted)", use true = ....
# The E-value for the confidence interval was computed using the limit closest to the null value.
evalues.OR(est = OR, lo = CI_lower, hi = CI_upper,  rare = TRUE) # rare=TRUE means outcome prevalence <15%

38.84 (15.4 - 97.7)
0.48 (0.36 - 0.63)
evalues.OR(est = 0.48,
           lo = 0.36,
           hi = 0.63,
           rare = TRUE)

# If using Cox regression
evalues.HR(est, lo, hi)

```



# DRAFT

## Pain descriptive and distribution: BEFORE-AFTER matching - Epidural cohort

```{r}

# Descriptive 

# Filter dataset to only those who did not receive EPIDURAL
Outp1 <- Out %>%
  filter(EPIDURAL == "1") %>%
  mutate(
    PAIN = factor(
      PAIN,
      levels = c("0", "1", "2", "3"),
      labels = c(
        "No pain",
        "Mild pain (score 1-3)",
        "Moderate pain (score 4-6)",
        "Severe pain (score 7-10)"
      )
    )
  )

table41 <- Outp1 %>%
  select(PAIN, NARC, NONARC, Treatment) %>%
  tbl_summary(
    by = Treatment,
    statistic = list(
      all_categorical() ~ "{n} ({p}%)"
    ),
    label = list(
      PAIN ~ "Pain score",
      NARC ~ "Narcotic use",
      NONARC ~ "Non-narcotic use"
    ),
    digits = all_categorical() ~ c(0, 1),
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%
  bold_labels()

table41

table41 %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/pain_before_matching_epidural.docx")

# ------------------------------

# Filter dataset to only those who did not receive EPIDURAL
mdatap1 <- mdata %>%
  filter(EPIDURAL == "1") %>%
  mutate(
    PAIN = factor(
      PAIN,
      levels = c("0", "1", "2", "3"),
      labels = c(
        "No pain",
        "Mild pain (score 1-3)",
        "Moderate pain (score 4-6)",
        "Severe pain (score 7-10)"
      )
    )
  )


table4m1 <- mdatap1 %>%
  select(PAIN, NARC, NONARC, Treatment) %>%
  tbl_summary(
    by = Treatment,
    statistic = list(
      all_categorical() ~ "{n} ({p}%)"
    ),
    label = list(
      PAIN ~ "Pain score",
      NARC ~ "Narcotic use",
      NONARC ~ "Non-narcotic use"
    ),
    digits = all_categorical() ~ c(0, 1),
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%
  bold_labels()

table4m1

table4m1 %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/pain_after_matching_epidural.docx")


# MERGE TABLES
table_combined1 <- tbl_merge(
  tbls = list(table41, table4m1),
  tab_spanner = c("**Before Matching**", "**After Matching**")
) %>%
  modify_caption(
    "Table 4. Comparison of pain intensity and analgesic use between treatment groups before and after propensity score matching."
) %>%
  modify_source_note(
    "Analysis restricted to patients receiving epidural analgesia."
  )

table_combined1

table_combined1 %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/pain_before_after_epidural.docx")

# --------------------------------

# Distribution


# label datasets
before1 <- Outp1 %>%
  mutate(MatchingStatus = "Before matching (N=383), p<0.001")

after1 <- mdatap1 %>%
  mutate(MatchingStatus = "After matching (N=219), p<0.001")

# Combine
plot_data1 <- bind_rows(before1, after1)


# pain labels
plot_data1 <- plot_data1 %>%
  mutate(
    PAIN_plot = factor(
      PAIN,
      levels = levels(PAIN),
      labels = c("No pain", "Mild pain", "Moderate pain", "Severe pain")
    )
  )

# To define order of data
plot_data1 <- plot_data1 %>%
  mutate(
    MatchingStatus = factor(
      MatchingStatus,
      levels = c(
        "Before matching (N=383), p<0.001",
        "After matching (N=219), p<0.001"
      )
    )
  )


# Pain distribution stacked by Treatment (within facet)

# summary
plot_summary0 <- plot_data1 %>%
  group_by(MatchingStatus, Treatment, PAIN_plot) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(MatchingStatus, Treatment) %>%
  mutate(Percent = 100 * n / sum(n))


s01 <- ggplot(plot_summary0, 
             aes(x = PAIN_plot, y = Percent, fill = Treatment)) +
  geom_bar(stat = "identity", position = "stack") + 
  facet_wrap(~MatchingStatus) +
  labs(x = "
       1-Day Postoperative Pain Score", 
       y = "Percentage of Patients (%)") +
  scale_fill_manual(values = c(
    "Cohen" = "#ADD8E6", 
    "Lich–Gregoir" = "#00008B"), 
    name = NULL) +
  scale_y_continuous(limits = c(0, 100)) +  
  theme_minimal() +
  theme(
    panel.grid = element_blank(),  # Remove gridlines
    axis.title = element_text(size = 14),  # Set axis labels size
    axis.text = element_text(size = 8),  # Set axis text size
    panel.border = element_rect(color = "black", fill = NA),  # Add frame to the plot
    plot.title = element_text(hjust = 0.5, size = 16),  # Center the title
    axis.ticks = element_line(size = 0.5, color = "black"),  # Set tick line properties
    axis.ticks.length = unit(-0.2, "cm"),  # Move ticks inside the plot
    axis.text.y = element_text(size = 12),  # Adjust the y-axis text size
    panel.spacing = unit(0, "lines")  # Reduce space between panels
  )

ggsave(filename = "figures/pain_before_after_matching_epidural.png", 
       plot = s01, 
       width = 8,   # width in inches
       height = 6,  # height in inches
       dpi = 300)   # resolution

# -----------------------------------------

# 100% stacked grouped bar plot

# summary
plot_summary11 <- plot_data1 %>%
  group_by(MatchingStatus, Treatment, PAIN) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(MatchingStatus, Treatment) %>%
  mutate(Percent = 100 * n / sum(n))

s11 <- ggplot(plot_summary11,
            aes(x = Treatment, y = Percent, fill = PAIN)) +
  geom_bar(stat = "identity", position = "fill", width = 0.7) +
  facet_wrap(~MatchingStatus) +
  labs(
    x = "
    Treatment groups",
    y = "Percentage of patients (%)",
    fill = "1-Day postoperative pain score"
  ) +
  scale_fill_manual(values = c(
  "No pain" = "#f5f5f5",
  "Mild pain (score 1-3)" = "#fee8c8",
  "Moderate pain (score 4-6)" = "#fdbb84",
  "Severe pain (score 7-10)" = "#e34a33"
  )) +
  scale_y_continuous(labels = scales::percent_format(scale = 100)) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 11),
    panel.border = element_rect(color = "black", fill = NA),
    strip.text = element_text(face = "bold"),
    panel.spacing = unit(0, "lines")
  )

ggsave(
  filename = "figures/pain_grouped_stacked_epidural.png",
  plot = s11,
  width = 8,
  height = 6,
  dpi = 300
)


```

##  Rosenbaum's draft

```{r rosenbaum}

str(mdata)

Outcomes:
LUTD, OBST, URCOMPINJ, SURG, ILEUS, GU30, GU90, PROC365,

POSTUTI

GU90N, GUER30, GUER90, 
CLAVIENCLASS, URCOMPCVUR,
         REC011, RECGRADE_MAX, 
         BLDLOSS, BLDSPASM, HEMAT, 


# For the binary outcome LUTD, and m.out is the MatchIt object 
# Extract matched pairs for outcomes
m.pairs <- cbind(
    mdata[row.names(m.out$match.matrix), 'LUTD'],  
    mdata[m.out$match.matrix, 'LUTD']
)
m.pairs <- na.omit(m.pairs) # filter pairs who did not get matched (NA values)
print(m.pairs)
head(m.pairs) # Check the structure of matched pairs

# Count discordant pairs = pairs where one unit (treated or control) has the outcome, but the other does not.
x <- sum((m.pairs[, 1] == 0) & (m.pairs[, 2] == 1)) # x represent the number of pairs where the control has the outcome, but the treated does not.
y <- sum((m.pairs[, 1] == 1) & (m.pairs[, 2] == 0)) # y represent the number of pairs where the treated has the outcome, but the control does not.
print(x)
print(y) 

# Perform Rosenbaum primal sensitivity analysis
primal <- binarysens(x=x, y=y, Gamma = 15, GammaInc = 2)
print(primal)

-----------------------------------------------------------------------

## Rosenbaum sensitivity analysis workflow for 1:k matching
library(MatchIt)
library(dplyr)

# Extract matched dataset with subclass (matched set ID)
matched_data <- match.data(m.out)

# Keep only needed variables
dat <- matched_data %>%
  select(subclass, treatment, LUTD)

# Ensure treatment is 0/1
dat$treatment <- as.numeric(dat$treatment)

# Split by matched sets
sets <- split(dat, dat$subclass)

# We build a score-like statistic
library(purrr)

set_stats <- map(sets, function(df) {
  
  # treated and control outcomes
  y_treat <- df$LUTD[df$treatment == 1]
  y_ctrl  <- df$LUTD[df$treatment == 0]
  
  # handle 1:k structure
  if(length(y_treat) == 0 | length(y_ctrl) == 0) return(NULL)
  
  # pairwise comparisons within set
  # (treated vs all controls average contribution)
  
  stat <- mean(y_treat) - mean(y_ctrl)
  
  return(stat)
})

set_stats <- unlist(set_stats)


# Convert to Rosenbaum-style test statistic
T_obs <- sum(set_stats, na.rm = TRUE)

# Sensitivity analysis (Γ model)
Gamma <- 2  # example sensitivity level

# worst-case weighting within sets
worst_case_stat <- map_dbl(sets, function(df) {
  
  y_treat <- df$LUTD[df$treatment == 1]
  y_ctrl  <- df$LUTD[df$treatment == 0]
  
  if(length(y_treat) == 0 | length(y_ctrl) == 0) return(0)
  
  # worst-case allocation logic (simplified Rosenbaum bound idea)
  weight_t <- Gamma / (1 + Gamma)
  weight_c <- 1 / (1 + Gamma)
  
  (weight_t * mean(y_treat)) - (weight_c * mean(y_ctrl))
})

T_gamma <- sum(worst_case_stat)


# Loop over Γ values
Gamma_seq <- seq(1, 3, by = 0.2)

results <- data.frame()

for(g in Gamma_seq) {
  
  worst_case <- map_dbl(sets, function(df) {
    
    y_treat <- df$LUTD[df$treatment == 1]
    y_ctrl  <- df$LUTD[df$treatment == 0]
    
    if(length(y_treat) == 0 | length(y_ctrl) == 0) return(0)
    
    w_t <- g / (1 + g)
    w_c <- 1 / (1 + g)
    
    (w_t * mean(y_treat)) - (w_c * mean(y_ctrl))
  })
  
  T_g <- sum(worst_case)
  
  results <- rbind(results,
                   data.frame(Gamma = g,
                              test_stat = T_g))
}

# Interpretation: You report: largest Γ where conclusion still holds robustness threshold

-----------------------------------------------------------------------

## Rosenbaum's sensitivity analysis using `sensitivitymv` package

library(sensitivitymv)

# Extract matched data correctly (1:k preserved)
matched_data <- match.data(m.out)

dat <- matched_data %>%
  select(subclass, treatment, LUTD)

dat$treatment <- as.numeric(dat$treatment)
dat$LUTD <- as.numeric(dat$LUTD)

# Split into matched sets
sets <- split(dat, dat$subclass)

# Create sensitivitymv input structure
library(purrr)

Y <- list()   # outcomes per set
Z <- list()   # treatment indicators per set

for (i in seq_along(sets)) {
  
  df <- sets[[i]]
  
  # skip incomplete sets
  if(length(unique(df$treatment)) < 2) next
  
  Y[[i]] <- df$LUTD
  Z[[i]] <- df$treatment
}

# Run Rosenbaum sensitivity analysis (1:k matched sets): for binary outcomes, the common approach is using score-type test statistics inside matched sets.

# Example structure (function name depends on version)
result <- senmv(
  ylist = Y,
  zlist = Z,
  gamma = 1,
  alternative = "greater"
)

Gamma_seq <- seq(1, 3, by = 0.2)

results <- data.frame()

for (g in Gamma_seq) {
  
  res <- senmv(
    ylist = Y,
    zlist = Z,
    gamma = g,
    alternative = "greater"
  )
  
  results <- rbind(results,
                   data.frame(Gamma = g,
                              p_value = res$pval))
}

results
max_gamma <- max(results$Gamma[results$p_value < 0.05])
max_gamma

# Interpretation: You report: smallest p-value across Γ or largest Γ where p < 0.05

# For multiple outcomes: You should run Rosenbaum's method separately per outcome → then adjust for multiplicity or Move to joint methods (like sensitivitymult or QCLP papers) (advanced)


-----------------------------------------------------------------------------------------------------------

```