---
title: "Outcome_analysis"
author: "Khadija Ismail"
date: "`r Sys.Date()`"
format:
  pdf:
    documentclass: article
    geometry: margin=1in
    code-overflow: wrap
    latex-engine: xelatex  # allows better font and color handling
    highlight-style: kate    # built-in code coloring
header-includes:
  - \usepackage{tcolorbox}
  - |
    \tcbset{
      colback=blue!10,
      colframe=blue!50,
      boxrule=0.5pt,
      arc=2mm,
      left=2mm,
      right=2mm,
      top=1mm,
      bottom=1mm
    }  
---

## Create the folders

```{r create folders, eval=FALSE}

dir.create("output")
dir.create("figures")
dir.create("reports")

```

## Load necessary libraries

```{r libraries, include = FALSE, warning=FALSE}

library(here)
library(dplyr)
library(VIM)
library(gtsummary)
library(flextable)
library(ggplot2)
library(survival)
library(survminer)
library(patchwork)
library(WeightIt)
library(readr)
library(cobalt)
library(ggsci)
library(survey)
library(geepack)
library(broom)
library(flextable)
library(EValue)
library(MatchIt)
library(rbounds)
library(scales)
library(tidyr)
library(gt)
library(DiagrammeR)
library(htmlwidgets)
library(webshot2)
library(DiagrammeRsvg)
library(rsvg)
library(emmeans)
```

## 1 Import data and define variables

```{r import, include = TRUE}

Outcome <- read.csv(
  here("data", "Outcome_data.csv"),
  header = TRUE,
  check.names = FALSE
)

Outcome <- Outcome %>%
  mutate(
    across(c(PID, QCODE), as.character),
    
    across(c(AGS, YEARS,BLDLOSS, BMI, CATHPERIOD, FUPM, HOSPTIME,OPRTIME,
             POSTUTIFUP, POSTUTI_T), as.numeric),
    
    across(c(ANASTOMO,BLDCOMPLEAK,BLDCOMPRETN,BLDCOMPVOID,BLDSPASM,CATH,CENTER,
             CLAVIENCLASS,EPIDURAL,GENDER, GU30, GU90N, GUER30, GUER90, HEMAT, 
             HISTOINJ,ILEUS, INCCOMPBLEED, INCCOMPINF, INCCOMPSCAR, NARC, 
             NONARC, PAIN, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR, PREOPTYPEU1,
             PREOPVURGRADE, PROC365, STENT, SURGIND, SURGTECH2, TRT2, UDR7M,
             URCOMPCVUR, URCOMPINJ, URCOMPOBST, URCOMPSTEN, POSTUTI, VURPHASE,
             VURSIDE, RECGRADE_MAX), as.factor)
  )

str(Outcome)

```

## 2 Data Imputation using KNN (k-nearest neighbors)

```{r imputation, include = TRUE}

# Missingness in the dataset
m_outcome <- colSums(is.na(Outcome)) / nrow(Outcome) * 100
print(m_outcome)


# KNN imputation
Outcome_knn <- Outcome # create a temporary dataset copy for KNN using scaled variables

# Convert categorical variables
cat_vars <- c(
  "GENDER","PREOPVURGRADE", "VURPHASE","VURSIDE",
  "UDR7M","PREOPRNSCR","HISTOINJ","SURGIND",
  "CENTER","TRT2", "SURGTECH2",
  "PREOPEPISODE1", "PREOPRNPLN","PREOPTYPEU1"
)
Outcome_knn[cat_vars] <- lapply(Outcome_knn[cat_vars], as.factor)

# Scale continuous variables
continuous_vars <- c("AGS", "BMI", "YEARS")
Outcome_knn[continuous_vars] <- scale(Outcome_knn[continuous_vars])


# KNN imputation without subsetting the dataset
Outcome_knn <- kNN(
  Outcome_knn,
  variable = c("PREOPEPISODE1", "PREOPRNPLN", "PREOPTYPEU1"),  # Variables to impute
  dist_var = c("AGS","GENDER","BMI", # Variables used to compute patient similarity
    "PREOPVURGRADE","VURPHASE","VURSIDE","UDR7M",
    "PREOPRNSCR","HISTOINJ","SURGIND","YEARS",
    "TRT2"
  ),
  k = 5,
  imp_var = FALSE
)


Out <- Outcome   # New dataset for analysis including imputed variables 
Out$PREOPEPISODE1 <- Outcome_knn$PREOPEPISODE1
Out$PREOPRNPLN   <- Outcome_knn$PREOPRNPLN
Out$PREOPTYPEU1  <- Outcome_knn$PREOPTYPEU1
```

## 3 Recode and create (composite) variables

```{r recode}

# Recode SURGIND into SURGIND2

Out <- Out %>%
  mutate(
    SURGIND2 = case_when(
      SURGIND == 4 ~ 1,
      SURGIND == 3 ~ 2,
      SURGIND == 1 ~ 3,
      SURGIND == 2 ~ 4,
      SURGIND %in% c(5, 6, 7, 8, 9, 10, 11) ~ 5,
      TRUE ~ NA_real_
    ),
    SURGIND2 = factor(SURGIND2)
  )


# Create a new variable LUTD by combining BLDCOMPRETN, BLDCOMPVOID, BLDCOMPLEAK
Out <- Out %>%
  mutate(
    LUTD = case_when(
      BLDCOMPRETN == 1 |
      BLDCOMPVOID == 1 |
      BLDCOMPLEAK == 1 ~ 1,

      BLDCOMPRETN == 0 &
      BLDCOMPVOID == 0 &
      BLDCOMPLEAK == 0 ~ 0,

      TRUE ~ NA_real_
    ),
    LUTD = factor(LUTD)
  )


# Create a new variable OBST by combining URCOMPOBST, URCOMPSTEN, ANASTOMO
Out <- Out %>%
  mutate(
    OBST = case_when(
      URCOMPOBST == 1 |
      URCOMPSTEN == 1 |
      ANASTOMO == 1 ~ 1,

      URCOMPOBST == 0 &
      URCOMPSTEN == 0 &
      ANASTOMO == 0 ~ 0,

      TRUE ~ NA_real_
    ),
    OBST = factor(OBST)
  )


# Create a new variable SURG by combining INCCOMPBLEED, INCCOMPINF, INCCOMPSCAR
Out <- Out %>%
  mutate(
    SURG = case_when(
      INCCOMPBLEED == 1 |
      INCCOMPINF == 1 |
      INCCOMPSCAR == 1 ~ 1,

      INCCOMPBLEED == 0 &
      INCCOMPINF == 0 &
      INCCOMPSCAR == 0 ~ 0,

      TRUE ~ NA_real_
    ),
    SURG = factor(SURG)
  )

# Create a new variable GU90 by combining no readmission (0) and planned readmission (2)
Out <- Out %>%
  mutate(
    GU90 = recode(as.character(GU90N),
                  "0" = "0",
                  "1" = "1",
                  "2" = "0"),
    GU90 = factor(GU90)
  )


# Create a categorical variable CATHPERIOD_G for the numerical variable CATHPERIOD
Out <- Out %>%
  mutate(CATHPERIOD_G = case_when(
    CATHPERIOD <= 3 ~ "Early removal ≤3 days",
    CATHPERIOD > 3 & CATHPERIOD <= 7 ~ "Standard removal 4–7 days",
    CATHPERIOD > 7 ~ "Delayed removal >7 days",
  ))

Out$CATHPERIOD_G <- factor(
  Out$CATHPERIOD_G, 
  levels = c("Early removal ≤3 days", "Standard removal 4–7 days", "Delayed removal >7 days")
)


# Recode complications

comp_vars <- c(
  "LUTD",
  "OBST",
  "URCOMPINJ",
  "SURG",
  "ILEUS"
)

Out[comp_vars] <- lapply(
  Out[comp_vars],
  function(x) as.numeric(as.character(x))
)

Out$ANY <- as.numeric(
  rowSums(
    Out[, comp_vars],
    na.rm = TRUE
  ) > 0
)

minor_vars <- c(
  "LUTD",
  "SURG",
  "ILEUS"
)

Out$MINOR <- as.numeric(
  rowSums(
    Out[, minor_vars],
    na.rm = TRUE
  ) > 0
)


major_vars <- c(
  "OBST",
  "URCOMPINJ"
)

Out$MAJOR <- as.numeric(
  rowSums(
    Out[, major_vars],
    na.rm = TRUE
  ) > 0
)


# Convert variables to appropriate data types for analysis
Out <- Out %>%
  mutate(
    across(c(PID, QCODE), as.character),
    
    across(c(AGS, YEARS,BLDLOSS, BMI, CATHPERIOD, FUPM, HOSPTIME,OPRTIME,
             POSTUTIFUP, POSTUTI_T), as.numeric),
    
    across(c(ANASTOMO,BLDCOMPLEAK,BLDCOMPRETN,
             BLDCOMPVOID,BLDSPASM,CATH,CENTER,CLAVIENCLASS,EPIDURAL,GENDER,
             GU30, GU90N, GUER30, GUER90, HEMAT, 
             HISTOINJ,ILEUS, INCCOMPBLEED, INCCOMPINF, INCCOMPSCAR, NARC, 
             NONARC, PAIN, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR, PREOPTYPEU1,
             PREOPVURGRADE, PROC365, STENT, SURGIND, SURGTECH2, TRT2, UDR7M,
             URCOMPCVUR, URCOMPINJ, URCOMPOBST, URCOMPSTEN, POSTUTI, VURPHASE,
             VURSIDE, RECGRADE_MAX, SURGIND2, LUTD, OBST, SURG, GU90,
             CATHPERIOD_G, ANY, MINOR, MAJOR), as.factor)
  )

str(Out)



```


## 4 Descriptive analysis: BEFORE weighting and matching

```{r descriptive, warning=FALSE}

# Baseline characteristics
table1<- Out %>%
  mutate(YEARS = factor(YEARS)) %>%   # Convert only within this pipeline  
  dplyr::select(YEARS, AGS, GENDER, BMI, HISTOINJ, SURGIND2, PREOPVURGRADE, VURSIDE, UDR7M, 
         VURPHASE, PREOPTYPEU1, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR,
         SURGTECH2, CENTER, TRT2
  ) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",  # shows missing only when present
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(
    test = list(
      YEARS ~ "chisq.test"
    ),  
  pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table1

table1 %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/baseline.docx")


# Baseline characteristics
table1b<- Out %>%
  dplyr::select(YEARS, AGS, GENDER, BMI, HISTOINJ, SURGIND2, PREOPVURGRADE, VURSIDE, UDR7M, 
         VURPHASE, PREOPTYPEU1, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR,
         SURGTECH2, CENTER, TRT2
  ) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",  # shows missing only when present
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table1b

table1b %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/baseline2.docx")


# Procedural factors
table2<- Out %>%
  dplyr::select(TRT2, OPRTIME, STENT, CATH, CATHPERIOD, CATHPERIOD_G,HOSPTIME) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})", # or ~ "{mean} ± {sd}",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table2

table2 %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/procedural.docx")

  
# Outcomes
table3<- Out %>%
  dplyr::select(TRT2, FUPM, LUTD, OBST, URCOMPINJ, SURG, ILEUS, CLAVIENCLASS, URCOMPCVUR,
         GU30, GU90, GU90N, GUER30, GUER90, PROC365, 
         BLDLOSS, BLDSPASM, HEMAT, 
         POSTUTI) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})", # or ~ "{mean} ± {sd}",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table3

table3 %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/outcomes.docx")


## Treatment distribution change over time using a chi-square test

tab_year <- table(Out$YEARS, Out$Treatment)

chisq.test(tab_year)

p_value_year <- chisq.test(tab_year)$p.value

p_label <- ifelse(
  p_value_year < 0.001,
  "Chi-square p < 0.001",
  paste0(
    "Chi-square p = ",
    format.pval(p_value_year, digits = 3)
  )
)

p_label 

# Proportion plot for treatment across 

plot_data1 <- Out %>%
  count(YEARS, Treatment) %>%
  group_by(Treatment) %>%
  mutate(
    Percent = 100 * n / sum(n)
  ) %>%
  ungroup()

pt <- ggplot(
  plot_data1,
  aes(
    x = Percent,
    y = factor(YEARS),
    fill = Treatment
  )
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7,
    colour = "black"
  ) +
  scale_x_continuous(
    limits = c(0, 100),
    breaks = seq(0, 100, 20),
    expand = expansion(mult = c(0, 0.02))
  ) +
  scale_fill_viridis_d(option = "mako", begin = 0.3, end = 0.8) +
  labs(
    x = "Proportion",
    y = "Year of Surgery",
    fill = "Treatment Group"
  ) +
  annotate(
    "text",
    x = 70,
    y = Inf,
    label = p_label,
    vjust = 1.5,
    size = 4
  ) +
  theme_classic()

pt

ggsave(filename = "figures/treatment.png", 
       plot = pt, 
       width = 8,   # width in inches
       height = 10,  # height in inches
       dpi = 300)   # resolution


######## Postoperative UTI outcome as time-to-event outcome

# Create labeled TRT2 variable only for survival analysis
Out$Treatment <- factor(
  Out$TRT2,
  levels = c(0,1),
  labels = c("Cohen", "Lich–Gregoir")
)

surv_object <- Surv(time = Out$POSTUTIFUP, event = Out$POSTUTI== 1)
fit <- survfit(surv_object ~ Treatment , data = Out)

p_u <- ggsurvplot(
  fit,
  data = Out,
  fun="event",  # Show cumulative incidence (1 - survival)
  pval = FALSE,
  pval.size = 4,
  pval.coord = c(0, 0.9),  #  c(x,y) according to my x and y scale
  conf.int = TRUE,
  risk.table = TRUE,
  risk.table.y.text = FALSE,   # to remove text from y-axis in the risk table
  # risk.table.title = "At risk",
  risk.table.fontsize = 4,   # ontrols numbers in table
  xlim = c(0, 135),
  break.time.by = 12,
  xlab = "Follow-up time",
  ylab = "Cumulative incidence of postopetative symptomatic UTI",
  palette = c("#482878", "#2E8B8B"),    # instead of "#ADD8E6", "#00008B"
  legend.title = "Treatment",
  legend.labs = c("Cohen Group", "Lich-Gregoir Group"),
  ylim = c(0, 1) # Force y-axis from 0 to 1
)

# calculate P-value from ggsurvplot (pval = TRUE), then turn it off

p_u$plot <- p_u$plot +
  annotate(
    "text",
    x = 20,
    y = 0.90,
    label = "Log rank test p = 0.058",
    size = 4
  )

#-----------------------
# Customize the plot
#-----------------------
p_u$plot <- p_u$plot +
  scale_x_continuous(
    limits = c(0, 135),
    breaks = seq(0, 135, 12)
  ) +
  scale_y_continuous(
    labels = function(x) paste0(round(x * 100, 1), "%"),
    limits = c(0, 1)
  ) +
  theme_classic() +   # Many clinical epidemiology journals prefer theme_classic() instead of theme_bw() as it automatically removes all gridlines
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x  = element_text(size = 10),
    axis.text.y  = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text  = element_text(size = 10)
  )

p_u$plot <- p_u$plot +
  labs(title = "(A) Before overlap weighting")

#----------------------------
# Customize the risk table
#----------------------------
p_u$table <- p_u$table +
  scale_x_continuous(
    limits = c(0, 135),
    breaks = seq(0, 135, 12)
  ) +
  theme(
    axis.title.x = element_blank(),
    axis.text.x  = element_blank(),
    axis.ticks.x = element_blank(),
    axis.line.x  = element_blank(),
    axis.line.y  = element_blank(),
    plot.title   = element_text(size = 12),
    text         = element_text(size = 10),
    axis.title.y = element_text(size = 12)
  )

#------------------------------------------------------------
# Combine plot and risk table using patchwork
#------------------------------------------------------------
final_plot <- p_u$plot / p_u$table +
  plot_layout(heights = c(4, 1))


#------------------------------------------------------------
# Save the figure
#------------------------------------------------------------
ggsave(
  filename = "figures/UTI.png",
  plot = final_plot,
  width = 8,
  height = 6,
  dpi = 300
)



# The estimated 1-year cumulative probability of UTI

s <- summary(fit, times = 12)

uti_1yr <- data.frame(
  Treatment = s$strata,
  UTI_1yr = 1 - s$surv,
  Lower_95CI = 1 - s$upper,
  Upper_95CI = 1 - s$lower
)


uti_1yr$UTI_1yr <- 100 * uti_1yr$UTI_1yr
uti_1yr$Lower_95CI <- 100 * uti_1yr$Lower_95CI
uti_1yr$Upper_95CI <- 100 * uti_1yr$Upper_95CI

uti_1yr

```

# MAIN ANALYSIS

### 1 Do weighting: using ATO

```{r weightingATO}

set.seed(123)

w.out <- weightit(
  TRT2 ~ AGS + YEARS + GENDER + BMI + PREOPRNPLN + HISTOINJ +
    SURGIND2 + PREOPVURGRADE + VURSIDE + UDR7M + VURPHASE +
    PREOPEPISODE1 + PREOPTYPEU1 + PREOPRNSCR + SURGTECH2,
  data = Out,
  method = "ps",
  estimand = "ATO",   
  stabilize = FALSE 
)
Out$weights <- w.out$weights  # Add weights to the dataset
write.csv(Out, "data/weighted_data.csv", row.names = FALSE)

summary(w.out$weights)


# Table for balance
bal <- cobalt::bal.tab(w.out, un = TRUE, ESS = TRUE, m.threshold = 0.1)  
bal 

bal_df <- as.data.frame(bal$Balance)
smd_table <- bal_df %>%
  mutate(
    Variable = rownames(bal_df),
    SMD_Before = round(abs(Diff.Un), 3),   
    SMD_After  = round(abs(Diff.Adj), 3)
  ) %>% 
  dplyr::select(Variable, SMD_Before, SMD_After)

smd_table %>%
  flextable() %>%
  save_as_docx(path = "output/SMD_w.docx")


# Figure for balance - Love plot
pl <- love.plot(
  w.out,
  threshold = 0.1,
  abs = TRUE, 
  stats = "mean.diffs",      
  var.order = "unadjusted", 
  drop.distance = TRUE, 
  sample.names = c("Before overlap weighting", "After overlap weighting"),
  size = 4,
    var.names = c(
    AGS = "Age at surgery",
    YEARS = "Year of surgery",
    BMI = "Body mass index",
    GENDER = "Female gender",
    PREOPRNPLN = "Preop pyelonephritis",
    HISTOINJ = "History of injection",
    VURSIDE = "Right-sided VUR",
    UDR7M = "Ureteral dilation ≥ 7mm",
    PREOPTYPEU1 = "Preop febrile UTIs",
    PREOPRNSCR = "Preop renal scarring",
    VURPHASE_1 = "Reflux: voiding phase",
    VURPHASE_2 = "Reflux: filling phase",
    VURPHASE_3 = "Reflux: filling + voiding",
    SURGTECH2_1 = "Surgeon experience ≥100 operations",
    SURGTECH2_2 = "Surgeon experience 50-100 operations",
    SURGTECH2_3 = "Surgeon experience <50 operations",
    PREOPEPISODE1_1 = "Preop UTI episodes: 1",
    PREOPEPISODE1_2 = "Preop UTI episodes: 2",
    PREOPEPISODE1_3 = "Preop UTI episodes: ≥3",
    SURGIND2_1 = "Indication: breakthrough UTI",
    SURGIND2_2 = "Indication: high-grade reflux (III-V)",
    SURGIND2_3 = "Indication: poor compliance to medical treatment",
    SURGIND2_4 = "Indication: ineffective/poorly tolerated CAP",
    SURGIND2_5 = "Indication: other",
    PREOPVURGRADE_3 = "Preop VUR grade: III",
    PREOPVURGRADE_4 = "Preop VUR grade: IV",
    PREOPVURGRADE_5 = "Preop VUR grade: V"
  )
  )

pl <- pl +
    scale_color_manual(
    values = c(
      "Before overlap weighting" = "#0072B2",
      "After overlap weighting" = "#D55E00"
    )
  ) +
    labs(
      x = "Absolute Standardized Differences",
      subtitle = "Overlap population of all children"
  ) +
    theme(
      plot.margin = margin(10, 10, 10, 10),
      axis.text = element_text(size = 16),
      axis.title = element_text(size = 16),
      plot.title = element_text(size = 16),
      legend.text = element_text(size = 16),
      legend.title = element_text(size = 16),
      axis.ticks = element_line(size = 0.5, color = "black"),
      axis.line = element_line(size = 0.5, color = "black"),
      panel.background = element_blank(), 
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      axis.ticks.length = unit(0.3, "cm"),
      panel.spacing = unit(2, "lines")
   )

ggsave ("figures/love_plot_w.png", plot = pl, width = 12, height = 10, dpi = 300)

# Compute mean SMD
smd_df <- bal$Balance
mean_smd_before <- mean(abs(smd_df$Diff.Un), na.rm = TRUE) # calculate mean SMD before matching
mean_smd_after <- mean(abs(smd_df$Diff.Adj), na.rm = TRUE) # calculate mean SMD before matching
mean_smd <- data.frame(
  Mean_SMD_Before = mean_smd_before,
  Mean_SMD_After = mean_smd_after
)

mean_smd

# how much effective sample size remains (overall ESS: calculated manually)?
summary(w.out$weights)
bal.tab(w.out)$Effective.Sample.Size
sum(w.out$weights)^2 / sum(w.out$weights^2)


# propensity score distribution
summary(w.out$ps)
pl2 <-plot(summary(w.out, type = "hist"))
ggsave ("figures/propensity_w.png", plot = pl2, width = 12, height = 10, dpi = 300)


# Distribution of overlap weights: histogram and density

## Histogram
summary(w.out$weights)
png("figures/weights_histo_w.png",
    width = 6,
    height = 4,
    units = "in",
    res = 300)

hist(
  w.out$weights,
  breaks = 30,
  col = "lightblue",
  border = "black",
  main = "Distribution of Overlap Weights",
  xlab = "Overlap Weight"
)
dev.off()



# Before-After weighting
p_ps <- bal.plot(
  w.out,
  var.name = "prop.score",
  type = "density",
  which = "both"
) 

p_ps <- p_ps +
  scale_color_viridis_d(
    option = "mako",
    begin = 0.3,
    end = 0.8,
    labels = c("Cohen group", "Lich–Gregoir group")
  ) +
  scale_fill_viridis_d(
    option = "mako",
    begin = 0.3,
    end = 0.8,
    labels = c("Cohen group", "Lich–Gregoir group")
  )

ggsave(
  "figures/PS_density_before_after_ATO.png",
  p_ps,
  width = 10,
  height = 7,
  dpi = 300
)

```

### 2 Descriptive analysis: AFTER weighting

```{r descriptivew, warning=FALSE}

# Create survey design object using overlap weights
design_ato <- svydesign(
  ids = ~1, 
  data = Out,
  weights = ~weights
)

# Weighted baseline characteristics
table1w <- design_ato %>%
  tbl_svysummary(
    by = TRT2,    
    include = c(
      YEARS, AGS, GENDER, BMI, HISTOINJ, SURGIND2, PREOPVURGRADE, VURSIDE, UDR7M, 
         VURPHASE, PREOPTYPEU1, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR,
         SURGTECH2, CENTER  
  ),
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = all_categorical() ~ c(0, 1),
    missing = "ifany",  
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  bold_labels()

table1w

table1w %>%
  as_flex_table() %>%
  flextable::save_as_docx(
    path = "output/baseline_w.docx"
  )


# Weighted procedural factors
table2w<- design_ato %>%
  tbl_svysummary(
    by = TRT2,  # for stratification
    include = c (
      OPRTIME, STENT, CATH, CATHPERIOD, CATHPERIOD_G, HOSPTIME
    ),
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})", # or ~ "{mean} ± {sd}",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table2w

table2w %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/procedural_w.docx")


# Outcomes
table3w<- design_ato %>%
  tbl_svysummary(
    by = TRT2, 
    include = c (
      FUPM, LUTD, OBST, URCOMPINJ, SURG, ILEUS, CLAVIENCLASS, URCOMPCVUR,
         GU30, GU90, GU90N, GUER30, GUER90, PROC365, 
         BLDLOSS, BLDSPASM, HEMAT, POSTUTI
    ),
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})", # or ~ "{mean} ± {sd}",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table3w

table3w %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/outcomes_w.docx")



######## Postoperative UTI outcome as time-to-event outcome: Weighted survival curve

fit_w <- survfit(
  Surv(POSTUTIFUP, POSTUTI == 1) ~ Treatment,
  data = Out,
  weights = w.out$weights
)

p_u_w <- ggsurvplot(
  fit_w,
  data = Out,
  fun = "event",
  pval = FALSE,
  pval.size = 4,
  pval.coord = c(0, 0.9),  #  c(x,y) according to my x and y scale
  conf.int = TRUE,
  risk.table = TRUE,
  risk.table.y.text = FALSE,   # to remove text from y-axis in the risk table
  risk.table.fontsize = 4,   # controls numbers in table
  xlim = c(0,135),
  break.time.by = 12,
  xlab = "Follow-up time",
  ylab = "Cumulative incidence of postoperative symptomatic UTI",
  palette = c("#482878", "#2E8B8B"),    # instead of "#ADD8E6", "#00008B"
  legend.title = "Treatment",
  legend.labs = c("Cohen Group", "Lich-Gregoir Group"),
  ylim = c(0,1)
)

cox_w <- svycoxph(
  Surv(POSTUTIFUP, POSTUTI == 1) ~ Treatment,
  design = design_ato
)

summary(cox_w)

p_u_w$plot <- p_u_w$plot +
  annotate(
    "text",
    x = 20,
    y = 0.90,
    label = "Weighted Cox p = 0.250",
    size = 4
  )

#-----------------------
# Customize the plot
#-----------------------
p_u_w$plot <- p_u_w$plot +
  scale_x_continuous(
    limits = c(0, 135),
    breaks = seq(0, 135, 12)
  ) +
  scale_y_continuous(
    labels = function(x) paste0(round(x * 100, 1), "%"),
    limits = c(0, 1)
  ) +
  theme_classic() +   # Many clinical epidemiology journals prefer theme_classic() instead of theme_bw() as it automatically removes all gridlines
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x  = element_text(size = 10),
    axis.text.y  = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text  = element_text(size = 10)
  )


p_u_w$plot <- p_u_w$plot +
  labs(title = "(B) After overlap weighting")


#----------------------------
# Customize the risk table
#----------------------------
p_u_w$table <- p_u_w$table +
  scale_x_continuous(
    limits = c(0, 135),
    breaks = seq(0, 135, 12)
  ) +
  theme(
    axis.title.x = element_blank(),
    axis.text.x  = element_blank(),
    axis.ticks.x = element_blank(),
    axis.line.x  = element_blank(),
    axis.line.y  = element_blank(),
    plot.title   = element_text(size = 12),
    text         = element_text(size = 10),
    axis.title.y = element_text(size = 12)
  )

#------------------------------------------------------------
# Combine plot and risk table
#------------------------------------------------------------
final_plot_w <- p_u_w$plot / p_u_w$table +
  plot_layout(heights = c(4, 1))



#------------------------------------------------------------
# Save the figure
#------------------------------------------------------------
ggsave(
  filename = "figures/UTI_w.png",
  plot = final_plot_w,
  width = 8,
  height = 6,
  dpi = 300
)



# Combine UTI before and after weighting plots

UTI_combined <- final_plot | final_plot_w

ggsave(
  filename = "figures/UTI_ba_w.png",
  plot = UTI_combined,
  width = 16,
  height = 6,
  dpi = 300
)



# Estimated 1-year survival
s_w <- summary(fit_w, times = 12, extend = TRUE)  # # The extend = TRUE is useful if there isn't an event exactly at 365 days.

# Estimated 1-year cumulative probability of UTI
uti_1yr_w <- data.frame(
  Treatment = s_w$strata,
  UTI_1yr = 100 * (1 - s_w$surv),
  Lower_95CI = 100 * (1 - s_w$upper),
  Upper_95CI = 100 * (1 - s_w$lower)
)

uti_1yr_w

```


### 3 Regression models

#### Block 1

```{r reg1w_norec, warning=FALSE}

# GEE model after overlap weighting - Accounting for center-clustering

# Block 1: technique effect on postoperative outcomes = Univariable analyses

outcomes <- c(
  "LUTD",
  "OBST",
  "URCOMPINJ",
  "SURG",
  "ILEUS",
  "GU30",
  "GU90",
  "PROC365"
)

# convert outcomes to numeric
Out[outcomes] <- lapply(
  Out[outcomes],
  function(x) as.numeric(as.character(x))
)

# Apply GEE model after overlap weighting for all binary outcomes
gee_results <- lapply(outcomes, function(y) {
  formula <- as.formula(
    paste(y, "~ TRT2")
  )
  model <- geeglm(
    formula,
    data = Out,
    id = CENTER,
    weights = weights,
    family = binomial(link = "logit"),
    corstr = "exchangeable"
  )
  tidy(model, exponentiate = TRUE, conf.int = TRUE)   # estimate = OR because exponentiate = TRUE
})
names(gee_results) <- outcomes


# Combine results into one table
gee_table <- do.call(
  rbind,
  lapply(names(gee_results), function(x){
    tmp <- gee_results[[x]]
    tmp <- tmp %>%
      filter(grepl("^TRT2", term)) %>%
      mutate(outcome = x)
    tmp
  })
)

# Create final manuscript table
gee_table_final <- gee_table %>%
  mutate(
    Effect_measure = "OR",
    Estimate = sprintf("%.2f", estimate),
    CI = paste0(
      sprintf("%.2f", conf.low),
      "–",
      sprintf("%.2f", conf.high)
    ),
    P_value = p.value
  ) %>%
  dplyr::select(
    Outcome = outcome,
    Effect_measure,
    Estimate,
    CI,
    P_value
  )

# weighted Cox model for POSTUTI

cox_uti <- svycoxph(
  Surv(POSTUTIFUP, POSTUTI == 1) ~ TRT2 + strata(CENTER),
  design = design_ato
)

cox_summary <- summary(cox_uti)

cox_row <- grep(
  "^TRT2",
  rownames(cox_summary$coefficients)
)

POSTUTI_table <- data.frame(
  Outcome = "POSTUTI",
  Effect_measure = "HR",
  Estimate = sprintf(
    "%.2f",
    cox_summary$coefficients[
      cox_row,
      "exp(coef)"
    ]
  ),
  CI = paste0(
    sprintf("%.2f",
            cox_summary$conf.int[cox_row, "lower .95"]),
    "–",
    sprintf("%.2f",
            cox_summary$conf.int[cox_row, "upper .95"])
  ),
  P_value = cox_summary$coefficients[
    cox_row,
    "Pr(>|z|)"
  ]
)

# Combine final results
final_results <- rbind(
  gee_table_final,
  POSTUTI_table
)


# Multiple correction

## Bonferroni correction
final_results$p_bonferroni <- p.adjust(
  final_results$P_value,
  method = "bonferroni"
)

## Holm-Bonferroni
final_results$p_holm <- p.adjust(
  final_results$P_value,
  method = "holm"
)

## Benjamini-Hochberg FDR
final_results$p_FDR <- p.adjust(
  final_results$P_value,
  method = "BH"
)


final_results <- final_results %>%
  mutate(
    across(
      c(P_value, p_bonferroni, p_holm, p_FDR),
      ~case_when(
        .x < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", .x)
      )
    )
  )

final_results

final_results %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/treatment_unadj_w_norec.docx"
  )


# Evaluate whether CENTER distribution is balanced after weighting, despite that CENTER was not included in weighting

bal.tab(
   w.out,
   data = Out,
   addl = ~ CENTER
 )

# Results showed that all CENTER SMD < 0.05 → excellent balance
# Therefore, after ATO weighting, CENTER is well balanced between treatment groups.
```


#### Block 2a - without VUR recurrence

```{r reg2aw_norec, warning=FALSE}

# Block 2: exposure-effect analysis (stent) on postoperative outcomes = Multivariable analyses

outcomes <- c(
  "LUTD",
  "OBST",
  "URCOMPINJ",
  "SURG",
  "ILEUS",
  "GU30",
  "GU90",
  "PROC365"
)

# convert outcomes to numeric
Out[outcomes] <- lapply(
  Out[outcomes],
  function(x) as.numeric(as.character(x))
)

# Predictors to include in the outcome models
predictors <- c("TRT2", "STENT")


# Apply GEE model after overlap weighting for all binary outcomes
gee_results <- lapply(outcomes, function(y) {
  formula <- as.formula(
    paste(y, "~",
          paste(predictors, collapse = " + ")
   )
  )  
  model <- geeglm(
    formula,
    data = Out,
    id = CENTER,
    weights = weights,
    family = binomial(link = "logit"),
    corstr = "exchangeable"
  )
  tidy(model, exponentiate = TRUE, conf.int = TRUE)   # estimate = OR because exponentiate = TRUE
})
names(gee_results) <- outcomes

# Combine results into one table
gee_table <- do.call(
  rbind,
  lapply(names(gee_results), function(x){
    tmp <- gee_results[[x]]
    tmp %>%
      mutate(outcome = x)
  })
)

# Create final manuscript table
gee_table_final <- gee_table %>%
  mutate(
    Effect_measure = "OR",
    Estimate = sprintf("%.2f", estimate),
    CI = paste0(
      sprintf("%.2f", conf.low),
      "–",
      sprintf("%.2f", conf.high)
    ),
    P_value = p.value
  ) %>%
  dplyr::select(
    Outcome = outcome,
    Predictor = term,
    Effect_measure,
    Estimate,
    CI,
    P_value
  )

# weighted Cox model for POSTUTI

cox_uti <- svycoxph(
  Surv(POSTUTIFUP, POSTUTI == 1) ~ TRT2 + STENT  + strata(CENTER),
  design = design_ato
)

cox_summary <- summary(cox_uti)

cox_row <- rownames(cox_summary$coefficients)

POSTUTI_table <- data.frame(
  Outcome = "POSTUTI",
  Predictor = rownames(cox_summary$coefficients),
  Effect_measure = "HR",
  Estimate = sprintf(
    "%.2f",
    cox_summary$coefficients[
      cox_row,
      "exp(coef)"
    ]
  ),
  CI = paste0(
    sprintf("%.2f",
            cox_summary$conf.int[cox_row, "lower .95"]),
    "–",
    sprintf("%.2f",
            cox_summary$conf.int[cox_row, "upper .95"])
  ),
  P_value = cox_summary$coefficients[
    cox_row,
    "Pr(>|z|)"
  ]
)


# Combine final results
final_results <- rbind(
  gee_table_final,
  POSTUTI_table
)


final_results

final_results <- final_results %>%
  mutate(
    across(
      c(P_value),
      ~case_when(
        .x < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", .x)
      )
    )
  )


final_results %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/treatment_adj_all_wa_norec.docx"
  )


# Multiple correction

# Extract TRT2 rows only

gee_trt2 <- gee_table_final %>%
  filter(grepl("^TRT2", Predictor))

POSTUTI_trt2 <- POSTUTI_table %>%
  filter(grepl("^TRT2", Predictor))

# Combine only treatment effects
treatment_results <- rbind(
  gee_trt2,
  POSTUTI_trt2
)

# Apply Correction

treatment_results$p_bonferroni <- p.adjust(
  as.numeric(treatment_results$P_value),
  method = "bonferroni"                             # Bonferroni correction
)

treatment_results$p_holm <- p.adjust(
  as.numeric(treatment_results$P_value),
  method = "holm"                                   # Holm-Bonferroni
)

treatment_results$p_FDR <- p.adjust(
  as.numeric(treatment_results$P_value),
  method = "BH"                                    # Benjamini-Hochberg FDR
)


treatment_results <- treatment_results %>%
  mutate(
    across(
      c(P_value, p_bonferroni, p_holm, p_FDR),
      ~case_when(
        .x < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", .x)
      )
    )
  )

treatment_results

treatment_results %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/treatment_adj_wa_norec.docx"
  )


# ADDITIONAL MULTIPLE COMPARISONS

# Extract STENT rows only

gee_st <- gee_table_final %>%
  filter(grepl("^STENT", Predictor))

POSTUTI_st <- POSTUTI_table %>%
  filter(grepl("^STENT", Predictor))

# Combine only stent effects
st_results <- rbind(
  gee_st,
  POSTUTI_st
)

# Apply Correction

st_results$p_bonferroni <- p.adjust(
  as.numeric(st_results$P_value),
  method = "bonferroni"                             # Bonferroni correction
)

st_results$p_holm <- p.adjust(
  as.numeric(st_results$P_value),
  method = "holm"                                   # Holm-Bonferroni
)

st_results$p_FDR <- p.adjust(
  as.numeric(st_results$P_value),
  method = "BH"                                    # Benjamini-Hochberg FDR
)


st_results <- st_results %>%
  mutate(
    across(
      c(P_value, p_bonferroni, p_holm, p_FDR),
      ~case_when(
        .x < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", .x)
      )
    )
  )

st_results

st_results %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/stent_adj_wa_norec.docx"
  )

```

#### Block 2ai - without VUR recurrence + with interaction (secondary effect-modification analysis)

```{r reg2aw_noreci}

# Block 2: exposure-effect analysis (stent) on postoperative outcomes with interaction = Multivariable analyses

outcomes <- c(
  "LUTD",
  "OBST",
  "URCOMPINJ",
  "SURG",
  "ILEUS",
  "GU30",
  "GU90",
  "PROC365"
)

# convert outcomes to numeric
Out[outcomes] <- lapply(
  Out[outcomes],
  function(x) as.numeric(as.character(x))
)

# Predictors to include in the outcome models
predictors <- "TRT2 * STENT"


# Apply GEE model after overlap weighting for all binary outcomes
gee_results <- lapply(outcomes, function(y) {
  formula <- as.formula(
    paste(y, "~",
          paste(predictors, collapse = " + ")
   )
  )  
  model <- geeglm(
    formula,
    data = Out,
    id = CENTER,
    weights = weights,
    family = binomial(link = "logit"),
    corstr = "exchangeable"
  )
  tidy(model, exponentiate = TRUE, conf.int = TRUE)   # estimate = OR because exponentiate = TRUE
})
names(gee_results) <- outcomes

# Combine results into one table
gee_table <- do.call(
  rbind,
  lapply(names(gee_results), function(x){
    tmp <- gee_results[[x]]
    tmp %>%
      mutate(outcome = x)
  })
)

# Create final manuscript table
gee_table_final <- gee_table %>%
  mutate(
    Effect_measure = "OR",
    Estimate = sprintf("%.2f", estimate),
    CI = paste0(
      sprintf("%.2f", conf.low),
      "–",
      sprintf("%.2f", conf.high)
    ),
    P_value = p.value
  ) %>%
  dplyr::select(
    Outcome = outcome,
    Predictor = term,
    Effect_measure,
    Estimate,
    CI,
    P_value
  )


# weighted Cox model for POSTUTI

cox_uti <- svycoxph(
  Surv(POSTUTIFUP, POSTUTI == 1) ~ TRT2*STENT  + strata(CENTER),
  design = design_ato
)

cox_summary <- summary(cox_uti)

cox_row <- rownames(cox_summary$coefficients)

POSTUTI_table <- data.frame(
  Outcome = "POSTUTI",
  Predictor = rownames(cox_summary$coefficients),
  Effect_measure = "HR",
  Estimate = sprintf(
    "%.2f",
    cox_summary$coefficients[
      cox_row,
      "exp(coef)"
    ]
  ),
  CI = paste0(
    sprintf("%.2f",
            cox_summary$conf.int[cox_row, "lower .95"]),
    "–",
    sprintf("%.2f",
            cox_summary$conf.int[cox_row, "upper .95"])
  ),
  P_value = cox_summary$coefficients[
    cox_row,
    "Pr(>|z|)"
  ]
)


# Combine final results
final_results <- rbind(
  gee_table_final,
  POSTUTI_table
)


final_results

final_results <- final_results %>%
  mutate(
    across(
      c(P_value),
      ~case_when(
        .x < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", .x)
      )
    )
  )


final_results %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/treatment_adj_all_wa_norec_i.docx"
  )


# Multiple correction

# Extract TRT2 rows only

gee_trt2 <- gee_table_final %>%
  filter(grepl("^TRT2", Predictor))

POSTUTI_trt2 <- POSTUTI_table %>%
  filter(grepl("^TRT2", Predictor))

# Combine only treatment effects
treatment_results <- rbind(
  gee_trt2,
  POSTUTI_trt2
)

# Apply Correction

treatment_results$p_bonferroni <- p.adjust(
  as.numeric(treatment_results$P_value),
  method = "bonferroni"                             # Bonferroni correction
)

treatment_results$p_holm <- p.adjust(
  as.numeric(treatment_results$P_value),
  method = "holm"                                   # Holm-Bonferroni
)

treatment_results$p_FDR <- p.adjust(
  as.numeric(treatment_results$P_value),
  method = "BH"                                    # Benjamini-Hochberg FDR
)


treatment_results <- treatment_results %>%
  mutate(
    across(
      c(P_value, p_bonferroni, p_holm, p_FDR),
      ~case_when(
        .x < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", .x)
      )
    )
  )

treatment_results

treatment_results %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/treatment_adj_wa_norec_i.docx"
  )


# ADDITIONAL MULTIPLE COMPARISONS

# Extract STENT rows only

gee_st <- gee_table_final %>%
  filter(grepl("^STENT", Predictor))

POSTUTI_st <- POSTUTI_table %>%
  filter(grepl("^STENT", Predictor))

# Combine only stent effects
st_results <- rbind(
  gee_st,
  POSTUTI_st
)

# Apply Correction

st_results$p_bonferroni <- p.adjust(
  as.numeric(st_results$P_value),
  method = "bonferroni"                             # Bonferroni correction
)

st_results$p_holm <- p.adjust(
  as.numeric(st_results$P_value),
  method = "holm"                                   # Holm-Bonferroni
)

st_results$p_FDR <- p.adjust(
  as.numeric(st_results$P_value),
  method = "BH"                                    # Benjamini-Hochberg FDR
)


st_results <- st_results %>%
  mutate(
    across(
      c(P_value, p_bonferroni, p_holm, p_FDR),
      ~case_when(
        .x < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", .x)
      )
    )
  )

st_results

st_results %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/stent_adj_wa_norec_i.docx"
  )

```

#### Block 2ai - without VUR recurrence + with interaction (to calculate OR for two levels) (secondary effect-modification analysis)

```{r}

## Manual calculation

outcomes <- c(
  "LUTD",
  "OBST",
  "URCOMPINJ",
  "SURG",
  "ILEUS",
  "GU30",
  "GU90",
  "PROC365"
)

# Convert outcomes to numeric
Out[outcomes] <- lapply(
  Out[outcomes],
  function(x) as.numeric(as.character(x))
)


# Function to extract treatment effects within each stent stratum
get_gee_interaction_results <- function(y) {
  
  formula <- as.formula(
    paste(y, "~ TRT2 * STENT")
  )
  
  model <- geeglm(
    formula,
    data = Out,
    id = CENTER,
    weights = weights,
    family = binomial(link = "logit"),
    corstr = "exchangeable"
  )
  
  # Coefficients
  beta <- coef(model)
  
  # Robust covariance matrix
  V <- vcov(model)
  
  # -------------------------------------------------------
  # LG vs Cohen among NO-STENT patients
  # -------------------------------------------------------
  
  b_no_stent <- beta["TRT21"]
  
  se_no_stent <- sqrt(
    V["TRT21", "TRT21"]
  )
  
  OR_no_stent <- exp(b_no_stent)
  
  CI_no_stent <- exp(
    b_no_stent + c(-1, 1) * 1.96 * se_no_stent
  )
  
  # -------------------------------------------------------
  # LG vs Cohen among STENTED patients
  # = TRT21 + TRT21:STENT1
  # -------------------------------------------------------
  
  b_stent <- beta["TRT21"] +
    beta["TRT21:STENT1"]
  
  # Variance of the linear combination:
  # Var(beta1 + beta3)
  
  var_stent <-
    V["TRT21", "TRT21"] +
    V["TRT21:STENT1", "TRT21:STENT1"] +
    2 * V["TRT21", "TRT21:STENT1"]
  
  se_stent <- sqrt(var_stent)
  
  OR_stent <- exp(b_stent)
  
  CI_stent <- exp(
    b_stent + c(-1, 1) * 1.96 * se_stent
  )
  
  # -------------------------------------------------------
  # Interaction test
  # -------------------------------------------------------
  
  b_interaction <- beta["TRT21:STENT1"]
  
  se_interaction <- sqrt(
    V["TRT21:STENT1", "TRT21:STENT1"]
  )
  
  z_interaction <- b_interaction / se_interaction
  
  p_interaction <- 2 * pnorm(
    abs(z_interaction),
    lower.tail = FALSE
  )
  
  # -------------------------------------------------------
  # Return manuscript-ready results
  # -------------------------------------------------------
  
  data.frame(
    Outcome = y,
    
    `LG vs Cohen, No Stent` =
      sprintf(
        "%.2f (%.2f–%.2f)",
        OR_no_stent,
        CI_no_stent[1],
        CI_no_stent[2]
      ),
    
    `LG vs Cohen, Stent` =
      sprintf(
        "%.2f (%.2f–%.2f)",
        OR_stent,
        CI_stent[1],
        CI_stent[2]
      ),
    
    P_interaction = p_interaction,
    
    stringsAsFactors = FALSE
  )
}


# Run for all 8 outcomes
interaction_results <- do.call(
  rbind,
  lapply(outcomes, get_gee_interaction_results)
)


interaction_results



# POSTUTI

cox_uti <- svycoxph(
  Surv(POSTUTIFUP, POSTUTI == 1) ~ TRT2 * STENT +
    strata(CENTER),
  design = design_ato
)

# Coefficients
beta_cox <- coef(cox_uti)

# Covariance matrix
V_cox <- vcov(cox_uti)

# -------------------------------------------------------
# LG vs Cohen among NO-STENT patients
# -------------------------------------------------------

b_no_stent_cox <- beta_cox["TRT21"]

se_no_stent_cox <- sqrt(
  V_cox["TRT21", "TRT21"]
)

HR_no_stent <- exp(b_no_stent_cox)

CI_no_stent_cox <- exp(
  b_no_stent_cox +
    c(-1, 1) * 1.96 * se_no_stent_cox
)


# -------------------------------------------------------
# LG vs Cohen among STENTED patients
# = TRT21 + TRT21:STENT1
# -------------------------------------------------------

b_stent_cox <- beta_cox["TRT21"] +
  beta_cox["TRT21:STENT1"]

var_stent_cox <-
  V_cox["TRT21", "TRT21"] +
  V_cox["TRT21:STENT1", "TRT21:STENT1"] +
  2 * V_cox["TRT21", "TRT21:STENT1"]

se_stent_cox <- sqrt(var_stent_cox)

HR_stent <- exp(b_stent_cox)

CI_stent_cox <- exp(
  b_stent_cox +
    c(-1, 1) * 1.96 * se_stent_cox
)


# -------------------------------------------------------
# Interaction p-value
# -------------------------------------------------------

b_interaction_cox <- beta_cox["TRT21:STENT1"]

se_interaction_cox <- sqrt(
  V_cox["TRT21:STENT1", "TRT21:STENT1"]
)

z_interaction_cox <-
  b_interaction_cox / se_interaction_cox

p_interaction_cox <- 2 * pnorm(
  abs(z_interaction_cox),
  lower.tail = FALSE
)


# Create POSTUTI result
POSTUTI_interaction <- data.frame(
  Outcome = "POSTUTI",
  
  `LG vs Cohen, No Stent` =
    sprintf(
      "%.2f (%.2f–%.2f)",
      HR_no_stent,
      CI_no_stent_cox[1],
      CI_no_stent_cox[2]
    ),
  
  `LG vs Cohen, Stent` =
    sprintf(
      "%.2f (%.2f–%.2f)",
      HR_stent,
      CI_stent_cox[1],
      CI_stent_cox[2]
    ),
  
  P_interaction = p_interaction_cox
)

POSTUTI_interaction


```

### 4 PAIN - Non-epidural Cohort

#### 4.1 Filter & weight the new population

```{r filterpain}

# Filter dataset to only those who did not receive EPIDURAL
Outp <- Out %>%
  filter(EPIDURAL == "0") %>%
  mutate(
    PAIN = factor(
      PAIN,
      levels = c("0", "1", "2", "3"),
      labels = c(
        "No pain",
        "Mild pain (score 1-3)",
        "Moderate pain (score 4-6)",
        "Severe pain (score 7-10)"
      ),
      ordered = TRUE
    )
  )

# Do weighting: using ATO (Recommended)

set.seed(123)

w.outp <- weightit(
  TRT2 ~ AGS + YEARS + GENDER + BMI + PREOPRNPLN + HISTOINJ +
    SURGIND2 + PREOPVURGRADE + VURSIDE + UDR7M + VURPHASE +
    PREOPEPISODE1 + PREOPTYPEU1 + PREOPRNSCR + SURGTECH2,
  data = Outp,
  method = "ps",
  estimand = "ATO", 
  stabilize = FALSE  # used in ATE
)
Outp$weights <- w.outp$weights  # Add weights to the dataset
write.csv(Outp, "data/weighted_nonepidural_data.csv", row.names = FALSE)

summary(w.outp$weights)


# Table for balance

balp <- cobalt::bal.tab(w.outp, un = TRUE, ESS = TRUE, m.threshold = 0.1)  
balp 

balp_df <- as.data.frame(balp$Balance)
smd_table <- balp_df %>%
  mutate(
    Variable = rownames(balp_df),
    SMD_Before = round(abs(Diff.Un), 3),
    SMD_After  = round(abs(Diff.Adj), 3)
  ) %>%
  dplyr::select(Variable, SMD_Before, SMD_After)

smd_table %>%
  flextable() %>%
  save_as_docx(path = "output/SMD_pw.docx")


# Figure for balance - Love plot
plp <- love.plot(
  w.outp,
  threshold = 0.1,
  abs = TRUE, 
  stats = "mean.diffs",      
  var.order = "unadjusted", 
  drop.distance = TRUE, 
  sample.names = c("Before Overlap Weighting", "After Overlap Weighting"),
    var.names = c(
    AGS = "Age at surgery",
    YEARS = "Year of surgery",
    BMI = "Body mass index",
    GENDER = "Female gender",
    PREOPRNPLN = "Preop pyelonephritis",
    HISTOINJ = "History of injection",
    VURSIDE = "Right-sided VUR",
    UDR7M = "Ureteral dilation ≥ 7mm",
    PREOPTYPEU1 = "Preop febrile UTIs",
    PREOPRNSCR = "Preop renal scarring",
    VURPHASE_1 = "Reflux: voiding phase",
    VURPHASE_2 = "Reflux: filling phase",
    VURPHASE_3 = "Reflux: filling + voiding",
    SURGTECH2_1 = "Surgeon experience ≥100 operations",
    SURGTECH2_2 = "Surgeon experience 50-100 operations",
    SURGTECH2_3 = "Surgeon experience <50 operations",
    PREOPEPISODE1_1 = "Preop UTI episodes: 1",
    PREOPEPISODE1_2 = "Preop UTI episodes: 2",
    PREOPEPISODE1_3 = "Preop UTI episodes: ≥3",
    SURGIND2_1 = "Indication: breakthrough UTI",
    SURGIND2_2 = "Indication: high-grade reflux (III-V)",
    SURGIND2_3 = "Indication: poor compliance to medical treatment",
    SURGIND2_4 = "Indication: ineffective/poorly tolerated CAP",
    SURGIND2_5 = "Indication: other",
    PREOPVURGRADE_3 = "Preop VUR grade: III",
    PREOPVURGRADE_4 = "Preop VUR grade: IV",
    PREOPVURGRADE_5 = "Preop VUR grade: V"
  )
  )

plp <- plp +
    labs(
    x = "Absolute Standardized Differences",
    subtitle = "Overlap population of children who did not receive epidural analgesia"
  )
    theme(
      plot.margin = margin(10, 10, 10, 10),
      axis.text = element_text(size = 16),
      axis.title = element_text(size = 16),
      plot.title = element_text(size = 16),
      legend.text = element_text(size = 16),
      legend.title = element_text(size = 16),
      axis.ticks = element_line(size = 0.5, color = "black"),
      axis.line = element_line(size = 0.5, color = "black"),
      panel.background = element_blank(), 
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      axis.ticks.length = unit(0.3, "cm"),
      panel.spacing = unit(2, "lines")
   )

ggsave ("figures/love_plot_pw.png", plot = plp, width = 12, height = 10, dpi = 300)

# Compute mean SMD
smdp_df <- balp$Balance
mean_smdp_before <- mean(abs(smdp_df$Diff.Un), na.rm = TRUE) # calculate mean SMD before matching
mean_smdp_after <- mean(abs(smdp_df$Diff.Adj), na.rm = TRUE) # calculate mean SMD before matching
mean_smdp <- data.frame(
  Mean_SMDp_Before = mean_smdp_before,
  Mean_SMDp_After = mean_smdp_after
)

mean_smdp

# how much effective sample size remains (overall ESS: calculated manually)?
summary(w.outp$weights)
bal.tab(w.outp)$Effective.Sample.Size
sum(w.outp$weights)^2 / sum(w.outp$weights^2)


# propensity score distribution
summary(w.outp$ps)
pl2p <-plot(summary(w.outp, type = "hist"))
ggsave ("figures/propensity_pw.png", plot = pl2p, width = 12, height = 10, dpi = 300)


# Distribution of overlap weights: histogram and density

## Histogram
summary(w.outp$weights)
png("figures/weights_histo_pw.png",
    width = 6,
    height = 4,
    units = "in",
    res = 300)

hist(
  w.outp$weights,
  breaks = 30,
  col = "lightblue",
  border = "black",
  main = "Distribution of Overlap Weights",
  xlab = "Overlap Weight"
)
dev.off()


# Distributional balance for propensity score (purpose: to evaluate overlap/positivity):

# Before-After weighting
p_ps_pain <- bal.plot(
  w.outp,
  var.name = "prop.score",
  type = "density",
  which = "both"
) 

p_ps_pain <- p_ps_pain +
  scale_color_viridis_d(
    option = "mako",
    begin = 0.3,
    end = 0.8,
    labels = c("Cohen group", "Lich–Gregoir group")
  ) +
  scale_fill_viridis_d(
    option = "mako",
    begin = 0.3,
    end = 0.8,
    labels = c("Cohen group", "Lich–Gregoir group")
  )

ggsave(
  "figures/PS_density_before_after_pATO.png",
  p_ps_pain,
  width = 10,
  height = 7,
  dpi = 300
)

```
 
#### 4.2 Descriptive analysis

```{r painw}

# Baseline characteristics in the population for pain
table1p<- Outp %>%
  dplyr::select(YEARS, AGS, GENDER, BMI, HISTOINJ, SURGIND2, PREOPVURGRADE, VURSIDE, UDR7M, 
         VURPHASE, PREOPTYPEU1, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR,
         SURGTECH2, CENTER, TRT2
  ) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",  # shows missing only when present
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table1p

table1p %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/baseline_p.docx")


# Create survey design object using overlap weights
design_pato <- svydesign(
  ids = ~1, 
  data = Outp,
  weights = ~weights
)

# Weighted baseline characteristics
table1pw <- design_pato %>%
  tbl_svysummary(
    by = TRT2,    # for stratification
    include = c(
      YEARS, AGS, GENDER, BMI, HISTOINJ, SURGIND2, PREOPVURGRADE, VURSIDE, UDR7M, 
         VURPHASE, PREOPTYPEU1, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR,
         SURGTECH2, CENTER    # generally we should not include TRT2 in include list
  ),
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = all_categorical() ~ c(0, 1),
    missing = "ifany",  # shows missing only when present
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  bold_labels()

table1pw

table1pw %>%
  as_flex_table() %>%
  flextable::save_as_docx(
    path = "output/baseline_pw.docx"
  )


# Weighted procedural factors
table2p<- design_pato %>%
  tbl_svysummary(
    by = TRT2,  # for stratification
    include = c (
      OPRTIME, STENT, CATH, CATHPERIOD, CATHPERIOD_G, HOSPTIME
    ),
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})", # or ~ "{mean} ± {sd}",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table2p

table2p %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/procedural_pw.docx")

# Weighted pain

# Before weighting

table4 <- Outp %>%
  dplyr::select(PAIN, NARC, NONARC, Treatment) %>%
  tbl_summary(
    by = Treatment,
    statistic = list(
      all_categorical() ~ "{n} ({p}%)"
    ),
    label = list(
      PAIN ~ "Pain score",
      NARC ~ "Narcotic use",
      NONARC ~ "Non-narcotic use"
    ),
    digits = all_categorical() ~ c(0, 1),
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%
  bold_labels()


# After ATO weighting 

design_atop <- svydesign(
  ids = ~1,
  data = Outp,
  weights = ~weights
)

# Weighted pain characteristics
table4w <- design_atop %>%
  tbl_svysummary(
    by = Treatment,    # for stratification
    include = c(
      PAIN, NARC, NONARC
  ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)"
    ),
    label = list(
      PAIN ~ "Pain score",
      NARC ~ "Narcotic use",
      NONARC ~ "Non-narcotic use"
    ),
    digits = all_categorical() ~ c(0, 1),
    missing = "ifany",  # shows missing only when present
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>% 
  bold_labels()


# MERGE TABLES
table_combined <- tbl_merge(
  tbls = list(table4, table4w),
  tab_spanner = c("**Before overlap weighting**", "**After overlap weighting**")
) %>%
  modify_caption(
    "Table 4. Comparison of pain intensity and analgesic use between treatment groups before and after propensity score overlap weighting."
) %>%
  modify_source_note(
    "Analysis restricted to patients not receiving epidural analgesia."
  )

table_combined

table_combined %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/pain_w.docx")

```

#### 4.3 Plot:  BEFORE-AFTER weighting

```{r painplotw}

# label datasets
before <- Outp %>%
  mutate(
        plot_weight = 1,
        Status = "Before overlap weighting (N=383), p<0.001"
        )

after <- Outp %>%
  mutate(
    plot_weight = weights,
    Status = "After overlap weighting (ESS=219), p<0.001")

# Combine
plot_data <- bind_rows(before, after)

# pain labels
plot_data <- plot_data %>%
  mutate(
    PAIN_plot = factor(
      PAIN,
      levels = levels(PAIN),
      labels = c("No pain", "Mild pain", "Moderate pain", "Severe pain")
    )
  )

# To define order of data
plot_data <- plot_data %>%
  mutate(
    Status = factor(
      Status,
      levels = c(
        "Before overlap weighting (N=383), p<0.001",
        "After overlap weighting (ESS=219), p<0.001"
      )
    )
  )


# 100% stacked grouped bar plot

# summary
plot_summary1 <- plot_data %>%
  group_by(Status, Treatment, PAIN) %>%
  summarise(
    weighted_n = sum(plot_weight, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(Status, Treatment) %>%
  mutate(
    Percent = 100 * weighted_n / sum(weighted_n)
  )

s1 <- ggplot(plot_summary1,
            aes(x = Treatment, y = Percent, fill = PAIN)) +
  geom_bar(stat = "identity", position = "fill", width = 0.7) +
  facet_wrap(~Status) +
  labs(
    x = "
    Treatment groups",
    y = "Percentage of patients not receiving epidural analgesia (%)",
    fill = "1-Day postoperative pain score"
  ) +
  scale_fill_manual(values = c(
  "No pain" = "#f5f5f5",  # Intead of pure white "#ffffff"
  "Mild pain (score 1-3)" = "#fee8c8",
  "Moderate pain (score 4-6)" = "#fdbb84",
  "Severe pain (score 7-10)" = "#e34a33"
  )) +
  scale_y_continuous(labels = scales::percent_format(scale = 100)) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 11),
    panel.border = element_rect(color = "black", fill = NA),
    strip.text = element_text(face = "bold"),
    panel.spacing = unit(0, "lines")
  )

ggsave(
  filename = "figures/pain_stacked_w.png",
  plot = s1,
  width = 9,
  height = 6,
  dpi = 300
)

```


#### 4.4 Regression

```{r regpain}

# -----------------------------------------
### Moderate-severe pain vs. Other levels
# -----------------------------------------

Outp <- Outp %>%
  mutate(
    PAIN_ms = factor(
      ifelse(
        PAIN %in% c(
          "Moderate pain (score 4-6)",
          "Severe pain (score 7-10)"
        ),
        1,
        0
      ),
      levels = c(0, 1),
      labels = c(
        "No/Mild pain (score 0-3)",
        "Moderate-Severe pain (score 4-10)"
      )
    )
  )


Outp$PAIN_ms <- ifelse(
  Outp$PAIN_ms == "Moderate-Severe pain (score 4-10)",
  1,
  0
)

# -----------------------------------------------------
### Exploratory analysis: Severe pain vs. Other levels
# -----------------------------------------------------

Outp <- Outp %>%
  mutate(
    PAIN_s = factor(
      ifelse(
        PAIN == "Severe pain (score 7-10)",
        1,
        0
      ),
      levels = c(0, 1),
      labels = c(
        "No severe pain (score 0-6)",
        "Severe pain (score 7-10)"
      )
    )
  )

# a numeric binary outcome:
Outp$PAIN_s <- ifelse(
  Outp$PAIN_s == "Severe pain (score 7-10)",
  1,
  0
)

#----------
# Block 1
#----------

outcomes <- c(
  "PAIN_ms",
  "PAIN_s"
)

# convert outcomes to numeric
Outp[outcomes] <- lapply(
  Outp[outcomes],
  function(x) as.numeric(as.character(x))
)

# Apply GEE model after overlap weighting for all binary outcomes
gee_results <- lapply(outcomes, function(y) {
  formula <- as.formula(
    paste(y, "~ TRT2")
  )
  model <- geeglm(
    formula,
    data = Outp,
    id = CENTER,
    weights = weights,
    family = binomial(link = "logit"),
    corstr = "exchangeable"
  )
  tidy(model, exponentiate = TRUE, conf.int = TRUE)   # estimate = OR because exponentiate = TRUE
})
names(gee_results) <- outcomes


# Combine results into one table
gee_table <- do.call(
  rbind,
  lapply(names(gee_results), function(x){
    tmp <- gee_results[[x]]
    tmp <- tmp %>%
      filter(grepl("^TRT2", term)) %>%
      mutate(outcome = x)
    tmp
  })
)

# Create final manuscript table
gee_table_final <- gee_table %>%
  mutate(
    Effect_measure = "OR",
    Estimate = sprintf("%.2f", estimate),
    CI = paste0(
      sprintf("%.2f", conf.low),
      "–",
      sprintf("%.2f", conf.high)
    ),
    P_value = ifelse(p.value < 0.001, "<0.001", sprintf("%.3f", p.value))
  ) %>%
  dplyr::select(
    Outcome = outcome,
    Effect_measure,
    Estimate,
    CI,
    P_value
  )

gee_table_final

gee_table_final %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/pain_unadj_w.docx"
  )


#--------
# Block 2
#---------

outcomes <- c(
  "PAIN_ms",
  "PAIN_s"
)


# convert outcomes to numeric
Outp[outcomes] <- lapply(
  Outp[outcomes],
  function(x) as.numeric(as.character(x))
)

# Predictors to include in the outcome models
predictors <- c("TRT2", "STENT")


# Apply GEE model after overlap weighting for all binary outcomes
gee_results <- lapply(outcomes, function(y) {
  formula <- as.formula(
    paste(y, "~",
          paste(predictors, collapse = " + ")
   )
  )  
  model <- geeglm(
    formula,
    data = Outp,
    id = CENTER,
    weights = weights,
    family = binomial(link = "logit"),
    corstr = "exchangeable"
  )
  tidy(model, exponentiate = TRUE, conf.int = TRUE)   # estimate = OR because exponentiate = TRUE
})
names(gee_results) <- outcomes

# Combine results into one table
gee_table <- do.call(
  rbind,
  lapply(names(gee_results), function(x){
    tmp <- gee_results[[x]]
    tmp %>%
      mutate(outcome = x)
  })
)

# Create final manuscript table
gee_table_final <- gee_table %>%
  mutate(
    Effect_measure = "OR",
    Estimate = sprintf("%.2f", estimate),
    CI = paste0(
      sprintf("%.2f", conf.low),
      "–",
      sprintf("%.2f", conf.high)
    ),
    P_value = ifelse(p.value < 0.001, "<0.001", sprintf("%.3f", p.value))
  ) %>%
  dplyr::select(
    Outcome = outcome,
    Predictor = term,
    Effect_measure,
    Estimate,
    CI,
    P_value
  )

gee_table_final

gee_table_final %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/pain_adj_w.docx"
  )



#------------------------
# Block 2ai- Interaction
#------------------------

outcomes <- c(
  "PAIN_ms",
  "PAIN_s"
)


# convert outcomes to numeric
Outp[outcomes] <- lapply(
  Outp[outcomes],
  function(x) as.numeric(as.character(x))
)

# Function to extract treatment effects within each stent stratum
get_gee_interaction_results <- function(y) {
  
  formula <- as.formula(
    paste(y, "~ TRT2 * STENT")
  )
  
  model <- geeglm(
    formula,
    data = Outp,
    id = CENTER,
    weights = weights,
    family = binomial(link = "logit"),
    corstr = "exchangeable"
  )
  
  # Coefficients
  beta <- coef(model)
  
  # Robust covariance matrix
  V <- vcov(model)
  
  # -------------------------------------------------------
  # LG vs Cohen among NO-STENT patients
  # -------------------------------------------------------
  
  b_no_stent <- beta["TRT21"]
  
  se_no_stent <- sqrt(
    V["TRT21", "TRT21"]
  )
  
  OR_no_stent <- exp(b_no_stent)
  
  CI_no_stent <- exp(
    b_no_stent + c(-1, 1) * 1.96 * se_no_stent
  )
  
  # -------------------------------------------------------
  # LG vs Cohen among STENTED patients
  # = TRT21 + TRT21:STENT1
  # -------------------------------------------------------
  
  b_stent <- beta["TRT21"] +
    beta["TRT21:STENT1"]
  
  # Variance of the linear combination:
  # Var(beta1 + beta3)
  
  var_stent <-
    V["TRT21", "TRT21"] +
    V["TRT21:STENT1", "TRT21:STENT1"] +
    2 * V["TRT21", "TRT21:STENT1"]
  
  se_stent <- sqrt(var_stent)
  
  OR_stent <- exp(b_stent)
  
  CI_stent <- exp(
    b_stent + c(-1, 1) * 1.96 * se_stent
  )
  
  # -------------------------------------------------------
  # Interaction test
  # -------------------------------------------------------
  
  b_interaction <- beta["TRT21:STENT1"]
  
  se_interaction <- sqrt(
    V["TRT21:STENT1", "TRT21:STENT1"]
  )
  
  z_interaction <- b_interaction / se_interaction
  
  p_interaction <- 2 * pnorm(
    abs(z_interaction),
    lower.tail = FALSE
  )
  
  # -------------------------------------------------------
  # Return manuscript-ready results
  # -------------------------------------------------------
  
  data.frame(
    Outcome = y,
    
    `LG vs Cohen, No Stent` =
      sprintf(
        "%.2f (%.2f–%.2f)",
        OR_no_stent,
        CI_no_stent[1],
        CI_no_stent[2]
      ),
    
    `LG vs Cohen, Stent` =
      sprintf(
        "%.2f (%.2f–%.2f)",
        OR_stent,
        CI_stent[1],
        CI_stent[2]
      ),
    
    P_interaction = p_interaction,
    
    stringsAsFactors = FALSE
  )
}


# Run for all 8 outcomes
interaction_results <- do.call(
  rbind,
  lapply(outcomes, get_gee_interaction_results)
)


interaction_results
```


# SENSITIVITY ANALYSIS 1

### 1 E-value for outcomes

```{r evalue}

# E-value explains away a specific treatment–outcome association.

evalue_data <- data.frame(
  Outcome = c(
    "OBST",
    "URCOMPINJ",
    "SURG",
    "ILEUS",
    "GU90",
    "OBSTadj",
    "URCOMPINJadj",
    "SURGadj",
    "ILEUSadj",
    "GU90adj",
    "GU30adj",    
    "PROC365adj",
    "PAIN_ms",
    "PAIN_s",    
    "PAIN_msadj", 
    "PAIN_sadj"     
  ),
  OR = c(
    3.67,
    0.43,
    0.72,
    0.10,
    0.20,
    3.71,
    0.36,
    0.63,
    0.20,
    0.18,
    0.03,
    0.71,
    0.32,
    0.20,
    0.32,
    0.14
  ),
  CI_low = c(
    2.21,
    0.27,
    0.58,
    0.04,
    0.16,
    2.50,
    0.27,
    0.50,
    0.17,
    0.15,
    0.01,
    0.56,
    0.14,
    0.15,
    0.15,
    0.10
  ),
  CI_high = c(
    6.10,
    0.69,
    0.90,
    0.25,
    0.26,
    5.52,
    0.49,
    0.81,
    0.24,
    0.21,
    0.08,
    0.89,
    0.73,
    0.26,
    0.69,
    0.19
  )
)


# Specify rare outcome assumption
evalue_data <- evalue_data %>%
  mutate(
    rare = ifelse(
      Outcome %in% c("SURG", "GU90", "SURGadj", "GU90adj", "GU30adj", "Pain_ms", "Pain_s", "Pain_msadj", "Pain_sadj"),
      FALSE,
      TRUE
    )
  )


# Calculate E-values
evalue_results <- evalue_data %>%
  rowwise() %>%
  mutate(
    OR_input = ifelse(OR < 1, 1/OR, OR),
    CI_low_input = ifelse(OR < 1, 1/CI_high, CI_low),
    CI_high_input = ifelse(OR < 1, 1/CI_low, CI_high),
    
    E_value = list(
      evalues.OR(
        est = OR_input,
        lo = CI_low_input,
        hi = CI_high_input,
        rare = rare
      )
    )
  ) %>%
  ungroup()

evalue_table <- evalue_results %>%
  mutate(
    E_value_point = sapply(
      E_value,
      function(x) x["E-values", "point"]
    ),
    E_value_CI = sapply(
      E_value,
      function(x) x["E-values", "lower"]
    )
  ) %>%
  dplyr::select(
    Outcome,
    OR,
    CI_low,
    CI_high,
    E_value_point,
    E_value_CI
  )

evalue_table


evalue_table_formatted <- evalue_table %>%
  mutate(
    OR = sprintf("%.2f", OR),
    CI = paste0(
      sprintf("%.2f", CI_low),
      "–",
      sprintf("%.2f", CI_high)
    ),
    E_value_point = sprintf("%.2f", E_value_point),
    E_value_CI = sprintf("%.2f", E_value_CI)
  ) %>%
  dplyr::select(
    Outcome,
    OR,
    CI,
    E_value_point,
    E_value_CI
  )

evalue_table_formatted %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("OR", "CI", "E_value_point", "E_value_CI"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/E_value_stent.docx"
  )

```

#### 1.1. Plot E-value

```{r evalueplot}

# E-value sensitivity contour plot for Obstruction risk in overlap weighting before adjustment to procedural factors


# OBST values
RR_est <- 3.67
RR_CI  <- 2.21

E_value_point <- RR_est + sqrt(RR_est*(RR_est-1))
E_value_CI <- RR_CI + sqrt(RR_CI*(RR_CI-1))

# Function for contour
evalue_curve <- function(RR){

  x <- seq(RR + 0.001, 20, length.out = 5000)

  y <- RR * (x - 1)/(x - RR)

  data.frame(
    RR_EU = x,
    RR_UY = y
  )
}

curve_est <- evalue_curve(RR_est)
curve_CI  <- evalue_curve(RR_CI)


# Create plot
evalue_plot <- ggplot() +

  # Point estimate curve
  geom_line(
    data = curve_est,
    aes(
      x = RR_EU,
      y = RR_UY
    ),
    color = "red",
    linewidth = 0.8
  ) +

  # CI curve
  geom_line(
    data = curve_CI,
    aes(
      x = RR_EU,
      y = RR_UY
    ),
    color = "blue",
    linewidth = 0.8
  ) +

  # E-value point
  geom_point(
    aes(
      x = E_value_point,
      y = E_value_point
    ),
    color = "red",
    size = 2.5
  ) +

  # CI E-value point
  geom_point(
    aes(
      x = E_value_CI,
      y = E_value_CI
    ),
    color = "blue",
    size = 2.5
  ) +

  # Labels
  annotate(
    "text",
    x = E_value_point,
    y = E_value_point + 0.35,
    label = paste0(
      "E value: (",
      round(E_value_point,2),
      ", ",
      round(E_value_point,2),
      ")"
    ),
    color = "black",
    size = 4,
    hjust = 0
  ) +

  annotate(
    "text",
    x = E_value_CI,
    y = E_value_CI - 0.25,
    label = paste0(
      "E value (CI): (",
      round(E_value_CI,2),
      ", ",
      round(E_value_CI,2),
      ")"
    ),
    color = "black",
    size = 4,
    hjust = 0
  ) +

  scale_x_continuous(
    limits = c(1,20),
    breaks = seq(5,20,5)
  ) +

  scale_y_continuous(
    limits = c(1,20),
    breaks = seq(0,20,5)
  ) +

  labs(
    x = "Risk ratio for exposure-confounder relationship",
    y = "Risk ratio for confounder-outcome relationship"
  ) +

  theme_gray(base_size = 14)



# OBST values
RR_est_a <- 3.71
RR_CI_a  <- 2.50

E_value_point_a <- RR_est_a + sqrt(RR_est_a*(RR_est_a-1))
E_value_CI_a <- RR_CI_a + sqrt(RR_CI_a*(RR_CI_a-1))


# Function for contour
evalue_curve <- function(RR){

  x <- seq(RR + 0.001, 20, length.out = 5000)

  y <- RR * (x - 1)/(x - RR)

  data.frame(
    RR_EU = x,
    RR_UY = y
  )
}

curve_est_a <- evalue_curve(RR_est_a)
curve_CI_a  <- evalue_curve(RR_CI_a)


# Create plot
evalue_plot_a <- ggplot() +

  # Point estimate curve
  geom_line(
    data = curve_est_a,
    aes(
      x = RR_EU,
      y = RR_UY
    ),
    color = "red",
    linewidth = 0.8
  ) +

  # CI curve
  geom_line(
    data = curve_CI_a,
    aes(
      x = RR_EU,
      y = RR_UY
    ),
    color = "blue",
    linewidth = 0.8
  ) +

  # E-value point
  geom_point(
    aes(
      x = E_value_point_a,
      y = E_value_point_a
    ),
    color = "red",
    size = 2.5
  ) +

  # CI E-value point
  geom_point(
    aes(
      x = E_value_CI_a,
      y = E_value_CI_a
    ),
    color = "blue",
    size = 2.5
  ) +

  # Labels
  annotate(
    "text",
    x = E_value_point_a,
    y = E_value_point_a + 0.35,
    label = paste0(
      "E value: (",
      round(E_value_point_a,2),
      ", ",
      round(E_value_point_a,2),
      ")"
    ),
    color = "black",
    size = 4,
    hjust = 0
  ) +

  annotate(
    "text",
    x = E_value_CI_a,
    y = E_value_CI_a - 0.25,
    label = paste0(
      "E value (CI): (",
      round(E_value_CI_a,2),
      ", ",
      round(E_value_CI_a,2),
      ")"
    ),
    color = "black",
    size = 4,
    hjust = 0
  ) +

  scale_x_continuous(
    limits = c(1,20),
    breaks = seq(5,20,5)
  ) +

  scale_y_continuous(
    limits = c(1,20),
    breaks = seq(0,20,5)
  ) +

  labs(
    x = "Risk ratio for exposure-confounder relationship",
    y = "Risk ratio for confounder-outcome relationship"
  ) +

  theme_gray(base_size = 14)


#------------------------------------------------------------
# Combine plot and risk table using patchwork
#------------------------------------------------------------
combined_plot <- (evalue_plot | evalue_plot_a) +
  plot_annotation(
    tag_levels = "A"
  )


#------------------------------------------------------------
# Save the figure
#------------------------------------------------------------
ggsave(
  filename = "figures/Evalue_OBST.png",
  plot = combined_plot,
  width = 20,
  height = 10,
  dpi = 300
)


```


# SENSITIVITY ANALYSIS 2

### 1 Do matching 1:1 without replacement

```{r matching, warning=FALSE}

# Fit matching model using propensity score (calculated inside MatchIt): 1:1 matching

set.seed(123) 
 
m.out <- matchit(
  TRT2 ~ AGS + YEARS + GENDER + BMI + PREOPRNPLN + HISTOINJ +
    SURGIND2 + PREOPVURGRADE + VURSIDE + UDR7M + VURPHASE +
    PREOPEPISODE1 + PREOPTYPEU1 + PREOPRNSCR + SURGTECH2,
  data = Out,
  method = "nearest",
  ratio = 1,  # 1:1 matching (1 treated : 1 control)
  distance = "logit",
   caliper = 0.2
) 


mdata <- match.data(
  m.out,
  weights = "weights_psm"
)

readr::write_csv(mdata, "data/matched_data.csv")  


# Table for balance
balm <- cobalt::bal.tab(m.out, un = TRUE, m.threshold = 0.1)  
balm 

bal_dfm <- as.data.frame(balm$Balance)
smd_tablem <- bal_dfm %>%
  mutate(
    Variable = rownames(bal_dfm),
    SMD_Before = round(abs(Diff.Un), 3),
    SMD_After  = round(abs(Diff.Adj), 3)
  ) %>%
  select(Variable, SMD_Before, SMD_After)

smd_tablem %>%
  flextable() %>%
  save_as_docx(path = "output/SMD_psm.docx")


# how much effective sample size remains (overall ESS: calculated manually)?
summary(m.out$weights)
bal.tab(m.out)$Effective.Sample.Size
sum(m.out$weights)^2 / sum(m.out$weights^2)


# Figure for balance - Love plot
plm <- love.plot(
  m.out,
  threshold = 0.1,
  abs = TRUE, 
  stats = "mean.diffs",      
  var.order = "unadjusted",  
  drop.distance = TRUE,     
  sample.names = c("Before matching", "After matching"),
    size = 4,
    var.names = c(
    AGS = "Age at surgery",
    YEARS = "Year of surgery",
    BMI = "Body mass index",
    GENDER = "Female gender",
    PREOPRNPLN = "Preop pyelonephritis",
    HISTOINJ = "History of injection",
    VURSIDE = "Right-sided VUR",
    UDR7M = "Ureteral dilation ≥ 7mm",
    PREOPTYPEU1 = "Preop febrile UTIs",
    PREOPRNSCR = "Preop renal scarring",
    VURPHASE_1 = "Reflux: voiding phase",
    VURPHASE_2 = "Reflux: filling phase",
    VURPHASE_3 = "Reflux: filling + voiding",
    SURGTECH2_1 = "Surgeon experience ≥100 operations",
    SURGTECH2_2 = "Surgeon experience 50-100 operations",
    SURGTECH2_3 = "Surgeon experience <50 operations",
    PREOPEPISODE1_1 = "Preop UTI episodes: 1",
    PREOPEPISODE1_2 = "Preop UTI episodes: 2",
    PREOPEPISODE1_3 = "Preop UTI episodes: ≥3",
    SURGIND2_1 = "Indication: breakthrough UTI",
    SURGIND2_2 = "Indication: high-grade reflux (III-V)",
    SURGIND2_3 = "Indication: poor compliance to medical treatment",
    SURGIND2_4 = "Indication: ineffective/poorly tolerated CAP",
    SURGIND2_5 = "Indication: other",
    PREOPVURGRADE_3 = "Preop VUR grade: III",
    PREOPVURGRADE_4 = "Preop VUR grade: IV",
    PREOPVURGRADE_5 = "Preop VUR grade: V"
  )
  )

plm <- plm +
  scale_color_manual(
    values = c(
      "Before matching" = "#0072B2",
      "After matching" = "#D55E00"
    )
     )+
    labs(
        x = "Absolute Standardized Differences",
      subtitle = "Matched population"
  ) +
    theme(
      plot.margin = margin(10, 10, 10, 10),
      axis.text = element_text(size = 16),
      axis.title = element_text(size = 16),
      plot.title = element_text(size = 16),
      legend.text = element_text(size = 16),
      legend.title = element_text(size = 16),
      axis.ticks = element_line(size = 0.5, color = "black"),
      axis.line = element_line(size = 0.5, color = "black"),
      panel.background = element_blank(), 
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      axis.ticks.length = unit(0.3, "cm"),
      panel.spacing = unit(2, "lines")
   )

ggsave ("figures/love_plot_m.png", plot = plm, width = 12, height = 10, dpi = 300)


# Compute mean SMD
smd_df_m <- balm$Balance
mean_smd_before_m <- mean(abs(smd_df_m$Diff.Un), na.rm = TRUE) # calculate mean SMD before matching
mean_smd_after_m <- mean(abs(smd_df_m$Diff.Adj), na.rm = TRUE) # calculate mean SMD before matching
mean_smd_m <- data.frame(
  Mean_SMD_Before = mean_smd_before_m,
  Mean_SMD_After = mean_smd_after_m
)

mean_smd_m


# propensity score distribution: MatchIt does not store the propensity scores in m.out$ps. Instead, they are stored in m.out$distance.
summary(m.out$distance)
hist(m.out$distance)

ggplot(
  data.frame(
    ps = m.out$distance,
    Treatment  = factor(Out$Treatment)
  ),
  aes(ps, fill = Treatment)
) +
  geom_histogram(alpha = 0.5, bins = 30, position = "identity",   color = "black", linewidth = 0.3 ) +
    scale_fill_viridis_d(
    option = "mako",
    begin = 0.3,
    end = 0.8,
    labels = c("Cohen", "Lich–Gregoir")
  ) +
  labs(
    x = "Propensity score",
    y = "Count",
    fill = "Treatment"
  ) +
  theme_bw()

ggsave("figures/propensity_psm.png",
       width = 12,
       height = 10,
       dpi = 300)

# Distributional balance for propensity score

# Before-After matching
p_psm <- bal.plot(
  m.out,
  var.name = "distance",
  type = "density",
  which = "both"    
) 

p_psm <- p_psm +
  scale_color_viridis_d(
    option = "mako",
    begin = 0.3,
    end = 0.8,
    labels = c("Cohen group", "Lich–Gregoir group")
  ) +
  scale_fill_viridis_d(
    option = "mako",
    begin = 0.3,
    end = 0.8,
    labels = c("Cohen group", "Lich–Gregoir group")
  )

ggsave(
  "figures/PS_density_before_after_m.png",
  p_psm,
  width = 10,
  height = 6,
  dpi = 300
)
```

### 2 Descriptive analysis: AFTER matching

```{r descriptivem, warning=FALSE}

# mdata is the dataset with added weights_psm

# Convert variables to appropriate data types for analysis
mdata <- mdata %>%
  mutate(
    across(c(PID, QCODE), as.character),
    
    across(c(AGS, YEARS,BLDLOSS, BMI, CATHPERIOD, FUPM, HOSPTIME,OPRTIME,
             POSTUTIFUP, POSTUTI_T), as.numeric),
    
    across(c(ANASTOMO,BLDCOMPLEAK,BLDCOMPRETN,
             BLDCOMPVOID,BLDSPASM,CATH,CENTER,CLAVIENCLASS,EPIDURAL,GENDER,
             GU30, GU90N, GUER30, GUER90, HEMAT, 
             HISTOINJ,ILEUS, INCCOMPBLEED, INCCOMPINF, INCCOMPSCAR, NARC, 
             NONARC, PAIN, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR, PREOPTYPEU1,
             PREOPVURGRADE, PROC365, STENT, SURGIND, SURGTECH2, TRT2, UDR7M,
             URCOMPCVUR, URCOMPINJ, URCOMPOBST, URCOMPSTEN, POSTUTI, VURPHASE,
             VURSIDE, RECGRADE_MAX, SURGIND2, LUTD, OBST, SURG, GU90,
             CATHPERIOD_G, ANY, MINOR, MAJOR), as.factor)
  )

str(mdata) # 194 obs. of 71 variables


# Matched baseline characteristics
table1m<- mdata %>%
  select(YEARS, AGS, GENDER, BMI, HISTOINJ, SURGIND2, PREOPVURGRADE, VURSIDE, UDR7M, 
         VURPHASE, PREOPTYPEU1, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR,
         SURGTECH2, CENTER, TRT2
  ) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",  # shows missing only when present
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  bold_labels()

table1m <- table1m %>%
  modify_caption(
    "Baseline characteristics after 1:1 propensity score matching"
  )

table1m %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/baseline_m.docx")


# Matched procedural factors
table2m<- mdata %>%
  select(TRT2, OPRTIME, STENT, CATH, CATHPERIOD, CATHPERIOD_G, HOSPTIME) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})", # or ~ "{mean} ± {sd}",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table2m

table2m %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/procedural_m.docx")

# Outcomes
table3m<- mdata %>%
  select(TRT2, FUPM, LUTD, OBST, URCOMPINJ, SURG, ILEUS, CLAVIENCLASS, URCOMPCVUR,
         GU30, GU90, GU90N, GUER30, GUER90, PROC365, 
         BLDLOSS, BLDSPASM, HEMAT, 
         POSTUTI) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})", # or ~ "{mean} ± {sd}",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table3m

table3m %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/outcomes_m.docx")


######## Postoperative UTI outcome as time-to-event outcome: Weighted survival curve
fit_psm <- survfit(
  Surv(POSTUTIFUP, POSTUTI == 1) ~ Treatment,
  data = mdata
)

logrank_test <- survdiff(
  Surv(POSTUTIFUP, POSTUTI == 1) ~ TRT2,
  data = mdata
)

p_value <- 1 - pchisq(
  logrank_test$chisq,
  df = length(logrank_test$n) - 1
)

p_label <- paste0("Log-rank test p = ", format.pval(p_value, digits = 3, eps = 0.001))

p_u_psm <- ggsurvplot(
  fit_psm,
  data = mdata,
  fun = "event",
  pval = p_label,
  pval.size = 4,
  pval.coord = c(0, 0.9),  #  c(x,y) according to my x and y scale
  conf.int = TRUE,
  risk.table = TRUE,
  risk.table.y.text = FALSE,   # to remove text from y-axis in the risk table
  risk.table.fontsize = 4,   # controls numbers in table
  xlim = c(0,135),
  break.time.by = 12,
  xlab = "Follow-up time",
  ylab = "Cumulative incidence of postoperative symptomatic UTI",
  palette = c("#ADD8E6", "#00008B"),
  legend.title = "Treatment",
  legend.labs = c("Cohen Group", "Lich-Gregoir Group"),
  ylim = c(0,1)
)

#-----------------------
# Customize the plot
#-----------------------
p_u_psm$plot <- p_u_psm$plot +
  scale_x_continuous(
    limits = c(0, 135),
    breaks = seq(0, 135, 12)
  ) +
  scale_y_continuous(
    labels = function(x) paste0(round(x * 100, 1), "%"),
    limits = c(0, 1)
  ) +
  theme_classic() +   # Many clinical epidemiology journals prefer theme_classic() instead of theme_bw() as it automatically removes all gridlines
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x  = element_text(size = 10),
    axis.text.y  = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text  = element_text(size = 10)
  )

#----------------------------
# Customize the risk table
#----------------------------
p_u_psm$table <- p_u_psm$table +
  scale_x_continuous(
    limits = c(0, 135),
    breaks = seq(0, 135, 12)
  ) +
  theme(
    axis.title.x = element_blank(),
    axis.text.x  = element_blank(),
    axis.ticks.x = element_blank(),
    axis.line.x  = element_blank(),
    axis.line.y  = element_blank(),
    plot.title   = element_text(size = 12),
    text         = element_text(size = 10),
    axis.title.y = element_text(size = 12)
  )

#------------------------------------------------------------
# Combine plot and risk table
#------------------------------------------------------------
final_plot_psm <- p_u_psm$plot / p_u_psm$table +
  plot_layout(heights = c(4, 1))


#------------------------------------------------------------
# Save the figure
#------------------------------------------------------------
ggsave(
  filename = "figures/UTI_m.png",
  plot = final_plot_psm,
  width = 8,
  height = 6,
  dpi = 300
)

# Estimated 1-year survival
s_psm <- summary(fit_psm, times = 12, extend = TRUE)

# Estimated 1-year cumulative probability of UTI
uti_1yr_psm <- data.frame(
  Treatment = s_psm$strata,
  UTI_1yr = 100 * (1 - s_psm$surv),
  Lower_95CI = 100 * (1 - s_psm$upper),
  Upper_95CI = 100 * (1 - s_psm$lower)
)

uti_1yr_psm
```

### 3 Regression

#### Block 1 - without VUR recurrence

```{r reg1m_norec}

# GEE model after matching - Accounting for center-clustering

# Block 1: technique effect on postoperative outcomes = Univariable analyses

outcomes <- c(
  "LUTD",
  "OBST",
  "URCOMPINJ",
  "SURG",
  "ILEUS",
  "GU30",
  "GU90",
  "PROC365"
)

# convert outcomes to numeric
mdata[outcomes] <- lapply(
  mdata[outcomes],
  function(x) as.numeric(as.character(x))
)

# Apply GEE model after matching for all binary outcomes
gee_results_psm <- lapply(outcomes, function(y) {
  formula <- as.formula(
    paste(y, "~ TRT2")
  )
  model <- geeglm(
    formula,
    data = mdata,
    id = CENTER,
    weights = weights_psm,       # weights have no effect because weights are all equal
    family = binomial(link = "logit"),
    corstr = "exchangeable"
  )
  tidy(model, exponentiate = TRUE, conf.int = TRUE) 
})
names(gee_results_psm) <- outcomes


# Combine results into one table
gee_table_psm <- do.call(
  rbind,
  lapply(names(gee_results_psm), function(x){
    tmp <- gee_results_psm[[x]]
    tmp <- tmp %>%
      filter(grepl("^TRT2", term)) %>%
      mutate(outcome = x)
    tmp
  })
)

# Create final manuscript table
gee_table_final_psm <- gee_table_psm %>%
  mutate(
    Effect_measure = "OR",
    Estimate = sprintf("%.2f", estimate),
    CI = paste0(
      sprintf("%.2f", conf.low),
      "–",
      sprintf("%.2f", conf.high)
    ),
    P_value = p.value
  ) %>%
  dplyr::select(
    Outcome = outcome,
    Effect_measure,
    Estimate,
    CI,
    P_value
  )


# Cox model for POSTUTI

cox_uti_psm <- coxph(
  Surv(POSTUTIFUP, POSTUTI == 1) ~ TRT2 + strata(CENTER),
  data = mdata,
  weights = weights_psm,  # weights have no effect
  robust = TRUE,
  cluster = subclass  
)

cox_summarypsm <- summary(cox_uti_psm)

cox_row <- grep(
  "^TRT2",
  rownames(cox_summarypsm$coefficients)
)

POSTUTI_table_psm <- data.frame(
  Outcome = "POSTUTI",
  Effect_measure = "HR",
  Estimate = sprintf(
    "%.2f",
    cox_summarypsm$coefficients[
      cox_row,
      "exp(coef)"
    ]
  ),
  CI = paste0(
    sprintf("%.2f",
            cox_summarypsm$conf.int[cox_row, "lower .95"]),
    "–",
    sprintf("%.2f",
            cox_summarypsm$conf.int[cox_row, "upper .95"])
  ),
  P_value = cox_summarypsm$coefficients[
    cox_row,
    "Pr(>|z|)"
  ]
)

# Combine final results
final_resultspsm <- rbind(
  gee_table_final_psm,
  POSTUTI_table_psm
)


# Multiple correction

## Bonferroni correction
final_resultspsm$p_bonferroni <- p.adjust(
  final_resultspsm$P_value,
  method = "bonferroni"
)

## Holm-Bonferroni
final_resultspsm$p_holm <- p.adjust(
  final_resultspsm$P_value,
  method = "holm"
)

## Benjamini-Hochberg FDR
final_resultspsm$p_FDR <- p.adjust(
  final_resultspsm$P_value,
  method = "BH"
)


final_resultspsm <- final_resultspsm %>%
  mutate(
    across(
      c(P_value, p_bonferroni, p_holm, p_FDR),
      ~case_when(
        .x < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", .x)
      )
    )
  )

final_resultspsm

final_resultspsm %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/treatment_unadj_m_norec.docx"
  )

```

#### Block 2 - without VUR recurrence

```{r reg2m_norec}

# Block 2: exposure-effect analysis (stent) on postoperative outcomes = Multivariable analyses

outcomes <- c(
  "LUTD",
  "OBST",
  "URCOMPINJ",
  "SURG",
  "ILEUS",
  "GU30",
  "GU90",
  "PROC365"
)

# convert outcomes to numeric
mdata[outcomes] <- lapply(
  mdata[outcomes],
  function(x) as.numeric(as.character(x))
)

# Predictors to include in the outcome models
predictors <- c("TRT2", "STENT")


# Apply GEE model after overlap weighting for all binary outcomes
gee_results_psm2 <- lapply(outcomes, function(y) {
  formula <- as.formula(
    paste(y, "~",
          paste(predictors, collapse = " + ")
   )
  )  
  model <- geeglm(
    formula,
    data = mdata,
    id = CENTER,
    weights = weights_psm,    # weights have no effect because weights are all equal
    family = binomial(link = "logit"),
    corstr = "exchangeable"
  )
  tidy(model, exponentiate = TRUE, conf.int = TRUE) 
})
names(gee_results_psm2) <- outcomes

# Combine results into one table
gee_table_psm2 <- do.call(
  rbind,
  lapply(names(gee_results_psm2), function(x){
    tmp <- gee_results_psm2[[x]]
    tmp %>%
      mutate(outcome = x)
  })
)

# Create final manuscript table
gee_table_final_psm2 <- gee_table_psm2 %>%
  mutate(
    Effect_measure = "OR",
    Estimate = sprintf("%.2f", estimate),
    CI = paste0(
      sprintf("%.2f", conf.low),
      "–",
      sprintf("%.2f", conf.high)
    ),
    P_value = p.value
  ) %>%
  dplyr::select(
    Outcome = outcome,
    Predictor = term,
    Effect_measure,
    Estimate,
    CI,
    P_value
  )


# Cox model for POSTUTI

cox_uti_psm2 <- coxph(
  Surv(POSTUTIFUP, POSTUTI == 1) ~ TRT2 + STENT + strata(CENTER),
  data = mdata,
  weights = weights_psm,  # weights have no effect
  robust = TRUE,
  cluster = subclass   
)

cox_summarypsm2 <- summary(cox_uti_psm2)

cox_row <- rownames(cox_summarypsm2$coefficients)

POSTUTI_table_psm2 <- data.frame(
  Outcome = "POSTUTI",
  Predictor = rownames(cox_summarypsm2$coefficients),
  Effect_measure = "HR",
  Estimate = sprintf(
    "%.2f",
    cox_summarypsm2$coefficients[
      cox_row,
      "exp(coef)"
    ]
  ),
  CI = paste0(
    sprintf("%.2f",
            cox_summarypsm2$conf.int[cox_row, "lower .95"]),
    "–",
    sprintf("%.2f",
            cox_summarypsm2$conf.int[cox_row, "upper .95"])
  ),
  P_value = cox_summarypsm2$coefficients[
    cox_row,
    "Pr(>|z|)"
  ]
)


# Combine final results
final_results_psm2 <- rbind(
  gee_table_final_psm2,
  POSTUTI_table_psm2
)


final_results_psm2

final_results_psm2 <- final_results_psm2 %>%
  mutate(
    across(
      c(P_value),
      ~case_when(
        .x < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", .x)
      )
    )
  )


final_results_psm2 %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/treatment_adj_all_m_norec.docx"
  )


# Multiple correction

# Extract TRT2 rows only

gee_trt2_psm2 <- gee_table_final_psm2 %>%
  filter(grepl("^TRT2", Predictor))

POSTUTI_trt2_psm2 <- POSTUTI_table_psm2 %>%
  filter(grepl("^TRT2", Predictor))

# Combine only treatment effects
treatment_results_psm2 <- rbind(
  gee_trt2_psm2,
  POSTUTI_trt2_psm2
)

# Apply Correction

treatment_results_psm2$p_bonferroni <- p.adjust(
  as.numeric(treatment_results_psm2$P_value),
  method = "bonferroni"                             # Bonferroni correction
)

treatment_results_psm2$p_holm <- p.adjust(
  as.numeric(treatment_results_psm2$P_value),
  method = "holm"                                   # Holm-Bonferroni
)

treatment_results_psm2$p_FDR <- p.adjust(
  as.numeric(treatment_results_psm2$P_value),
  method = "BH"                                    # Benjamini-Hochberg FDR
)


treatment_results_psm2 <- treatment_results_psm2 %>%
  mutate(
    across(
      c(P_value, p_bonferroni, p_holm, p_FDR),
      ~case_when(
        .x < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", .x)
      )
    )
  )

treatment_results_psm2

treatment_results_psm2 %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/treatment_adj_m_norec.docx"
  )


# ADDITIONAL MULTIPLE COMPARISONS

# Extract STENT rows only

gee_st_psm2 <- gee_table_final_psm2 %>%
  filter(grepl("^STENT", Predictor))

POSTUTI_st_psm2 <- POSTUTI_table_psm2 %>%
  filter(grepl("^STENT", Predictor))

# Combine only stent effects
st_results_psm2 <- rbind(
  gee_st_psm2,
  POSTUTI_st_psm2
)

# Apply Correction

st_results_psm2$p_bonferroni <- p.adjust(
  as.numeric(st_results_psm2$P_value),
  method = "bonferroni"                             # Bonferroni correction
)

st_results_psm2$p_holm <- p.adjust(
  as.numeric(st_results_psm2$P_value),
  method = "holm"                                   # Holm-Bonferroni
)

st_results_psm2$p_FDR <- p.adjust(
  as.numeric(st_results_psm2$P_value),
  method = "BH"                                    # Benjamini-Hochberg FDR
)


st_results_psm2 <- st_results_psm2 %>%
  mutate(
    across(
      c(P_value, p_bonferroni, p_holm, p_FDR),
      ~case_when(
        .x < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", .x)
      )
    )
  )

st_results_psm2

st_results_psm2 %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/stent_adj_m_norec.docx"
  )
```



#### Block 2i1 - without VUR recurrence

```{r reg2m_norec}

# Block 2: exposure-effect analysis (stent) on postoperative outcomes = Multivariable analyses

outcomes <- c(
  "LUTD",
  "OBST",
  "URCOMPINJ",
  "SURG",
  "ILEUS",
  "GU30",
  "GU90",
  "PROC365"
)

# convert outcomes to numeric
mdata[outcomes] <- lapply(
  mdata[outcomes],
  function(x) as.numeric(as.character(x))
)

# Predictors to include in the outcome models
predictors <- "TRT2 * STENT"


# Apply GEE model after overlap weighting for all binary outcomes
gee_results_psm2 <- lapply(outcomes, function(y) {
  formula <- as.formula(
    paste(y, "~",
          paste(predictors, collapse = " + ")
   )
  )  
  model <- geeglm(
    formula,
    data = mdata,
    id = CENTER,
    weights = weights_psm,    # weights have no effect because weights are all equal
    family = binomial(link = "logit"),
    corstr = "exchangeable"
  )
  tidy(model, exponentiate = TRUE, conf.int = TRUE)   # estimate = OR because exponentiate = TRUE
})
names(gee_results_psm2) <- outcomes

# Combine results into one table
gee_table_psm2 <- do.call(
  rbind,
  lapply(names(gee_results_psm2), function(x){
    tmp <- gee_results_psm2[[x]]
    tmp %>%
      mutate(outcome = x)
  })
)

# Create final manuscript table
gee_table_final_psm2 <- gee_table_psm2 %>%
  mutate(
    Effect_measure = "OR",
    Estimate = sprintf("%.2f", estimate),
    CI = paste0(
      sprintf("%.2f", conf.low),
      "–",
      sprintf("%.2f", conf.high)
    ),
    P_value = p.value
  ) %>%
  dplyr::select(
    Outcome = outcome,
    Predictor = term,
    Effect_measure,
    Estimate,
    CI,
    P_value
  )


# Cox model for POSTUTI

cox_uti_psm2 <- coxph(
  Surv(POSTUTIFUP, POSTUTI == 1) ~ TRT2*STENT + strata(CENTER),
  data = mdata,
  weights = weights_psm,  # weights have no effect
  robust = TRUE,
  cluster = subclass   
)

cox_summarypsm2 <- summary(cox_uti_psm2)

cox_row <- rownames(cox_summarypsm2$coefficients)

POSTUTI_table_psm2 <- data.frame(
  Outcome = "POSTUTI",
  Predictor = rownames(cox_summarypsm2$coefficients),
  Effect_measure = "HR",
  Estimate = sprintf(
    "%.2f",
    cox_summarypsm2$coefficients[
      cox_row,
      "exp(coef)"
    ]
  ),
  CI = paste0(
    sprintf("%.2f",
            cox_summarypsm2$conf.int[cox_row, "lower .95"]),
    "–",
    sprintf("%.2f",
            cox_summarypsm2$conf.int[cox_row, "upper .95"])
  ),
  P_value = cox_summarypsm2$coefficients[
    cox_row,
    "Pr(>|z|)"
  ]
)


# Combine final results
final_results_psm2 <- rbind(
  gee_table_final_psm2,
  POSTUTI_table_psm2
)


final_results_psm2

final_results_psm2 <- final_results_psm2 %>%
  mutate(
    across(
      c(P_value),
      ~case_when(
        .x < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", .x)
      )
    )
  )


final_results_psm2 %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/treatment_adj_all_m_norec_i.docx"
  )


# Multiple correction

# Extract TRT2 rows only

gee_trt2_psm2 <- gee_table_final_psm2 %>%
  filter(grepl("^TRT2", Predictor))

POSTUTI_trt2_psm2 <- POSTUTI_table_psm2 %>%
  filter(grepl("^TRT2", Predictor))

# Combine only treatment effects
treatment_results_psm2 <- rbind(
  gee_trt2_psm2,
  POSTUTI_trt2_psm2
)

# Apply Correction

treatment_results_psm2$p_bonferroni <- p.adjust(
  as.numeric(treatment_results_psm2$P_value),
  method = "bonferroni"                             # Bonferroni correction
)

treatment_results_psm2$p_holm <- p.adjust(
  as.numeric(treatment_results_psm2$P_value),
  method = "holm"                                   # Holm-Bonferroni
)

treatment_results_psm2$p_FDR <- p.adjust(
  as.numeric(treatment_results_psm2$P_value),
  method = "BH"                                    # Benjamini-Hochberg FDR
)


treatment_results_psm2 <- treatment_results_psm2 %>%
  mutate(
    across(
      c(P_value, p_bonferroni, p_holm, p_FDR),
      ~case_when(
        .x < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", .x)
      )
    )
  )

treatment_results_psm2

treatment_results_psm2 %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/treatment_adj_m_norec_i.docx"
  )


# ADDITIONAL MULTIPLE COMPARISONS

# Extract STENT rows only

gee_st_psm2 <- gee_table_final_psm2 %>%
  filter(grepl("^STENT", Predictor))

POSTUTI_st_psm2 <- POSTUTI_table_psm2 %>%
  filter(grepl("^STENT", Predictor))

# Combine only stent effects
st_results_psm2 <- rbind(
  gee_st_psm2,
  POSTUTI_st_psm2
)

# Apply Correction

st_results_psm2$p_bonferroni <- p.adjust(
  as.numeric(st_results_psm2$P_value),
  method = "bonferroni"                             # Bonferroni correction
)

st_results_psm2$p_holm <- p.adjust(
  as.numeric(st_results_psm2$P_value),
  method = "holm"                                   # Holm-Bonferroni
)

st_results_psm2$p_FDR <- p.adjust(
  as.numeric(st_results_psm2$P_value),
  method = "BH"                                    # Benjamini-Hochberg FDR
)


st_results_psm2 <- st_results_psm2 %>%
  mutate(
    across(
      c(P_value, p_bonferroni, p_holm, p_FDR),
      ~case_when(
        .x < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", .x)
      )
    )
  )

st_results_psm2

st_results_psm2 %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/stent_adj_m_norec_i.docx"
  )
```


#### Block 2i2 - without VUR recurrence + with interaction (to calculate OR for two levels) (secondary effect-modification analysis)

```{r reg2m_norec}

# Block 2: exposure-effect analysis (stent) on postoperative outcomes = Multivariable analyses

outcomes <- c(
  "LUTD",
  "OBST",
  "URCOMPINJ",
  "SURG",
  "ILEUS",
  "GU30",
  "GU90",
  "PROC365"
)

# convert outcomes to numeric
mdata[outcomes] <- lapply(
  mdata[outcomes],
  function(x) as.numeric(as.character(x))
)


# Apply GEE model after overlap weighting for all binary outcomes
get_gee_results_psm2 <- function(y) {
  
  formula <- as.formula(
    paste(y, "~ TRT2 * STENT")
  )
  
  model <- geeglm(
    formula,
    data = mdata,
    id = CENTER,
    weights = weights_psm,    # weights have no effect because weights are all equal
    family = binomial(link = "logit"),
    corstr = "exchangeable"
  )
  
  # Coefficients
  beta <- coef(model)
  
  # Robust covariance matrix
  V <- vcov(model)
  
  # -------------------------------------------------------
  # LG vs Cohen among NO-STENT patients
  # -------------------------------------------------------
  
  b_no_stent <- beta["TRT21"]
  
  se_no_stent <- sqrt(
    V["TRT21", "TRT21"]
  )
  
  OR_no_stent <- exp(b_no_stent)
  
  CI_no_stent <- exp(
    b_no_stent + c(-1, 1) * 1.96 * se_no_stent
  )
  
  # -------------------------------------------------------
  # LG vs Cohen among STENTED patients
  # = TRT21 + TRT21:STENT1
  # -------------------------------------------------------
  
  b_stent <- beta["TRT21"] +
    beta["TRT21:STENT1"]
  
  # Variance of the linear combination:
  # Var(beta1 + beta3)
  
  var_stent <-
    V["TRT21", "TRT21"] +
    V["TRT21:STENT1", "TRT21:STENT1"] +
    2 * V["TRT21", "TRT21:STENT1"]
  
  se_stent <- sqrt(var_stent)
  
  OR_stent <- exp(b_stent)
  
  CI_stent <- exp(
    b_stent + c(-1, 1) * 1.96 * se_stent
  )
  
  # -------------------------------------------------------
  # Interaction test
  # -------------------------------------------------------
  
  b_interaction <- beta["TRT21:STENT1"]
  
  se_interaction <- sqrt(
    V["TRT21:STENT1", "TRT21:STENT1"]
  )
  
  z_interaction <- b_interaction / se_interaction
  
  p_interaction <- 2 * pnorm(
    abs(z_interaction),
    lower.tail = FALSE
  )
  
  # -------------------------------------------------------
  # Return manuscript-ready results
  # -------------------------------------------------------
  
  data.frame(
    Outcome = y,
    
    `LG vs Cohen, No Stent` =
      sprintf(
        "%.2f (%.2f–%.2f)",
        OR_no_stent,
        CI_no_stent[1],
        CI_no_stent[2]
      ),
    
    `LG vs Cohen, Stent` =
      sprintf(
        "%.2f (%.2f–%.2f)",
        OR_stent,
        CI_stent[1],
        CI_stent[2]
      ),
    
    P_interaction = p_interaction,
    
    stringsAsFactors = FALSE
  )
}


# Run for all 8 outcomes
interaction_results_m <- do.call(
  rbind,
  lapply(outcomes, get_gee_results_psm2)
)


interaction_results_m


# Cox model for POSTUTI

cox_uti_psm2 <- coxph(
  Surv(POSTUTIFUP, POSTUTI == 1) ~ TRT2*STENT + strata(CENTER),
  data = mdata,
  weights = weights_psm,  # weights have no effect
  robust = TRUE,
  cluster = subclass   
)

# Coefficients
beta_cox <- coef(cox_uti_psm2)

# Covariance matrix
V_cox <- vcov(cox_uti_psm2)

# -------------------------------------------------------
# LG vs Cohen among NO-STENT patients
# -------------------------------------------------------

b_no_stent_cox <- beta_cox["TRT21"]

se_no_stent_cox <- sqrt(
  V_cox["TRT21", "TRT21"]
)

HR_no_stent <- exp(b_no_stent_cox)

CI_no_stent_cox <- exp(
  b_no_stent_cox +
    c(-1, 1) * 1.96 * se_no_stent_cox
)


# -------------------------------------------------------
# LG vs Cohen among STENTED patients
# = TRT21 + TRT21:STENT1
# -------------------------------------------------------

b_stent_cox <- beta_cox["TRT21"] +
  beta_cox["TRT21:STENT1"]

var_stent_cox <-
  V_cox["TRT21", "TRT21"] +
  V_cox["TRT21:STENT1", "TRT21:STENT1"] +
  2 * V_cox["TRT21", "TRT21:STENT1"]

se_stent_cox <- sqrt(var_stent_cox)

HR_stent <- exp(b_stent_cox)

CI_stent_cox <- exp(
  b_stent_cox +
    c(-1, 1) * 1.96 * se_stent_cox
)


# -------------------------------------------------------
# Interaction p-value
# -------------------------------------------------------

b_interaction_cox <- beta_cox["TRT21:STENT1"]

se_interaction_cox <- sqrt(
  V_cox["TRT21:STENT1", "TRT21:STENT1"]
)

z_interaction_cox <-
  b_interaction_cox / se_interaction_cox

p_interaction_cox <- 2 * pnorm(
  abs(z_interaction_cox),
  lower.tail = FALSE
)


# Create POSTUTI result
POSTUTI_interaction_m <- data.frame(
  Outcome = "POSTUTI",
  
  `LG vs Cohen, No Stent` =
    sprintf(
      "%.2f (%.2f–%.2f)",
      HR_no_stent,
      CI_no_stent_cox[1],
      CI_no_stent_cox[2]
    ),
  
  `LG vs Cohen, Stent` =
    sprintf(
      "%.2f (%.2f–%.2f)",
      HR_stent,
      CI_stent_cox[1],
      CI_stent_cox[2]
    ),
  
  P_interaction = p_interaction_cox
)

POSTUTI_interaction_m

```

### 4 Rosenbaum's sensitivity analyses 

```{r rosenbaum}

# Rosenbaum's primal sensitivity analysis

outcomes <- c(
  "LUTD",
  "OBST",
  "URCOMPINJ",
  "SURG",
  "ILEUS",
  "GU30",
  "GU90",
  "PROC365"
)

# Convert outcomes to numeric
mdata[outcomes] <- lapply(
  mdata[outcomes],
  function(x) as.numeric(as.character(x))
)


# Function for Rosenbaum sensitivity analysis using rbounds
rosenbaum_binary <- function(outcome, data, match_object, 
                             gamma_seq = seq(1, 11, by = 0.1),
                            alpha = 0.05) {  
  
  # matched pairs
  treated_ids <- rownames(match_object$match.matrix)
  control_ids <- match_object$match.matrix[, 1]
  
  pairs <- data.frame(
    treated = data[treated_ids, outcome],
    control = data[control_ids, outcome]
  )
  
  # remove missing outcome pairs
  pairs <- na.omit(pairs)
  
  # discordant pairs
  # x = control has outcome, treated does not
  # y = treated has outcome, control does not
  x <- sum(pairs$control == 1 & pairs$treated == 0)
  y <- sum(pairs$treated == 1 & pairs$control == 0)
  
  # run Rosenbaum sensitivity
  if ((x + y) == 0) {
    return(data.frame(
      Outcome = outcome,
      Discordant_pairs = 0,
      x = x,
      y = y,
      p_Gamma1 = NA,
      gamma_max = NA,
      p_gamma_max = NA
    ))
  }
  
  # Run sensitivity over Gamma values

  gamma_results <- sapply(gamma_seq, function(g) {
    
  res <- binarysens(
      x = x,
      y = y,
      Gamma = g,
      GammaInc = 0.1  # GammaInc defines the increment used to increase Γ values when the function evaluates sensitivity.
    )

    # extract upper bound p-value corresponding to Gamma g
    res$bounds$`Upper bound`[
      res$bounds$Gamma == g
    ]
  })
  
    # p-value at Gamma = 1
    p_gamma1 <- gamma_results[gamma_seq == 1]
  
    # first Gamma where upper p-value >= alpha
    idx <- which(gamma_results < alpha)

if(length(idx) == 0){

  if(p_gamma1 >= alpha){
    
    gamma_max <- "NS at Gamma=1"
    p_gamma_max <- NA
    
  } else {
    
    gamma_max <- paste0(">=", max(gamma_seq))
    p_gamma_max <- gamma_results[length(gamma_results)]
    
  }

} else {
  
  gamma_max_value <- gamma_seq[max(idx)]
  
  # If still significant at the maximum tested Gamma
  if(gamma_max_value == max(gamma_seq)){
    
    gamma_max <- paste0(">=", max(gamma_seq))
    
  } else {
    
    gamma_max <- gamma_max_value
    
  }
  
  p_gamma_max <- gamma_results[max(idx)]
}

  # Extract p-values from rbounds object
  data.frame(
    Outcome = outcome,
    Discordant_pairs = x + y,
    x = x,
    y = y,
    p_Gamma1 = round(p_gamma1, 3),
    gamma_max = gamma_max,
    p_gamma_max = round(p_gamma_max, 3)
  )
}


# Run all outcomes
rosenbaum_results <- do.call(
  rbind,
  lapply(
    outcomes,
    rosenbaum_binary,
    data = mdata,
    match_object = m.out
  )
)

rosenbaum_results


# Rename columns for publication
rosenbaum_results_pub <- rosenbaum_results %>%
  rename(
    Outcome = Outcome,
    `Discordant pairs` = Discordant_pairs,
    `Control only events (x)` = x,
    `Treated only events (y)` = y,
    `P-value (Γ=1)` = p_Gamma1,
    `Γmax` = gamma_max,
    `P-value at Γmax` = p_gamma_max
  )


# Create publication table
rosenbaum_table <- rosenbaum_results_pub %>%
  flextable() %>%
  
  # Add title
  add_header_lines(
    "Rosenbaum’s primal sensitivity analysis for postoperative outcomes in the matched cohort."
  ) %>%
  
  # Add footnote
  add_footer_lines(
    "The Gamma value Γ is a measure of sensitivity to hidden bias, representing the magnitude of differential odds of treatment assignment due to an unmeasured confounder that could alter the study conclusion. Γmax refers to the highest value of Γ for which the upper-bound p-value remained below 0.05. P-values correspond to the upper bound."
  ) %>%
  
  theme_booktabs() %>%
  autofit() %>%
  
  align(
    j = c(
      "Discordant pairs",
      "Control only events (x)",
      "Treated only events (y)",
      "P-value (Γ=1)",
      "Γmax",
      "P-value at Γmax"
    ),
    align = "center",
    part = "all"
  )


# Save as Word document
save_as_docx(
  rosenbaum_table,
  path = "output/Rosenbaum_effect.docx"
)

```


### 5 PAIN - Non-epidural Cohort

#### 5.1 Filter & match the new population

```{r filterpain}

# Filter dataset to only those who did not receive EPIDURAL
Outp <- Out %>%
  filter(EPIDURAL == "0") %>%
  mutate(
    PAIN = factor(
      PAIN,
      levels = c("0", "1", "2", "3"),
      labels = c(
        "No pain",
        "Mild pain (score 1-3)",
        "Moderate pain (score 4-6)",
        "Severe pain (score 7-10)"
      ),
      ordered = TRUE
    )
  )

# Do matching

set.seed(123)

m.outp <- matchit(
  TRT2 ~ AGS + YEARS + GENDER + BMI + PREOPRNPLN + HISTOINJ +
    SURGIND2 + PREOPVURGRADE + VURSIDE + UDR7M + VURPHASE +
    PREOPEPISODE1 + PREOPTYPEU1 + PREOPRNSCR + SURGTECH2,
  data = Outp,
  method = "nearest",
  ratio = 1,  # 1:1 matching (1 treated : 1 control)
  distance = "logit",
  caliper = 0.2   
)


mdatap <- match.data(
  m.outp,
  weights = "weightsp_psm" 
)
readr::write_csv(mdatap, "data/matched_nonepidural_data.csv") 



# Table for balance
# This gives: SMD before and after matching, and flagged imbalance (>0.1)
balmp <- cobalt::bal.tab(m.outp, un = TRUE, ESS = TRUE, m.threshold = 0.1)
balmp 

balmp_df <- as.data.frame(balmp$Balance)
smd_tablemp <- balmp_df %>%
  mutate(
    Variable = rownames(balmp_df),
    SMD_Before = round(abs(Diff.Un), 3),
    SMD_After  = round(abs(Diff.Adj), 3)
  ) %>%
  dplyr::select(Variable, SMD_Before, SMD_After) 

smd_tablemp %>%
  flextable() %>%
  save_as_docx(path = "output/SMD_psm_p.docx")



# Figure for balance - Love plot
plmp <- love.plot(
  m.outp,
  threshold = 0.1,
  abs = TRUE, 
  stats = "mean.diffs",      
  var.order = "unadjusted", 
  drop.distance = TRUE,   
  sample.names = c("Before matching", "After matching"),
    size = 4,
    var.names = c(
    AGS = "Age at surgery",
    YEARS = "Year of surgery",
    BMI = "Body mass index",
    GENDER = "Female gender",
    PREOPRNPLN = "Preop pyelonephritis",
    HISTOINJ = "History of injection",
    VURSIDE = "Right-sided VUR",
    UDR7M = "Ureteral dilation ≥ 7mm",
    PREOPTYPEU1 = "Preop febrile UTIs",
    PREOPRNSCR = "Preop renal scarring",
    VURPHASE_1 = "Reflux: voiding phase",
    VURPHASE_2 = "Reflux: filling phase",
    VURPHASE_3 = "Reflux: filling + voiding",
    SURGTECH2_1 = "Surgeon experience ≥100 operations",
    SURGTECH2_2 = "Surgeon experience 50-100 operations",
    SURGTECH2_3 = "Surgeon experience <50 operations",
    PREOPEPISODE1_1 = "Preop UTI episodes: 1",
    PREOPEPISODE1_2 = "Preop UTI episodes: 2",
    PREOPEPISODE1_3 = "Preop UTI episodes: ≥3",
    SURGIND2_1 = "Indication: breakthrough UTI",
    SURGIND2_2 = "Indication: high-grade reflux (III-V)",
    SURGIND2_3 = "Indication: poor compliance to medical treatment",
    SURGIND2_4 = "Indication: ineffective/poorly tolerated CAP",
    SURGIND2_5 = "Indication: other",
    PREOPVURGRADE_3 = "Preop VUR grade: III",
    PREOPVURGRADE_4 = "Preop VUR grade: IV",
    PREOPVURGRADE_5 = "Preop VUR grade: V"
  )
  )

plmp <- plmp +
    labs(
    x = "Absolute Standardized Differences",
    subtitle = "Matched population of children who did not receive epidural analgesia"
  )
    theme(
      plot.margin = margin(10, 10, 10, 10),
      axis.text = element_text(size = 16),
      axis.title = element_text(size = 16),
      plot.title = element_text(size = 16),
      legend.text = element_text(size = 16),
      legend.title = element_text(size = 16),
      axis.ticks = element_line(size = 0.5, color = "black"),
      axis.line = element_line(size = 0.5, color = "black"),
      panel.background = element_blank(), 
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      axis.ticks.length = unit(0.3, "cm"),
      panel.spacing = unit(2, "lines")
   )

ggsave ("figures/love_plot_pm.png", plot = plmp, width = 12, height = 10, dpi = 300)

# Compute mean SMD
smdmp_df <- balmp$Balance
mean_smdmp_before <- mean(abs(smdmp_df$Diff.Un), na.rm = TRUE) 
mean_smdmp_after <- mean(abs(smdmp_df$Diff.Adj), na.rm = TRUE) 
mean_smdmp <- data.frame(
  Mean_SMDmp_Before = mean_smdmp_before,
  Mean_SMDmp_After = mean_smdmp_after
)

mean_smdmp


# how much effective sample size remains (overall ESS: calculated manually)?
summary(m.outp$weights)
bal.tab(m.outp)$Effective.Sample.Size
sum(m.outp$weights)^2 / sum(m.outp$weights^2)



# propensity score distribution
summary(m.outp$distance)
hist(m.outp$distance)

ggplot(
  data.frame(
    ps = m.outp$distance,
    Treatment  = factor(Outp$Treatment)
  ),
  aes(ps, fill = Treatment)
) +
  geom_histogram(alpha = 0.5, bins = 30, position = "identity",   color = "black", linewidth = 0.3 ) +
    scale_fill_viridis_d(
    option = "mako",
    begin = 0.3,
    end = 0.8,
    labels = c("Cohen", "Lich–Gregoir")
  ) +
  labs(
    x = "Propensity score",
    y = "Count",
    fill = "Treatment"
  ) +
  theme_bw()

ggsave("figures/propensity_psm_p.png",
       width = 12,
       height = 10,
       dpi = 300)


# Distributional balance for propensity score 

# Before-After weighting
p_psm_pain <- bal.plot(
  m.outp,
  var.name = "distance",
  type = "density",
  which = "both"
) 

p_psm_pain <- p_psm_pain +
  scale_color_viridis_d(
    option = "mako",
    begin = 0.3,
    end = 0.8,
    labels = c("Cohen group", "Lich–Gregoir group")
  ) +
  scale_fill_viridis_d(
    option = "mako",
    begin = 0.3,
    end = 0.8,
    labels = c("Cohen group", "Lich–Gregoir group")
  )

ggsave(
  "figures/PS_density_before_after_pm.png",
  p_psm_pain,
  width = 10,
  height = 7,
  dpi = 300
)

```
 
#### 5.2 Descriptive analysis

```{r painw}

# mdatap is the dataset with added weightsp_psm

# Convert variables to appropriate data types for analysis
mdatap <- mdatap %>%
  mutate(
    across(c(PID, QCODE), as.character),
    
    across(c(AGS, YEARS,BLDLOSS, BMI, CATHPERIOD, FUPM, HOSPTIME,OPRTIME,
             POSTUTIFUP, POSTUTI_T), as.numeric),
    
    across(c(ANASTOMO,BLDCOMPLEAK,BLDCOMPRETN,
             BLDCOMPVOID,BLDSPASM,CATH,CENTER,CLAVIENCLASS,EPIDURAL,GENDER,
             GU30, GU90N, GUER30, GUER90, HEMAT, 
             HISTOINJ,ILEUS, INCCOMPBLEED, INCCOMPINF, INCCOMPSCAR, NARC, 
             NONARC, PAIN, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR, PREOPTYPEU1,
             PREOPVURGRADE, PROC365, STENT, SURGIND, SURGTECH2, TRT2, UDR7M,
             URCOMPCVUR, URCOMPINJ, URCOMPOBST, URCOMPSTEN, POSTUTI, VURPHASE,
             VURSIDE, RECGRADE_MAX, SURGIND2, LUTD, OBST, SURG, GU90,
             CATHPERIOD_G, ANY, MINOR, MAJOR), as.factor)
  )

str(mdatap)


# Matched baseline characteristics
table1mp<- mdatap %>%
  select(YEARS, AGS, GENDER, BMI, HISTOINJ, SURGIND2, PREOPVURGRADE, VURSIDE, UDR7M, VURPHASE, PREOPTYPEU1, PREOPEPISODE1, PREOPRNPLN, PREOPRNSCR,
         SURGTECH2, CENTER, TRT2
  ) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",  # shows missing only when present
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  
  bold_labels()

table1mp <- table1mp %>%
  modify_caption(
    "Baseline characteristics after 1:1 propensity score matching among children who did not receive epidural analgesia"
  )

table1mp %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/baseline_m_pain.docx")


# Matched procedural factors
table2mp<- mdatap %>%
  select(TRT2, OPRTIME, STENT, CATH, CATHPERIOD, CATHPERIOD_G, HOSPTIME) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})", # or ~ "{mean} ± {sd}",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%  #  3 decimals 
  bold_labels()

table2mp

table2mp %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/procedural_m_pain.docx")


# Matched pain

# Before matching

table4 <- Outp %>%
  dplyr::select(PAIN, NARC, NONARC, Treatment) %>%
  tbl_summary(
    by = Treatment,
    statistic = list(
      all_categorical() ~ "{n} ({p}%)"
    ),
    label = list(
      PAIN ~ "Pain score",
      NARC ~ "Narcotic use",
      NONARC ~ "Non-narcotic use"
    ),
    digits = all_categorical() ~ c(0, 1),
    missing = "ifany",
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>%
  bold_labels()


# After matching 


# Matched pain characteristics

table4m<- mdatap %>%
  select(PAIN, NARC, NONARC, TRT2
  ) %>%
  tbl_summary(
    by = TRT2,  # for stratification
    statistic = list(
      all_continuous() ~ "{median} ({p25}-{p75})",
      all_categorical() ~ "{n} ({p}%)" 
    ),
    label = list(
      PAIN ~ "Pain score",
      NARC ~ "Narcotic use",
      NONARC ~ "Non-narcotic use"
    ),
    digits = all_categorical() ~ c(0, 1),  # n = 0 decimals, p = 1 decimal
    missing = "ifany",  # shows missing only when present
    missing_text = "Missing"
  ) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3)) %>% 
  bold_labels()

table4m <- table4m %>%
  modify_caption(
    "Pain characteristics after 1:1 propensity score matching among children who did not receive epidural analgesia"
  )


# MERGE TABLES
table_combined_m <- tbl_merge(
  tbls = list(table4, table4m),
  tab_spanner = c("**Before matching**", "**After matching**")
) %>%
  modify_caption(
    "Table 4. Comparison of pain intensity and analgesic use between treatment groups before and after propensity score 1:1 matching."
) %>%
  modify_source_note(
    "Analysis restricted to patients not receiving epidural analgesia."
  )

table_combined_m

table_combined_m %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "output/pain_m.docx")

```

#### 5.3 Plot:  BEFORE-AFTER matching

```{r painplotm}

# ============================================================
# Pain distribution before and after 1:1 propensity-score matching
# Non-epidural subgroup
# ============================================================

# -----------------------------
# 1. Prepare datasets
# -----------------------------

# Before matching: all children without epidural analgesia
before <- Outp %>%
  mutate(
    plot_weight = 1,
    Status = "Before matching (N=383), p<0.001"
  )

# After matching: matched non-epidural population
after <- mdatap %>%
  mutate(
    plot_weight = weightsp_psm,
    Status = "After matching (N=180), p<0.001"
  )

# -----------------------------
# 2. Combine datasets
# -----------------------------

plot_data <- bind_rows(before, after)

# -----------------------------
# 3. Pain labels
# -----------------------------


plot_data <- plot_data %>%
  mutate(
    PAIN_plot = factor(
      PAIN,
      levels = levels(PAIN),
      labels = c(
        "No pain", 
        "Mild pain", 
        "Moderate pain", 
        "Severe pain"
        )
      )
    )

# -----------------------------
# 4. Define order of panels
# -----------------------------

plot_data <- plot_data %>%
  mutate(
    Status = factor(
      Status,
      levels = c(
        "Before matching (N=383), p<0.001",
        "After matching (N=180), p<0.001"
      )
    )
  )


# ============================================================
# Figure : 100% stacked bar plot
# ============================================================

plot_summary1 <- plot_data %>%
  group_by(Status, Treatment, PAIN_plot) %>%
  summarise(
    weighted_n = sum(plot_weight, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(Status, Treatment) %>%
  mutate(
    Percent = 100 * weighted_n / sum(weighted_n)
  )


s1 <- ggplot(
  plot_summary1,
  aes(
    x = Treatment,
    y = Percent,
    fill = PAIN_plot
  )
) +
  geom_bar(
    stat = "identity",
    position = "fill",
    width = 0.7
  ) +
  facet_wrap(~Status) +
  labs(
    x = "Treatment groups",
    y = "Percentage of patients not receiving epidural analgesia (%)",
    fill = "1-Day postoperative pain score"
  ) +
  scale_fill_manual(
    values = c(
      "No pain" = "#f5f5f5",
      "Mild pain" = "#fee8c8",
      "Moderate pain" = "#fdbb84",
      "Severe pain" = "#e34a33"
    )
  ) +
  scale_y_continuous(
    labels = scales::percent_format(scale = 100)
  ) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 11),
    panel.border = element_rect(
      color = "black",
      fill = NA
    ),
    strip.text = element_text(
      face = "bold"
    ),
    panel.spacing = unit(
      0,
      "lines"
    )
  )


ggsave(
  filename = "figures/pain_stacked_m.png",
  plot = s1,
  width = 9,
  height = 6,
  dpi = 300
)
```


#### 5.4 Regression

```{r regpain}

# -----------------------------------------
### Moderate-severe pain vs. Other levels
# -----------------------------------------

mdatap <- mdatap %>%
  mutate(
    PAIN_ms = factor(
      ifelse(
        PAIN %in% c(
          "Moderate pain (score 4-6)",
          "Severe pain (score 7-10)"
        ),
        1,
        0
      ),
      levels = c(0, 1),
      labels = c(
        "No/Mild pain (score 0-3)",
        "Moderate-Severe pain (score 4-10)"
      )
    )
  )


mdatap$PAIN_ms <- ifelse(
  mdatap$PAIN_ms == "Moderate-Severe pain (score 4-10)",
  1,
  0
)

# -----------------------------------------------------
### Exploratory analysis: Severe pain vs. Other levels
# -----------------------------------------------------

mdatap <- mdatap %>%
  mutate(
    PAIN_s = factor(
      ifelse(
        PAIN == "Severe pain (score 7-10)",
        1,
        0
      ),
      levels = c(0, 1),
      labels = c(
        "No severe pain (score 0-6)",
        "Severe pain (score 7-10)"
      )
    )
  )

# a numeric binary outcome:
mdatap$PAIN_s <- ifelse(
  mdatap$PAIN_s == "Severe pain (score 7-10)",
  1,
  0
)

#----------
# Block 1
#----------

outcomes <- c(
  "PAIN_ms",
  "PAIN_s"
)

# convert outcomes to numeric
mdatap[outcomes] <- lapply(
  mdatap[outcomes],
  function(x) as.numeric(as.character(x))
)

# Apply GEE model after matching for all binary outcomes
gee_results_psmp <- lapply(outcomes, function(y) {
  formula <- as.formula(
    paste(y, "~ TRT2")
  )
  model <- geeglm(
    formula,
    data = mdatap,
    id = CENTER,
    weights = weightsp_psm,
    family = binomial(link = "logit"),
    corstr = "exchangeable"
  )
  tidy(model, exponentiate = TRUE, conf.int = TRUE)   # estimate = OR because exponentiate = TRUE
})
names(gee_results_psmp) <- outcomes


# Combine results into one table
gee_table_psmp <- do.call(
  rbind,
  lapply(names(gee_results_psmp), function(x){
    tmp <- gee_results_psmp[[x]]
    tmp <- tmp %>%
      filter(grepl("^TRT2", term)) %>%
      mutate(outcome = x)
    tmp
  })
)

# Create final manuscript table
gee_table_final_psmp <- gee_table_psmp %>%
  mutate(
    Effect_measure = "OR",
    Estimate = sprintf("%.2f", estimate),
    CI = paste0(
      sprintf("%.2f", conf.low),
      "–",
      sprintf("%.2f", conf.high)
    ),
    P_value = ifelse(p.value < 0.001, "<0.001", sprintf("%.3f", p.value))
  ) %>%
  dplyr::select(
    Outcome = outcome,
    Effect_measure,
    Estimate,
    CI,
    P_value
  )

gee_table_final_psmp

gee_table_final_psmp %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/pain_unadj_m.docx"
  )


#--------
# Block 2
#---------

outcomes <- c(
  "PAIN_ms",
  "PAIN_s"
)


# convert outcomes to numeric
mdatap[outcomes] <- lapply(
  mdatap[outcomes],
  function(x) as.numeric(as.character(x))
)

# Predictors to include in the outcome models
predictors <- c("TRT2", "STENT")


# Apply GEE model after overlap weighting for all binary outcomes
gee_results_psmp <- lapply(outcomes, function(y) {
  formula <- as.formula(
    paste(y, "~",
          paste(predictors, collapse = " + ")
   )
  )  
  model <- geeglm(
    formula,
    data = mdatap,
    id = CENTER,
    weights = weightsp_psm,
    family = binomial(link = "logit"),
    corstr = "exchangeable"
  )
  tidy(model, exponentiate = TRUE, conf.int = TRUE)   # estimate = OR because exponentiate = TRUE
})
names(gee_results_psmp) <- outcomes

# Combine results into one table
gee_table_psmp <- do.call(
  rbind,
  lapply(names(gee_results_psmp), function(x){
    tmp <- gee_results_psmp[[x]]
    tmp %>%
      mutate(outcome = x)
  })
)

# Create final manuscript table
gee_table_final_psmp <- gee_table_psmp %>%
  mutate(
    Effect_measure = "OR",
    Estimate = sprintf("%.2f", estimate),
    CI = paste0(
      sprintf("%.2f", conf.low),
      "–",
      sprintf("%.2f", conf.high)
    ),
    P_value = ifelse(p.value < 0.001, "<0.001", sprintf("%.3f", p.value))
  ) %>%
  dplyr::select(
    Outcome = outcome,
    Predictor = term,
    Effect_measure,
    Estimate,
    CI,
    P_value
  )

gee_table_final_psmp

gee_table_final_psmp %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    j = c("Estimate", "CI", "P_value"),
    align = "center",
    part = "all"
  ) %>%
  save_as_docx(
    path = "output/pain_adj_m.docx"
  )


#------------------------
# Block 2ai- Interaction
#------------------------

outcomes <- c(
  "PAIN_ms",
  "PAIN_s"
)


# convert outcomes to numeric
mdatap[outcomes] <- lapply(
  mdatap[outcomes],
  function(x) as.numeric(as.character(x))
)

# Function to extract treatment effects within each stent stratum
get_gee_interaction_results <- function(y) {
  
  formula <- as.formula(
    paste(y, "~ TRT2 * STENT")
  )
  
  model <- geeglm(
    formula,
    data = mdatap,
    id = CENTER,
    weights = weightsp_psm,
    family = binomial(link = "logit"),
    corstr = "exchangeable"
  )
  
  # Coefficients
  beta <- coef(model)
  
  # Robust covariance matrix
  V <- vcov(model)
  
  # -------------------------------------------------------
  # LG vs Cohen among NO-STENT patients
  # -------------------------------------------------------
  
  b_no_stent <- beta["TRT21"]
  
  se_no_stent <- sqrt(
    V["TRT21", "TRT21"]
  )
  
  OR_no_stent <- exp(b_no_stent)
  
  CI_no_stent <- exp(
    b_no_stent + c(-1, 1) * 1.96 * se_no_stent
  )
  
  # -------------------------------------------------------
  # LG vs Cohen among STENTED patients
  # = TRT21 + TRT21:STENT1
  # -------------------------------------------------------
  
  b_stent <- beta["TRT21"] +
    beta["TRT21:STENT1"]
  
  # Variance of the linear combination:
  # Var(beta1 + beta3)
  
  var_stent <-
    V["TRT21", "TRT21"] +
    V["TRT21:STENT1", "TRT21:STENT1"] +
    2 * V["TRT21", "TRT21:STENT1"]
  
  se_stent <- sqrt(var_stent)
  
  OR_stent <- exp(b_stent)
  
  CI_stent <- exp(
    b_stent + c(-1, 1) * 1.96 * se_stent
  )
  
  # -------------------------------------------------------
  # Interaction test
  # -------------------------------------------------------
  
  b_interaction <- beta["TRT21:STENT1"]
  
  se_interaction <- sqrt(
    V["TRT21:STENT1", "TRT21:STENT1"]
  )
  
  z_interaction <- b_interaction / se_interaction
  
  p_interaction <- 2 * pnorm(
    abs(z_interaction),
    lower.tail = FALSE
  )
  
  # -------------------------------------------------------
  # Return manuscript-ready results
  # -------------------------------------------------------
  
  data.frame(
    Outcome = y,
    
    `LG vs Cohen, No Stent` =
      sprintf(
        "%.2f (%.2f–%.2f)",
        OR_no_stent,
        CI_no_stent[1],
        CI_no_stent[2]
      ),
    
    `LG vs Cohen, Stent` =
      sprintf(
        "%.2f (%.2f–%.2f)",
        OR_stent,
        CI_stent[1],
        CI_stent[2]
      ),
    
    P_interaction = p_interaction,
    
    stringsAsFactors = FALSE
  )
}


# Run for all 2 outcomes
interaction_results <- do.call(
  rbind,
  lapply(outcomes, get_gee_interaction_results)
)


interaction_results
```

#### 5.5 Rosenbaum's sensitivity analyses 

```{r rosenbaum}

# Rosenbaum's primal sensitivity analysis

outcomes <- c(
  "PAIN_ms",
  "PAIN_s"
)

# Convert outcomes to numeric
mdatap[outcomes] <- lapply(
  mdatap[outcomes],
  function(x) as.numeric(as.character(x))
)


# Function for Rosenbaum sensitivity analysis using rbounds
rosenbaum_binary <- function(outcome, data, match_object, 
                             gamma_seq = seq(1, 11, by = 0.1),
                            alpha = 0.05) {  
  
  # matched pairs
  treated_ids <- rownames(match_object$match.matrix)
  control_ids <- match_object$match.matrix[, 1]
  
  pairs <- data.frame(
    treated = data[treated_ids, outcome],
    control = data[control_ids, outcome]
  )
  
  # remove missing outcome pairs
  pairs <- na.omit(pairs)
  
  # discordant pairs
  # x = control has outcome, treated does not
  # y = treated has outcome, control does not
  x <- sum(pairs$control == 1 & pairs$treated == 0)
  y <- sum(pairs$treated == 1 & pairs$control == 0)
  
  # run Rosenbaum sensitivity
  if ((x + y) == 0) {
    return(data.frame(
      Outcome = outcome,
      Discordant_pairs = 0,
      x = x,
      y = y,
      p_Gamma1 = NA,
      gamma_max = NA,
      p_gamma_max = NA
    ))
  }
  
  # Run sensitivity over Gamma values

  gamma_results <- sapply(gamma_seq, function(g) {
    
  res <- binarysens(
      x = x,
      y = y,
      Gamma = g,
      GammaInc = 0.1  # GammaInc defines the increment used to increase Γ values when the function evaluates sensitivity.
    )

    # extract upper bound p-value corresponding to Gamma g
    res$bounds$`Upper bound`[
      res$bounds$Gamma == g
    ]
  })
  
    # p-value at Gamma = 1
    p_gamma1 <- gamma_results[gamma_seq == 1]
  
    # first Gamma where upper p-value >= alpha
    idx <- which(gamma_results < alpha)

if(length(idx) == 0){

  if(p_gamma1 >= alpha){
    
    gamma_max <- "NS at Gamma=1"
    p_gamma_max <- NA
    
  } else {
    
    gamma_max <- paste0(">=", max(gamma_seq))
    p_gamma_max <- gamma_results[length(gamma_results)]
    
  }

} else {
  
  gamma_max_value <- gamma_seq[max(idx)]
  
  # If still significant at the maximum tested Gamma
  if(gamma_max_value == max(gamma_seq)){
    
    gamma_max <- paste0(">=", max(gamma_seq))
    
  } else {
    
    gamma_max <- gamma_max_value
    
  }
  
  p_gamma_max <- gamma_results[max(idx)]
}

  # Extract p-values from rbounds object
  data.frame(
    Outcome = outcome,
    Discordant_pairs = x + y,
    x = x,
    y = y,
    p_Gamma1 = round(p_gamma1, 3),
    gamma_max = gamma_max,
    p_gamma_max = round(p_gamma_max, 3)
  )
}


# Run all outcomes
rosenbaum_results <- do.call(
  rbind,
  lapply(
    outcomes,
    rosenbaum_binary,
    data = mdatap,
    match_object = m.outp
  )
)

rosenbaum_results


# Rename columns for publication
rosenbaum_results_pub <- rosenbaum_results %>%
  rename(
    Outcome = Outcome,
    `Discordant pairs` = Discordant_pairs,
    `Control only events (x)` = x,
    `Treated only events (y)` = y,
    `P-value (Γ=1)` = p_Gamma1,
    `Γmax` = gamma_max,
    `P-value at Γmax` = p_gamma_max
  )


# Create publication table
rosenbaum_tablep <- rosenbaum_results_pub %>%
  flextable() %>%
  
  # Add title
  add_header_lines(
    "Rosenbaum’s primal sensitivity analysis for pain in the matched cohort."
  ) %>%
  
  # Add footnote
  add_footer_lines(
    "The Gamma value Γ is a measure of sensitivity to hidden bias, representing the magnitude of differential odds of treatment assignment due to an unmeasured confounder that could alter the study conclusion. Γmax refers to the highest value of Γ for which the upper-bound p-value remained below 0.05. P-values correspond to the upper bound."
  ) %>%
  
  theme_booktabs() %>%
  autofit() %>%
  
  align(
    j = c(
      "Discordant pairs",
      "Control only events (x)",
      "Treated only events (y)",
      "P-value (Γ=1)",
      "Γmax",
      "P-value at Γmax"
    ),
    align = "center",
    part = "all"
  )


# Save as Word document
save_as_docx(
  rosenbaum_tablep,
  path = "output/Rosenbaum_effect_pain.docx"
)

```

# TEMPORAL CHANGES

### Number of procedures per year

#### Plots

```{r trtplot}

#---------------------------------------
# Horizontal bar for each year
#---------------------------------------

# -----------------
# The whole cohort
# -----------------

plot_data1 <- Out %>%
  count(YEARS, Treatment) %>%
  group_by(Treatment) %>%
  mutate(
    Percent = 100 * n / sum(n)
  ) %>%
  ungroup()

p_y_m1 <- ggplot(
  plot_data1,
  aes(
    x = Percent,
    y = factor(YEARS),
    fill = Treatment
  )
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7,
    colour = "black"
  ) +
  scale_x_continuous(
    limits = c(0, 100),
    breaks = seq(0, 100, 20),
    expand = expansion(mult = c(0, 0.02))
  ) +
  scale_fill_viridis_d(option = "mako", begin = 0.3, end = 0.8
  ) +
  labs(x = "Proportion", y = "Year of Surgery", fill = "Treatment Group") +
  theme_classic()

p_y_m1


# ---------------------
# After ATO weighting
# ---------------------

plot_data_ato <- Out %>%
  group_by(YEARS, Treatment) %>%
  summarise(
    weighted_n = sum(weights),
    .groups = "drop"
  ) %>%
  group_by(Treatment) %>%
  mutate(
    Percent = 100 * weighted_n / sum(weighted_n)
  ) %>%
  ungroup()

p_y_m_ato <- ggplot(
  plot_data_ato,
  aes(
    x = Percent,
    y = factor(YEARS),
    fill = Treatment
  )
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7,
    colour = "black"
  ) +
  scale_x_continuous(
    limits = c(0, 100),
    breaks = seq(0, 100, 20),
    expand = expansion(mult = c(0, 0.02))
  ) +
  scale_fill_viridis_d(
    option = "mako",
    begin = 0.3,
    end = 0.8
  ) +
  labs(
    x = "Proportion",
    y = "Year of Surgery",
    fill = "Group"
  ) +
  theme_classic()

p_y_m_ato



# -----------------
# After matching
# -----------------

plot_data <- mdata %>%
  count(YEARS, Treatment) %>%
  group_by(Treatment) %>%
  mutate(
    Percent = 100 * n / sum(n)
  ) %>%
  ungroup()

p_y_m <- ggplot(
  plot_data,
  aes(
    x = Percent,
    y = factor(YEARS),
    fill = Treatment
  )
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7,
    colour = "black"
  ) +
  scale_x_continuous(
    limits = c(0, 100),
    breaks = seq(0, 100, 20),
    expand = expansion(mult = c(0, 0.02))
  ) +
  scale_fill_viridis_d(option = "mako", begin = 0.3, end = 0.8
  ) +
  labs(x = "Proportion", y = "Year of Surgery", fill = "Group") +
  theme_classic()

p_y_m

#------------------------------------------------------------
# Add subtitle (we can keep or remove them from the final figure)
#------------------------------------------------------------

p_y_m1 <- p_y_m1 +
  labs(subtitle = "Whole cohort")


p_y_m_ato <- p_y_m_ato +
  labs(subtitle = "Overlap weighting population")

p_y_m <- p_y_m +
  labs(subtitle = "Matched cohort")

#------------------------------------------------------------
# Combine plot 
#------------------------------------------------------------

treatment_plot <-
  p_y_m1 /
  p_y_m_ato /
  p_y_m +
  plot_layout(heights = c(2,2,2)) +
  plot_annotation(
    tag_levels = "A"
  )

#------------------------------------------------------------
# Save the figure
#------------------------------------------------------------

ggsave(filename = "figures/treatment_across_years.png", 
       plot = treatment_plot, 
       width = 8,   # width in inches
       height = 10,  # height in inches
       dpi = 300)   # resolution

```

#### Table

```{r trttable}

# -----------------
# The whole cohort
# -----------------
year_table <- Out %>%
  count(YEARS, Treatment) %>%
  group_by(YEARS) %>%
  mutate(
    Percent = 100 * n / sum(n),
    n_percent = paste0(n, " (", round(Percent, 1), "%)")
  ) %>%
  select(YEARS, Treatment, n_percent) %>%
  pivot_wider(
    names_from = Treatment,
    values_from = n_percent
  ) %>%
  left_join(
    Out %>%
      count(YEARS, name = "Total_n") %>%
      mutate(
        Total_percent = 100 * Total_n / nrow(Out),
        Total = paste0(Total_n, " (", round(Total_percent, 1), "%)")
      ) %>%
      select(YEARS, Total),
    by = "YEARS"
  ) %>%
  arrange(YEARS)

year_table <- year_table %>%
  rename(
    `Year of Surgery` = YEARS,
    `Cohen n (%)` = Cohen,
    `Lich–Gregoir n (%)` = `Lich–Gregoir`,
    `Total surgeries` = Total
  )

year_table %>%
  gt()

year_table


year_table <- year_table %>%
  mutate(
    `Year of Surgery` = as.character(`Year of Surgery`)
  )

year_table %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    align = "center",
    part = "all"
  ) %>%
save_as_docx(
  path = "output/treatment_year_whole_cohort.docx"
)



# -----------------
# After matching
# -----------------

year_tablem <- mdata %>%
  count(YEARS, Treatment) %>%
  group_by(YEARS) %>%
  mutate(
    Percent = 100 * n / sum(n),
    n_percent = paste0(n, " (", round(Percent, 1), "%)")
  ) %>%
  select(YEARS, Treatment, n_percent) %>%
  pivot_wider(
    names_from = Treatment,
    values_from = n_percent
  ) %>%
  left_join(
    Out %>%
      count(YEARS, name = "Total_n") %>%
      mutate(
        Total_percent = 100 * Total_n / nrow(Out),
        Total = paste0(Total_n, " (", round(Total_percent, 1), "%)")
      ) %>%
      select(YEARS, Total),
    by = "YEARS"
  ) %>%
  arrange(YEARS)

year_tablem <- year_tablem %>%
  rename(
    `Year of Surgery` = YEARS,
    `Cohen n (%)` = Cohen,
    `Lich–Gregoir n (%)` = `Lich–Gregoir`,
    `Total surgeries` = Total
  )

year_tablem %>%
  gt()

year_tablem


year_tablem <- year_tablem %>%
  mutate(
    `Year of Surgery` = as.character(`Year of Surgery`)
  )

year_tablem %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    align = "center",
    part = "all"
  ) %>%
save_as_docx(
  path = "output/treatment_year_matched_cohort.docx"
)


# ---------------------
# After ATO weighting
# ---------------------

year_table_ato <- Out %>%
  group_by(YEARS, Treatment) %>%
  summarise(
    weighted_n = sum(weights),
    .groups = "drop"
  ) %>%
  group_by(YEARS) %>%
  mutate(
    Percent = 100 * weighted_n / sum(weighted_n),
    n_percent = paste0(
      round(weighted_n, 1),
      " (",
      round(Percent, 1),
      "%)"
    )
  ) %>%
  select(YEARS, Treatment, n_percent) %>%
  pivot_wider(
    names_from = Treatment,
    values_from = n_percent
  ) %>%
  left_join(
    Out %>%
      group_by(YEARS) %>%
      summarise(
        weighted_total = sum(weights),
        .groups = "drop"
      ) %>%
      mutate(
        Total_percent = 100 * weighted_total / sum(weighted_total),
        Total = paste0(
          round(weighted_total, 1),
          " (",
          round(Total_percent, 1),
          "%)"
        )
      ),
    by = "YEARS"
  ) %>%
  arrange(YEARS)

year_table_ato <- year_table_ato %>%
  rename(
    `Year of Surgery` = YEARS,
    `Cohen n (%)` = Cohen,
    `Lich–Gregoir n (%)` = `Lich–Gregoir`,
    `Total surgeries` = Total
  )

year_table_ato %>%
  gt()

year_table_ato


year_table_ato <- year_table_ato %>%
  mutate(
    `Year of Surgery` = as.character(`Year of Surgery`)
  )

year_table_ato %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  align(
    align = "center",
    part = "all"
  ) %>%
save_as_docx(
  path = "output/treatment_year_overlap_cohort.docx"
)

```


#### Transition in practice: Observed transition in practice

```{r transition}

# -----------------
# The whole cohort
# -----------------

plot_data1 <- Out %>%
  count(YEARS, Treatment) %>%
  group_by(YEARS) %>%
  mutate(
    Percent = 100 * n / sum(n)
  ) %>%
  ungroup()

p_transition1 <- ggplot(
  plot_data1,
  aes(
    x = YEARS,
    y = Percent,
    color = Treatment,
    group = Treatment
  )
) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2) +
  scale_y_continuous(
    limits = c(0, 100),
    breaks = seq(0, 100, 20),
    labels = function(x) paste0(x, "%")
  ) +
  scale_x_continuous(
    limits = c(2010, 2022),
    breaks = seq(2010, 2022, 1),
    expand = expansion(mult = c(0, 0.02))
  ) +
  scale_color_viridis_d(
    option = "mako",
    begin = 0.3,
    end = 0.8
  ) +
  labs(
    x = "Year of Surgery",
    y = "Proportion of Procedures",
    color = "Group"
  ) +
  theme_classic()

p_transition1

# -----------------
# After matching
# -----------------

plot_data <- mdata %>%
  count(YEARS, Treatment) %>%
  group_by(YEARS) %>%
  mutate(
    Percent = 100 * n / sum(n)
  ) %>%
  ungroup()

p_transition <- ggplot(
  plot_data,
  aes(
    x = YEARS,
    y = Percent,
    color = Treatment,
    group = Treatment
  )
) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2) +
  scale_y_continuous(
    limits = c(0, 100),
    breaks = seq(0, 100, 20),
    labels = function(x) paste0(x, "%")
  ) +
  scale_x_continuous(
    limits = c(2010, 2022),
    breaks = seq(2010, 2022, 1),
    expand = expansion(mult = c(0, 0.02))
  ) +
  scale_color_viridis_d(
    option = "mako",
    begin = 0.3,
    end = 0.8
  ) +
  labs(
    x = "Year of Surgery",
    y = "Proportion of Procedures",
    color = "Group"
  ) +
  theme_classic()

p_transition

# ---------------------
# After ATO weighting
# ---------------------

plot_data_ato <- Out %>%
  group_by(YEARS, Treatment) %>%
  summarise(
    weighted_n = sum(weights),
    .groups = "drop"
  ) %>%
  group_by(YEARS) %>%
  mutate(
    Percent = 100 * weighted_n / sum(weighted_n)
  ) %>%
  ungroup()

p_transition_ato <- ggplot(
  plot_data_ato,
  aes(
    x = YEARS,
    y = Percent,
    color = Treatment,
    group = Treatment
  )
) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2) +
  scale_y_continuous(
    limits = c(0,100),
    breaks = seq(0,100,20),
    labels = function(x) paste0(x,"%")
  ) +
  scale_x_continuous(
  limits = c(2010, 2022),
  breaks = seq(2010, 2022, 1),
  expand = expansion(mult = c(0, 0.02))
  ) +
  scale_color_viridis_d(
    option = "mako",
    begin = 0.3,
    end = 0.8
  ) +
  labs(
    x = "Year of Surgery",
    y = "ATO-weighted proportion of procedures",
    color = "Group"
  ) +
  theme_classic()

p_transition_ato

#------------------------------------------------------------
# Add subtitle (we can keep or remove them from the final figure)
#------------------------------------------------------------

p_transition1 <- p_transition1 +
  labs(subtitle = "Whole cohort")

p_transition <- p_transition +
  labs(subtitle = "Matched cohort")

p_transition_ato <- p_transition_ato +
  labs(subtitle = "Overlap weighting population")

#------------------------------------------------------------
# Combine plot 
#------------------------------------------------------------

transition_plot <-
  p_transition1 /
  p_transition /
  p_transition_ato +
  plot_layout(heights = c(2,2,2)) +
  plot_annotation(
    tag_levels = "A"
  )

#------------------------------------------------------------
# Save the figure
#------------------------------------------------------------
ggsave(filename = "figures/transition_in practice.png", 
       plot = transition_plot, 
       width = 8,   # width in inches
       height = 10,  # height in inches
       dpi = 300)   # resolution

```

# FLOWCHART

```{r flow}

f <- grViz("
digraph CONSORT {

graph [
    layout = dot,
    rankdir = TB,
    splines = ortho,
    nodesep = 0.4,
    ranksep = 0.6
]

node [
  shape = box,
  style = 'rounded,filled',
  fillcolor = white
]

# Main pathway
A [label =
'Children undergoing unilateral ureteral reimplantation
June 2010 – September 2022
Assessed for eligibility
N = 441']


C [label = 'Original cohort\\nN = 412 (93.4%)

Cohen group n= 197\\nLich-Gregoir group n= 215']

D [label = 'Propensity score overlap weighting (ATO) using R software

Propensity score model covariates: 
Calendar year
Indications for surgery
Prior Deflux injection
Age at surgery
Gender
BMI
VUR grade and laterality
Ureteral dilation
VUR phase on VCUG
Type and number of preoperative UTIs
Preoperative acute pyelonephritis and renal scarring on DMSA
Surgeon experience

Covariate balance: Absolute standardized difference (ASD) <0.1']

E [label = 'Weighted overlap pseudo-population\\nN = 412

No exclusions after weighting, all patients contributed to analysis with weights']

F [label = 'Weighted outcome analyses']

# Side exclusion
B [label = 'Excluded n = 29 (6.6%)

Secondary VUR n = 0\\nRepeat or tapering reimplantation procedures n = 0\\nBladder and bowel dysfunction n = 0\\nPosterior urethral valves n = 0\\nPrevious bladder surgery n = 0\\nReflux-associated anomalies (ureterocoeles, duplex systems, megaureter, ectopic ureter) n = 28\\nSuspected renal failure related to multicystic dysplastic kidney n = 1']


# Invisible branching point
X [shape = point, width = 0.01, label = '']

# Main flow
A -> X [arrowhead = none]
X -> C 
C -> D
D -> E
E -> F

# Side branch
X -> B [style = dashed]

# Keep exclusion box beside the main flow
{ rank = same; X; B }

}
")


svg <- export_svg(f)
writeLines(svg, "figures/flowchart.svg")


rsvg_png(
  "figures/flowchart.svg",
  "figures/flowchart.png",
  width = 10000
)



saveWidget(
  f,
  file = "figures/flowchart.html",
  selfcontained = TRUE
)


webshot(
  "figures/flowchart.html",
  file = "figures/flowchart.png",
  vwidth = 800
)


# Convert html to png online: https://cloudconvert.com/to-png
```
